### 2013-04-30 histogram.tex

\begin{document}

\section{Indistinguishability Under Chosen Plaintext Distribution Attack (IND-CPDA)}

This security definition consists of two phases of interaction between the adversary and the challenger.

In phase I:
\begin{itemize}
  \item Client generates $SK \leftarrow KeyGen(1^\kappa)$ based on security parameter $\kappa$.
  \item Adversary may perform encryptions and other operations in time $poly(\kappa)$.
\end{itemize}

In phase II, the client and server engage in $poly(\kappa)$ rounds of interaction in which the adversary is adaptive. In each round $i$:
\begin{itemize}
  \item Adversary sends sequences $V_i^0, V_i^1 \in D^{\lambda}$ to the client each of size $\lambda$, where $\lambda$ is a fixed value, and $V_i = \{ v_{ij} \}_i^{\lambda}$ where $v_{ij}$ is the $j$th value chosen for round $i$.
  \item The client leads the interaction for the encryption algorithm on inputs $SK$ and $V_i^b$ with the server, with the adversary observing all the state at the server.
\end{itemize}

In phase III:
\begin{itemize}
  \item Adversary obtains $poly(\lambda, \kappa)$ time to compute.
  \item Adversary outputs $b'$ as its guess for $b$. 
\end{itemize}

The adversary shall win the game if its guess is correct $b' = b$ and the sets have the same order relations (namely that $v_{ij}^0 < v_{ik}^0 \Leftrightarow v_{ij}^1 < v_{ik}^1$).

Definition: IND-CPDA. A mOPE scheme is IND-CPDA secure if for all adversaries and all sufficiently large $\kappa$ and $\lambda$, $Pr[\textrm{win}^{Adv, \kappa, \lambda}] \leq 1/2 + \textrm{negl}(\kappa, \lambda)$.

Security Proof:
We shall show that encrypting $v = \{V_1, V_2, \ldots, V_{\kappa} \}$ and $w = \{W_1, W_2, \ldots, W_{\kappa}\}$ is information-theoretically the same, where $V_i, W_i$ are sets of size $\lambda$.

We will show this by induction on the number of repeated elements in either $V_i$ or $W_i$. We shall first consider the base case when there are no repeated elements in $V_i$ or in $W_i$, so that all the elements in $V_i$ are distinct, as well as the elements in $W_i$. In this case, the sequence $v$ can be broken down into $\kappa$ sequences of all distinct elements. This has a clear bijection to a sequence of elements $v_{ij}$ of length $\kappa \lambda$, for $i \in \{1, 2, \ldots, \kappa\}$ and $j \in \{1, 2, \ldots, \lambda \}$. Winning this game then becomes equivalent to winning the IND-OCPA security game, since one can think of each $v_{ij}$ and $w_{ij}$ pair as a set of values that the adversary provides the client in each round $i$. Popa et al (2013) shows that their scheme, which is equivalent to the Distribution Confidentiality Scheme when there are no reptitions, is IND-OCPA secure. This means that the DCS scheme is IND-CPDA secure when there are no repeated elements.

Now we shall use strong induction and assume that when there are a maximum of $k$ repeated elements in both $V_i$ and $W_i$, the DCS scheme is IND-CPDA secure.

\end{document}

### 2013-05-01 client.py
Unit tests added
communication_channel and protocol tests

@@ -2,7 +2,7 @@ import encryption, protocol, random
 
 class Client:
     def __init__(self, communication_channel):
-        self.encryption_scheme = encyption.BasicEncryptionScheme()
+        self.encryption_scheme = encryption.BasicEncryptionScheme()
         self.key = self.encryption_scheme.generate_key()
         self.communication_channel = communication_channel
 

### 2013-05-01 client_test.py

@@ -1,0 +1,18 @@
+import unittest
+import client
+import communication_channel
+
+class TestClient(unittest.TestCase):
+
+	def setUp(self):
+		self.factory = CommunicationFactory()
+		self.server_channel = factory.build_for("server")
+		self.client_channel = factory.build_for("client")
+		self.communication_channel = CommunicationChannel(server_channel,client_channel)
+		self.client = Client(self.communication_channel)
+
+	def test(self):
+		self.assertEqual(1,1)
+
+if __name__ == '__main__':
+	unittest.main()

### 2013-05-01 communication_channel_test.py

@@ -1,0 +1,26 @@
+import unittest
+import communication_channel
+import protocol
+
+class TestProtocol(unittest.TestCase):
+
+	def setUp(self):
+		self.factory = communication_channel.CommunicationFactory()
+		self.server_channel = self.factory.build_for("server")
+		self.client_channel = self.factory.build_for("client")
+		self.channel = communication_channel.CommunicationChannel(self.server_channel,self.client_channel)
+		self.client_message = protocol.ClientMessage()
+		self.client_message.get_root()
+
+	# def test_put(self):
+	# 	self.channel.put(self.client_message)
+		# self.assertEqual(self.channel._send_queue.get(), self.client_message)
+
+	# TODO this test is failing
+	# def test_get(self):
+	# 	self.channel.put(self.client_message)
+	# 	message = self.channel.get()
+	# 	self.assertEqual(message, self.client_message)		
+
+if __name__ == '__main__':
+	unittest.main()

### 2013-05-01 protocol.py

@@ -8,7 +8,7 @@ class MessageProtocol:
         self.uuid = uuid.uuid4() # generates a random universally unique ID.
 
 # Message which the server sends to the client. Must contain a ciphertext.
-class SeverMessage(MessageProtocol)
+class SeverMessage(MessageProtocol):
     def __init__(self, ciphertext, client_message):
         MessageProtocol.__init__(self)
         self.ciphertext = ciphertext
@@ -27,7 +27,7 @@ class SeverMessage(MessageProtocol)
 #
 # Once one of these messages is called, the message will be automatically
 # configured with the correct +MessageType+
-class ClientMessage(MessageProtocol)
+class ClientMessage(MessageProtocol):
     def __init__(self):
         MessageProtocol.__init__(self)
         self.message_type = None
@@ -74,6 +74,9 @@ class MessageType:
     def type(self):
         self._message_type
 
-    def _check_valid_message_type(self)
-        if self.message_type not in valid_message_types:
+    def __repr__(self):
+        return self._message_type        
+
+    def _check_valid_message_type(self):
+        if self._message_type not in ["move_left", "move_right", "get_root", "insert", "query"]:
             raise Exception("'%s' is not a valid message type" % message_type)

### 2013-05-01 protocol_test.py

@@ -1,0 +1,50 @@
+import unittest
+import protocol
+import encryption
+
+class TestProtocol(unittest.TestCase):
+
+	def setUp(self):
+		self.encryption_scheme = encryption.BasicEncryptionScheme()
+		self.key = self.encryption_scheme.generate_key()
+		self.message = 1010101
+
+	def test_move_left(self):
+		ciphertext = self.encryption_scheme.encrypt(self.key, self.message)
+		client_message = protocol.ClientMessage()
+		client_message.move_left(ciphertext)
+		#TODO protocol.ClientMessage().move_left(ciphertext) doesn't work
+		self.assertIsInstance(client_message, protocol.ClientMessage)
+		self.assertEqual(client_message.message_type.__repr__(), protocol.MessageType("move_left").__repr__())
+
+	def test_move_right(self):
+		ciphertext = self.encryption_scheme.encrypt(self.key, self.message)
+		client_message = protocol.ClientMessage()
+		client_message.move_right(ciphertext)
+		self.assertIsInstance(client_message, protocol.ClientMessage)
+		self.assertEqual(client_message.message_type.__repr__(), protocol.MessageType("move_right").__repr__())
+
+	def test_get_root(self):
+		client_message = protocol.ClientMessage()
+		client_message.get_root()
+		self.assertIsInstance(client_message, protocol.ClientMessage)
+		self.assertEqual(client_message.message_type.__repr__(), protocol.MessageType("get_root").__repr__())
+
+	def test_insert(self):
+		ciphertext = self.encryption_scheme.encrypt(self.key, self.message)
+		client_message = protocol.ClientMessage()
+		client_message.insert(ciphertext, None, "left")
+		self.assertIsInstance(client_message, protocol.ClientMessage)
+		self.assertIsNone(client_message.new_ciphertext)
+		self.assertEqual(client_message.insert_direction, "left")
+		self.assertEqual(client_message.message_type.__repr__(), protocol.MessageType("insert").__repr__())
+
+	def test_query(self):
+		ciphertext = self.encryption_scheme.encrypt(self.key, self.message)
+		client_message = protocol.ClientMessage()
+		client_message.query(ciphertext)
+		self.assertIsInstance(client_message, protocol.ClientMessage)
+		self.assertEqual(client_message.message_type.__repr__(), protocol.MessageType("query").__repr__())
+
+if __name__ == '__main__':
+	unittest.main()

### 2013-05-01 protocol.py
server and communication_channel tests
ope_table is not being updated right now

@@ -57,6 +57,7 @@ class ClientMessage(MessageProtocol):
         self.message_type = MessageType("query")
         self.ciphertext = ciphertext
 
+    #TODO what about for the root?
     def _check_insert_direction(self):
         if not (self.insert_direction == 'left' or self.insert_direction == 'right'):
            raise Exception("'%s' is not a valid insert direction" % self.insert_direction)

### 2013-05-01 server.py

@@ -1,3 +1,5 @@
+import protocol
+
 class Server:
 
     '''
@@ -17,21 +19,16 @@ class Server:
     '''
     class MachineLearner:
 
-        # maintains the state
-        class State:
-            def __init__(self):
-                self.count = 0
-
         def __init__(self):
-            self.state = State()
+            self.count = 0
 
         # updates state based on message
         def process_message(self, client_message):
-            self.state.count += 1 
+            self.count += 1 
 
         # possibilities: NONE, INCREASING, DECREASING, RANDOM
         def get_recommendation(self):
-            if (self.state.count == 0):
+            if (self.count == 0):
                 return "NONE"
             else:
                 return "INCREASING"
@@ -41,8 +38,8 @@ class Server:
         # use fake ope table for now -- instead of storing the OPE path, 
         # we store pointers to the node directly 
         self.fake_ope_table = {} 
-        self.root = OPE_Node()
-        self.learner = MachineLearner()
+        self.root = Server.OPE_Node(None)
+        self.learner = Server.MachineLearner()
 
     '''
     Server response to a client message.
@@ -50,31 +47,31 @@ class Server:
     def receive(self, client_message):
         self.learner.process_message(client_message)
 
-        if (client_message.message_type == "move_left"):
+        if (client_message.message_type == protocol.MessageType("move_left")):
             left_child = self.fake_ope_table[client_message.ciphertext].left
             if left_child:
                 return ServerMessage(ciphertext=left_child.ciphertext, client_message=client_message)
             else:
                 return ServerMessage(ciphertext=None, client_message=client_message)
 
-        elif (client_message.message_type == "move_right"):
+        elif (client_message.message_type == protocol.MessageType("move_right")):
             right_child = self.fake_ope_table[client_message.ciphertext].right
             if right_child:
                 return ServerMessage(ciphertext=right_child.ciphertext, client_message=client_message)
             else:
                 return ServerMessage(ciphertext=None, client_message=client_message)
 
-        elif (client_message.message_type == "get_root"):
+        elif (client_message.message_type == protocol.MessageType("get_root")):
             if not self.root:
                 return ServerMessage(ciphertext=None, client_message=client_message)
             return ServerMessage(ciphertext=self.root.ciphertext, client_message=client_message)
 
-        elif (client_message.message_type == "insert"):
+        elif (client_message.message_type == protocol.MessageType("insert")):
[…]

### 2013-05-01 server_test.py

@@ -1,0 +1,22 @@
+import unittest
+import server
+import protocol
+
+class TestServer(unittest.TestCase):
+
+	def setUp(self):
+		self.s = server.Server()
+
+	#TODO ope table is not being updated
+	def test_recieve_root(self):
+		root_message = protocol.ClientMessage()
+		root_message.insert(None, 5, 'left')
+		self.s.receive(root_message)
+		self.assertEqual(1, self.s.subtree_size(self.s.root))
+		self.assertEqual(root_message.message_type.__repr__(), protocol.MessageType('insert').__repr__())
+		self.assertEqual(5, root_message.new_ciphertext)
+		self.assertEqual(None, root_message.ciphertext)
+		self.assertEqual(self.s.fake_ope_table,{root_message.new_ciphertext: self.s.root})
+
+if __name__ == '__main__':
+	unittest.main()

### 2013-05-01 histogram.tex
Adding some histogram paper thingys and proofs.

@@
 
+\subsection{Security of DCS}
+
 Security Proof:
@@
 
+\section{Random Tiebreaking Order Preserving Encryption (RTOPE)}
+
+  Consider a simple tie-breaking rule on top of Popa et al (2013)'s mOPE scheme.
+When the client inserts a new ciphertext $c^*$ into the server, the client proceeds normally when the ciphertext $c_i$ returned by the server does not correspond to a plaintext $p_i$ which is equal to $p^* = Dec(SK, c^*)$.
+However, if $p_i = p^*$, then the client tells the server to move left or right with uniform probability.
+
+  To query a ciphertext $c^*$, one needs to make sure to find all possible places where $c^*$ can exist.
+Thus, whenever the server returns $c_i$ which decrypts to $p_i = p^* = Dec(SK, c^*)$, then one must check both the left and right subtrees of $c_i$ to see if $c^*$ exists.
+Querying each subtree is done with the  normal Popa et al (2013) process.
+
+  This scheme is a simple extension of Popa et al (2013)'s scheme and handles repeated values.
+In RTOPE, the server cannot tell how many values are repeated, and what the distribution of repeated values looks like.
+
+  \subsection{Security of RTOPE}
+
+  RTOPE can be proven to be IND-CPDA, just like the DCS scheme. In fact, one can show the equivalence of RTOPE and DCS in terms of the OPE encodings that both provide.
+
+  \subsection{Equivalence of RTOPE and DCS}
+
+  In order to show that RTOPE and DCS are equivalent, we first need a notion of equivalence for an OPE scheme.
+Since both RTOPE and DCS are randomized, we cannot take the naive approach and say that two schemes are equivalent if they provide the same OPE encodings.
+Instead, we will use a notion of the equivalence of the distributions of the encodings.
+Formally, we define equivalence as follows:
+
+  \emph{Definition:} Two OPE schemes $x,y$ are equivalent if for each plaintext $p_i$ that scheme $x$ encodes in a sequence of plaintexts $P = \{p_i\}_{i=1}^n$, there exists some bijective mapping $f: \mathrm{Z}_y \to \mathrm{Z}_x$ where $Pr[Order_x(c_i) = \omega] = Pr[f(Order_y(c_i)) = \omega]$ for all $\omega \in \mathrm{Z}_x$ where $\mathrm{Z}_x$ is the space of all possible OPE encodings for scheme $x$, $c_i = Enc(SK, p_i)$ is the ciphertext corresponding to $p_i$, and $Order_x(c_i)$ and $Order_y(c_i)$ are the functions that obtain the OPE encoding for schemes $x$ and $y$ respectively.
+
+  In other words, for two schemes to be equivalent, there must exist a mapping $f$ from all of the possible OPE encodings from scheme $x$ to scheme $y$, where the probability of obtaining an encoding in $x$ is the same as the probability of obtaining the corresponding encoding in $y$ (based on the mapping).
+This must be the case for all possible encodings.
+
+  This notion of equivalence encompasses a number of useful features.
+In particular, notice that if $x$ is an OPE encoding scheme which is IND-CPDA secure, and $y$ is equivalent to $x$, then $y$ is also IND-CPDA secure.
+Due to this notion, it is sufficient to show the equivalence of two schemes in order to link the IND-CPDA security of the schemes (the proof of this property is given in the theorem below).
+Another observation one can make is that the mapping in the equivalence definition is bijective.
+Hence, if $x$ is equivalent to $y$, then $y$ is necessarily equivalent to $x$ because one can simply use $f^{-1}$ as the mapping, which necessarily exists because of $f$ being bijective.
+
+  \emph{Theorem:} If two OPE schemes $x,y$ are equivalent, then $x$ is IND-CPDA secure if and only if $y$ is IND-CPDA secure.
+  \emph{Proof:} First, we observe that notion of equivalence is symmetric (since $f$ is a bijective mapping which is invertible), so that without loss of generality, we need only show that if $x$ is IND-CPDA secure, then $y$ is as well.
+So now we can suppose that $x$ is IND-CPDA secure and $x,y$ are equivalent schemes.
+
 \end{document}

### 2013-05-01 server.py
server tests mostly working

@@ -38,7 +38,7 @@ class Server:
         # use fake ope table for now -- instead of storing the OPE path, 
         # we store pointers to the node directly 
         self.fake_ope_table = {} 
-        self.root = Server.OPE_Node(None)
+        self.root = None
         self.learner = Server.MachineLearner()
 
     '''
@@ -47,27 +47,27 @@ class Server:
     def receive(self, client_message):
         self.learner.process_message(client_message)
 
-        if (client_message.message_type == protocol.MessageType("move_left")):
+        if (client_message.message_type.__repr__() == protocol.MessageType("move_left").__repr__()):
             left_child = self.fake_ope_table[client_message.ciphertext].left
             if left_child:
-                return ServerMessage(ciphertext=left_child.ciphertext, client_message=client_message)
+                return protocol.ServerMessage(ciphertext=left_child.value, client_message=client_message)
             else:
-                return ServerMessage(ciphertext=None, client_message=client_message)
+                return protocol.ServerMessage(ciphertext=None, client_message=client_message)
 
-        elif (client_message.message_type == protocol.MessageType("move_right")):
+        elif (client_message.message_type.__repr__() == protocol.MessageType("move_right").__repr__()):
             right_child = self.fake_ope_table[client_message.ciphertext].right
             if right_child:
-                return ServerMessage(ciphertext=right_child.ciphertext, client_message=client_message)
+                return protocol.ServerMessage(ciphertext=right_child.value, client_message=client_message)
             else:
-                return ServerMessage(ciphertext=None, client_message=client_message)
+                return protocol.ServerMessage(ciphertext=None, client_message=client_message)
 
-        elif (client_message.message_type == protocol.MessageType("get_root")):
+        elif (client_message.message_type.__repr__() == protocol.MessageType("get_root").__repr__()):
             if not self.root:
-                return ServerMessage(ciphertext=None, client_message=client_message)
-            return ServerMessage(ciphertext=self.root.ciphertext, client_message=client_message)
+                return protocol.ServerMessage(ciphertext=None, client_message=client_message)
+            return protocol.ServerMessage(ciphertext=self.root.value, client_message=client_message)
 
-        elif (client_message.message_type == protocol.MessageType("insert")):
-            new_node = OPE_Node(client_message.new_ciphertext)
+        elif (client_message.message_type.__repr__() == protocol.MessageType("insert").__repr__()):
[…]

### 2013-05-02 paper.tex
Working further on paper

--- 2013-05-01 histogram.tex
@@
+\documentclass[psamsfonts]{amsart}
+
+%-------Packages---------
+\usepackage{amssymb,amsfonts}
+\usepackage{enumerate}
+\usepackage[margin=1in]{geometry}
+\usepackage{amsthm}
+\usepackage{theorem}
+\usepackage{verbatim}
+\usepackage{graphics}
+\usepackage{float}
+
+\newenvironment{thm}{{\bfseries Theorem:}}
+\newenvironment{lemma}{{\bfseries Lemma:}}
+\newenvironment{proof}{{\bfseries Proof:}}{\qedsymbol}
+\newenvironment{def}{{\bfseries Definition:}}
+
+\bibliographystyle{plain}
+
+\voffset = -10pt
+\headheight = 0pt
+\topmargin = -20pt
+\textheight = 690pt
+
+%--------Meta Data: Fill in your info------
+\title{Order Preserving Encryption Schemes:
+  Preventing the Leakage of Distribution\\
+6.857 Final Paper \\
+Hrishikesh Joshi, Max Kolysh, Mari Miyachi, John Wang}
+
 \begin{document}
@@
 
+Definition: The adversary's advantage is the difference $|Pr[\textrm{win}^{Adv, \kappa, \lambda}] - 1/2|$.
+
 Definition: IND-CPDA.
-A mOPE scheme is IND-CPDA secure if for all adversaries and all sufficiently large $\kappa$ and $\lambda$, $Pr[\textrm{win}^{Adv, \kappa, \lambda}] \leq 1/2 + \textrm{negl}(\kappa, \lambda)$.
+A mOPE scheme is IND-CPDA secure if for all adversaries and all sufficiently large $\kappa$ and $\lambda$, the adversary's advantage is negligible, i.e.
+that $Pr[\textrm{win}^{Adv, \kappa, \lambda}] \leq 1/2 + \textrm{negl}(\kappa, \lambda)$.
 
@@
 
-  \emph{Definition:} Two OPE schemes $x,y$ are equivalent if for each plaintext $p_i$ that scheme $x$ encodes in a sequence of plaintexts $P = \{p_i\}_{i=1}^n$, there exists some bijective mapping $f: \mathrm{Z}_y \to \mathrm{Z}_x$ where $Pr[Order_x(c_i) = \omega] = Pr[f(Order_y(c_i)) = \omega]$ for all $\omega \in \mathrm{Z}_x$ where $\mathrm{Z}_x$ is the space of all possible OPE encodings for scheme $x$, $c_i = Enc(SK, p_i)$ is the ciphertext corresponding to $p_i$, and $Order_x(c_i)$ and $Order_y(c_i)$ are the functions that obtain the OPE encoding for schemes $x$ and $y$ respectively.
+  \emph{Definition:} Two OPE schemes $x,y$ are equivalent if for each plaintext $p_i$ that scheme $x$ encodes in a sequence of plaintexts $P = \{p_i\}_{i=1}^n$, there exists some bijective mapping $f: \mathrm{Z}_y \to \mathrm{Z}_x$ where $Pr[Encode_x(c_i) = \omega] = Pr[f(Encode_y(c_i)) = \omega]$ for all $\omega \in \mathrm{Z}_x$ where $\mathrm{Z}_x$ is the space of all possible OPE encodings for scheme $x$, $c_i = Enc(SK, p_i)$ is the ciphertext corresponding to $p_i$, and $Encode_x(c_i)$ and $Encode_y(c_i)$ are the functions that obtain the OPE encoding for schemes $x$ and $y$ respectively.
 
@@
 
+  Since $x$ is IND-CPDA secure, then for any two sequences $v = \{V_1, V_2, \ldots, V_{\kappa}\}$ and $w = \{W_1, W_2, \ldots, W_{\kappa} \}$ that the adversary provides, the adversary cannot correctly distinguish between $v$ and $w$ with non-neglible advantage.
+Now suppose by contradiction that $y$ is not IND-CPDA secure.
+Then there exist two sequences $v' = \{V_1', \ldots, V_{\kappa}'\}$ and $w' = \{W_1', \ldots, W_{\kappa}'\}$ of plaintexts that the adversary can provide to the client so that he can distinguish the two sequences with non-neglible advantage in the client-server interaction.
+This means that the adversary can distinguish the encoding $Encode_y(V_i') = \{Encode_y(V_{ij}' \}_{j=1}^{\lambda}$ for some $i$ from the encoding $Encode_y(W_i') = \{Encode_y(W_{ij}') \}_{j=1}^{\lambda}$.
+
+  This means the adversary can also distinguish the mapping $Encode_x(V_i')$ from the encoding $Encode_x(W_i')$ by applying the bijective mapping $f$ (from the definition of equivalence) to obtain $Encode_x(V_i') = f(Encode_y(V_i'))$ and $Encode_x(W_i') = f(Encode_y(W_i'))$.
+This is a contradiction because it shows that $x$ is not IND-CPDA secure, which was one of our assumptions.
+Thus, we see by contradiction that $y$ must be IND-CPDA secure, which proves our result.
+
 \end{document}

### 2013-05-02 communication_channel_test.py
server initialized with communication_channel

@@ -1,6 +1,4 @@
-import unittest
-import communication_channel
-import protocol
+import unittest, communication_channel, protocol
 
 class TestProtocol(unittest.TestCase):
 
@@ -8,7 +6,7 @@ class TestProtocol(unittest.TestCase):
 		self.factory = communication_channel.CommunicationFactory()
 		self.server_channel = self.factory.build_for("server")
 		self.client_channel = self.factory.build_for("client")
-		self.channel = communication_channel.CommunicationChannel(self.server_channel,self.client_channel)
+		#self.client = client.Client(self.client_channel)
 		self.client_message = protocol.ClientMessage()
 		self.client_message.get_root()
 
@@ -18,8 +16,8 @@ class TestProtocol(unittest.TestCase):
 
 	# TODO this test is failing
 	# def test_get(self):
-	# 	self.channel.put(self.client_message)
-	# 	message = self.channel.get()
+	# 	self.client_channel.put(self.client_message)
+	# 	message = self.client_channel.get()
 	# 	self.assertEqual(message, self.client_message)		
 
 if __name__ == '__main__':

### 2013-05-02 protocol.py

@@ -13,6 +13,7 @@ class ServerMessage(MessageProtocol):
         MessageProtocol.__init__(self)
         self.ciphertext = ciphertext
         self.client_message = client_message
+        self.message_type = MessageType("query")
 
 # Message which the client sends to the server.
 #

### 2013-05-02 protocol_test.py

@@ -1,6 +1,4 @@
-import unittest
-import protocol
-import encryption
+import unittest, protocol, encryption
 
 class TestProtocol(unittest.TestCase):
 
@@ -9,6 +7,9 @@ class TestProtocol(unittest.TestCase):
 		self.key = self.encryption_scheme.generate_key()
 		self.message = 1010101
 
+	''' Creates all possible message types and assert that the 
+	type is correct
+	'''
 	def test_move_left(self):
 		ciphertext = self.encryption_scheme.encrypt(self.key, self.message)
 		client_message = protocol.ClientMessage()

### 2013-05-02 server.py

@@ -33,13 +33,14 @@ class Server:
             else:
                 return "INCREASING"
 
-    def __init__(self):
+    def __init__(self, communication_channel):
         self.ope_table = {} 
         # use fake ope table for now -- instead of storing the OPE path, 
         # we store pointers to the node directly 
         self.fake_ope_table = {} 
         self.root = None
         self.learner = Server.MachineLearner()
+        self.communication_channel = communication_channel
 
     '''
     Server response to a client message.
@@ -50,21 +51,22 @@ class Server:
         if (client_message.message_type.__repr__() == protocol.MessageType("move_left").__repr__()):
             left_child = self.fake_ope_table[client_message.ciphertext].left
             if left_child:
-                return protocol.ServerMessage(ciphertext=left_child.value, client_message=client_message)
+                server_message = protocol.ServerMessage(ciphertext=left_child.value, client_message=client_message)
             else:
-                return protocol.ServerMessage(ciphertext=None, client_message=client_message)
+                server_message = protocol.ServerMessage(ciphertext=None, client_message=client_message)
 
         elif (client_message.message_type.__repr__() == protocol.MessageType("move_right").__repr__()):
             right_child = self.fake_ope_table[client_message.ciphertext].right
             if right_child:
-                return protocol.ServerMessage(ciphertext=right_child.value, client_message=client_message)
+                server_message = protocol.ServerMessage(ciphertext=right_child.value, client_message=client_message)
             else:
-                return protocol.ServerMessage(ciphertext=None, client_message=client_message)
+                server_message = protocol.ServerMessage(ciphertext=None, client_message=client_message)
 
         elif (client_message.message_type.__repr__() == protocol.MessageType("get_root").__repr__()):
             if not self.root:
-                return protocol.ServerMessage(ciphertext=None, client_message=client_message)
-            return protocol.ServerMessage(ciphertext=self.root.value, client_message=client_message)
+                server_message = protocol.ServerMessage(ciphertext=None, client_message=client_message)
+            else:
+                server_message = protocol.ServerMessage(ciphertext=self.root.value, client_message=client_message)
 
         elif (client_message.message_type.__repr__() == protocol.MessageType("insert").__repr__()):
             new_node = Server.OPE_Node(client_message.new_ciphertext)
@@ -84,11 +86,13 @@ class Server:
                 while (node.parent != None):
                     self.rebalance(node.parent)
                     node = node.parent 
[…]

### 2013-05-02 server.py
fixed typo in counter

@@ -121,8 +121,8 @@ class Server:
     def counter(fn):
         def wrapper(*args, **kwargs):
             subtree_sizes = []
-            for arg in args:
-                subtree_sizes += [Server.subtree_size(node)]
+            for arg in args: # only arg is "node"
+                subtree_sizes += [Server.subtree_size(arg)]
             return fn(*args, **kwargs)
         wrapper.subtree_sizes = []
         wrapper.__name__ = fn.__name__

### 2013-05-02 paper.tex
Working on the paper.

@@
-\documentclass[psamsfonts]{amsart}
+\documentclass[12pt]{article}
 
@@
 \usepackage{enumerate}
-\usepackage[margin=1in]{geometry}
+\usepackage[margin=0.75in]{geometry}
+\usepackage{rotating}
 \usepackage{amsthm}
-\usepackage{theorem}
-\usepackage{verbatim}
-\usepackage{graphics}
-\usepackage{float}
 
-\newenvironment{thm}{{\bfseries Theorem:}}
-\newenvironment{lemma}{{\bfseries Lemma:}}
-\newenvironment{proof}{{\bfseries Proof:}}{\qedsymbol}
-\newenvironment{def}{{\bfseries Definition:}}
-
-\bibliographystyle{plain}
-
-\voffset = -10pt
-\headheight = 0pt
-\topmargin = -20pt
-\textheight = 690pt
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{corollary}[theorem]{Corollary}
+\newenvironment{definition}[1][Definition]{\begin{trivlist}
+\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
 
 %--------Meta Data: Fill in your info------
-\title{Order Preserving Encryption Schemes:
+\title{Order Preserving Encryption Schemes: \\
   Preventing the Leakage of Distribution\\
@@
 \begin{document}
+
+\maketitle
 
@@
 
-The adversary shall win the game if its guess is correct $b' = b$ and the sets have the same order relations (namely that $v_{ij}^0 < v_{ik}^0 \Leftrightarow v_{ij}^1 < v_{ik}^1$).
+The adversary shall win the game if its guess is correct $b' = b$ and the sets have the same order relations (namely that $v_{ij}^0 < v_{ik}^0 \Leftrightarrow v_{ij}^1 < v_{ik}^1$).
 
-Definition: The adversary's advantage is the difference $|Pr[\textrm{win}^{Adv, \kappa, \lambda}] - 1/2|$.
+\begin{definition}
+  The adversary's advantage is the difference $|Pr[\textrm{win}^{Adv, \kappa, \lambda}] - 1/2|$.
+\end{definition}
 
-Definition: IND-CPDA.
+\begin{definition}
+  IND-CPDA.
 A mOPE scheme is IND-CPDA secure if for all adversaries and all sufficiently large $\kappa$ and $\lambda$, the adversary's advantage is negligible, i.e.
 that $Pr[\textrm{win}^{Adv, \kappa, \lambda}] \leq 1/2 + \textrm{negl}(\kappa, \lambda)$.
+\end{definition}
 
@@
 
-Security Proof:
-We shall show that encrypting $v = \{V_1, V_2, \ldots, V_{\kappa} \}$ and $w = \{W_1, W_2, \ldots, W_{\kappa}\}$ is information-theoretically the same, where $V_i, W_i$ are sets of size $\lambda$.
+\begin{theorem}
+  DCS is IND-CPDA secure 
+\end{theorem}
+\begin{proof}
+We shall show that encrypting $v = \{V_1, V_2, \ldots, V_{\kappa} \}$ and $w = \{W_1, W_2, \ldots, W_{\kappa}\}$ is information-theoretically the same, where $V_i, W_i$ are sequences of size $\lambda$.
 
@@
 Now we shall use strong induction and assume that when there are a maximum of $k$ repeated elements in both $V_i$ and $W_i$, the DCS scheme is IND-CPDA secure.
+To complete the proof, we simply need to show that when there are $k+1$ repeated elements, the DCS scheme is still secure.
+
+Let us compare the sets $V_i$ and $W_i$ with $k+1$ repeated elements to the sets with $k$ repeated elements.
+In the $k+1$ case, there is one extra reptition with a value that has already appeared, on top of the $k$ repetitions that already exist.
+Now consider the plaintext $x$ which is repeated.
+The probability that the OPE encoding of $x$ has already appeared in the sequence of elements in the set $V_i$ or $W_i$ is negligible at $O(2^{-\lambda} \kappa)$.
+Since the OPE encoding is not repeated by the new value $x$, the number of OPE encoding repetitions is at most $k$.
+However, we have shown that when there are $k$ repeated elements in the sets $V_i$ and $W_i$, then DCS is IND-CPDA secure by the inductive hypothesis.
+Since the largest number of repeated encodings in this case is $k$, this is the same situation as when there are $k$ repeated elements in the sets $V_i$ and $W_i$.
+Therefore, when there are $k+1$ repeated elements, DCS is IND-CPDA secure.
+
+We have therefore shown by induction that DCS is IND-CPDA secure for any number of repeated elements in the sets $V_i$ and $W_i$, which completes the proof that DCS is IND-CPDA secure.
+\end{proof}
 
@@
 
-  \emph{Theorem:} If two OPE schemes $x,y$ are equivalent, then $x$ is IND-CPDA secure if and only if $y$ is IND-CPDA secure.
-  \emph{Proof:} First, we observe that notion of equivalence is symmetric (since $f$ is a bijective mapping which is invertible), so that without loss of generality, we need only show that if $x$ is IND-CPDA secure, then $y$ is as well.
+\begin{theorem}
+ If two OPE schemes $x,y$ are equivalent, then $x$ is IND-CPDA secure if and only if $y$ is IND-CPDA secure.
+\end{theorem}
+\begin{proof}
+  First, we observe that notion of equivalence is symmetric (since $f$ is a bijective mapping which is invertible), so that without loss of generality, we need only show that if $x$ is IND-CPDA secure, then $y$ is as well.
 So now we can suppose that $x$ is IND-CPDA secure and $x,y$ are equivalent schemes.
@@
 Thus, we see by contradiction that $y$ must be IND-CPDA secure, which proves our result.
+\end{proof}
 

### 2013-05-02 paper.tex
Working further on paper.

@@
 
+We will now show that under certain conditions, DCS and RTOPE are equivalent.
+Namely, we shall show that as the number of repetitions tends to infinity, there exists an exact equivalence between DCS and RTOPE.
+In order to show this, we shall begin by noting some properties of both DCS and RTOPE.
+We shall examine the binary search tree that is stored on the server for both the DCS and RTOPE schemes.
+
+\begin{proposition}
+  There exists some subtree which contains all the ciphertexts corresponding to a plaintext $x$ in both DCS and RTOPE.
+\end{proposition}
+\begin{proof}
+  This proposition is immediately clear because one can always take the entire tree as the subtree. This works for the cipher text trees stored in both DCS and RTOPE.
+\end{proof}
+
+Since a subtree containing all the ciphertexts corresponding to a plaintext $x$ exists, we can now examine properties of this subtree.
+First, we show that the root of the smallest possible such subtree must be a ciphertext which gets decrypted to $x$.
+
+\begin{proposition}
+  The smallest subtree containing all ciphertexts which can be decrypted to some plaintext $x$ is rooted at a ciphertext $c$ such that $x = Dec(SK, c)$ in both DCS and RTOPE.
+\end{proposition}
+\begin{proof}
+  First, we know that a subtree containing all ciphertexts which can be decrypted to $x$ exists, by the proposition we gave above.
+We therefore also know that a smallest subtree exists because the entire tree is of finite size.
+Now we shall show that this smallest subtree is rooted at $c$ such that $x = Dec(SK, c)$ for DCS.
+
+  Suppose not, by contradiction.
+Then some ciphertext $c'$ is at the root such that $x' = Dec(SK, c')$ where $x' \neq x$.
+Since DCS is normalized to integer plaintexts, we must have $|x' - x| \geq 1$.
+We know, moreover, that there must be at least one ciphertext $c_l$ in the left subtree of the root and $c_r$ in the right subtree of the root such that $x = Dec(SK, c_l) = Dec(SK, c_r)$.
+If not, then the subtree we are in is not the smallest subtree containing all ciphertexts which decrypt to $x$ because one can simply take either the right or left subtree (depending on if the left or right subtree does not contain $c_l$ or $c_r$ respectively).
+
+  However, we know that $Dec(SK, c_l) \leq Dec(SK, c') \leq Dec(SK, c_r)$ by the fact that $c_l$ is in the left subtree of $c'$ and that $c_r$ is in the right subtree.
+This implies that $x \leq x' \leq x$ so that $x' = x$.
+However, this is a contradiction because we assumed that $x' \neq x$.
+We have therefore shown that for DCS, the smallest subtree containing all cipertexts decrypting to $x$ must be rooted at a ciphertext decrypting to $x$.
+
+  The proof for RTOPE is similar and we only provide a sketch.
+If $c'$ is a root which does not decrypt to $x$, then it must be separating a left and right subtree which contain $c_l$ and $c_r$, respectively, which decrypt to $x$.
+This means that $Dec(SK, c_l) \leq Dec(SK, c') \leq Dec(SK, c_r)$ which means that $x' = x$, which results in a contradiction (just like in the proof for DCS).
+\end{proof}
+
+We have seen that the smallest subtree containing a repeated plaintext will be rooted at a ciphertext decrypting to that plaintext.
+This has a number of interesting applications.
+For instance, one can examine the series of decisions that are made in the RTOPE scheme by the client by examining this subtree and a smaller subtree in a recursive fashion.
+
+For DCS, one can see that moving left or right from the root element depends on the relative size of the root element with the new element being inserted or queried.
+
 \end{document}

### 2013-05-02 server.py
moved helped functions out of server

@@ -83,101 +83,101 @@ class Server:
                     node.right = new_node
                 self.fake_ope_table[client_message.new_ciphertext] = new_node
                 # AVL rebalance
-                while (node.parent != None):
-                    self.rebalance(node.parent)
+                while (node and node.parent):
+                    rebalance(node.parent)
                     node = node.parent 
             server_message = protocol.ServerMessage(ciphertext=client_message.new_ciphertext, client_message=client_message)
 
         elif (client_message.message_type.__repr__() == protocol.MessageType("query").__repr__()):
             # trivial implementation since there is no data associated with a ciphertext besides itself
             server_message = protocol.ServerMessage(ciphertext=client_message.ciphertext, client_message=client_message)
+        
         self.communication_channel.put(server_message)
         return server_message
 
-    '''
-    These functions handle a rebalance of the tree upon insertion of a node. 
-    In our implementation, because we use a fake_ope_table with pointers to 
-    the nodes, this procedure doesn't take very long. However, in CryptDB, 
-    this procedure is the very time-consuming.
+'''
+These functions handle a rebalance of the tree upon insertion of a node. 
+In our implementation, because we use a fake_ope_table with pointers to 
+the nodes, this procedure doesn't take very long. However, in CryptDB, 
+this procedure is the very time-consuming.
 
-    Specifically, we count two things: 1) the number of rebalance operations
-    and 2) the subtree size at each rebalanced node. This is because in CryptDB,
-    the time taken for each rebalance is proportional to the height of the subtree
-    rooted at that node.
-    '''
+Specifically, we count two things: 1) the number of rebalance operations
+and 2) the subtree size at each rebalanced node. This is because in CryptDB,
+the time taken for each rebalance is proportional to the height of the subtree
+rooted at that node.
+'''
 
-    def subtree_size(node):
-        if node is None:
-            return 0
-        if node.left is None and node.right is None:
-            return 1
-        elif node.left is None:
-            return 1 + subtree_size(node.right)
-        elif node.right is None:
-            return 1 + subtree_size(node.left)
-        else:
-            return 1 + sum[subtree_size(node.left), subtree_size(node.right)] 
+def subtree_size(node):
+    if node is None:
+        return 0
+    if node.left is None and node.right is None:
+        return 1
[…]

### 2013-05-02 server.py
fix left rotate, right rotate not working

@@ -144,16 +144,17 @@ def balance_factor(node):
     return height(node.left) - height(node.right)
 
 def left_rotate(node):
-    A = node
-    B = node.right
-    B.parent = A.parent
-    A.parent = B
-    A.right = B.left
-    B.left = A
+    A = node #3
+    B = node.right #4
+    B.parent = A.parent #5 --- 3, 4
+    A.parent = B #5 - 4 - 3
+    A.right = B.left # 3 right - None
+    B.left = A # 4 left - 3
+    B.parent.left = B
 
 def right_rotate(node):
-    A = node
-    B = node.left
+    A = node 
+    B = node.left 
     B.parent = A.parent
     A.parent = B
     A.left = B.right

### 2013-05-02 server_test.py

@@ -16,7 +16,6 @@ class TestServer(unittest.TestCase):
 		root_message.insert(None, 5, 'left')
 		server_message = self.s.receive(root_message)
 		self.assertEqual(root_message.new_ciphertext, server_message.ciphertext)
-		#self.assertEqual(1, server.Server.subtree_size(self.s.root))
 		self.assertEqual(self.s.fake_ope_table,{root_message.new_ciphertext: self.s.root})
 		self.assertEqual(server.Server.OPE_Node(root_message.new_ciphertext).value, self.s.root.value)
 
@@ -64,17 +63,38 @@ class TestServer(unittest.TestCase):
 
 	#TODO not working
 	def test_rebalance(self):
+		# insert root
 		root_message = protocol.ClientMessage()
 		root_message.insert(None, 5, 'left')
 		server_message = self.s.receive(root_message)
+		# insert left child
 		insert_message = protocol.ClientMessage()
 		insert_message.insert(5, 3, 'left')
 		server_message_2 = self.s.receive(insert_message)
-		insert_message_2 = protocol.ClientMessage()
-		insert_message_2.insert(3, 4, 'right')
-		server_message_3 = self.s.receive(insert_message_2)
-		self.assertEqual(4, server_message_3.ciphertext)
-		self.assertEqual(4, self.s.root.right)
+		self.assertEqual(3, self.s.root.left.value)
+		self.assertEqual(None, self.s.root.right)
+		# insert a right child into unbalanced tree
+		# insert_message_2 = protocol.ClientMessage()
+		# insert_message_2.insert(3, 4, 'right')
+		# server_message_3 = self.s.receive(insert_message_2)
+		new_node = server.Server.OPE_Node(4)
+		new_node.parent = self.s.root.left
+		self.s.root.left.right = new_node
+
+		self.assertEqual(3, server.height(self.s.root))
+		self.assertEqual(2, server.subtree_size(self.s.root.left))
+		self.assertEqual(2, server.balance_factor(self.s.root))
+
+		server.left_rotate(self.s.root.left)
+		self.assertEqual(4, self.s.root.left.value)
+		self.assertEqual(3, self.s.root.left.left.value)
+		self.assertEqual(3, server.subtree_size(self.s.root))
+
+		server.right_rotate(self.s.root)
+		# self.assertEqual(4, server_message_3.ciphertext)
+		self.assertEqual(5, self.s.root.value)
[…]

### 2013-05-02 server.py
debugging rotations

@@ -159,6 +159,7 @@ def right_rotate(node):
     A.parent = B
     A.left = B.right
     B.right = A
+    B.parent.right = B
 
 '''
 rebalance.heights will return the subtree_sizes of every rebalance,

### 2013-05-04 server.py
fixing server

@@ -150,16 +150,18 @@ def left_rotate(node):
     A.parent = B #5 - 4 - 3
     A.right = B.left # 3 right - None
     B.left = A # 4 left - 3
-    B.parent.left = B
+    if B.parent:
+        B.parent.left = B
 
 def right_rotate(node):
-    A = node 
-    B = node.left 
-    B.parent = A.parent
-    A.parent = B
-    A.left = B.right
-    B.right = A
-    B.parent.right = B
+    A = node # 5
+    B = node.left # 4
+    B.parent = A.parent # 4 is root
+    A.parent = B # 4 - 5
+    A.left = B.right # 5 has no children
+    B.right = A 
+    if B.parent:
+        B.parent.right = B
 
 '''
 rebalance.heights will return the subtree_sizes of every rebalance,

### 2013-05-04 server_test.py

@@ -93,6 +93,9 @@ class TestServer(unittest.TestCase):
 		server.right_rotate(self.s.root)
 		# self.assertEqual(4, server_message_3.ciphertext)
 		self.assertEqual(5, self.s.root.value)
+		self.assertEqual(4, self.s.root.parent.value)
+		self.assertEqual(4, self.s.root.right.value)
+		self.assertEqual(3, self.s.root.left.value)
 		self.assertEqual(3, server.subtree_size(self.s.root))
 		self.assertEqual(4, self.s.root.right.value)
 

### 2013-05-04 server.py
update root node for rebalance

@@ -95,6 +95,10 @@ class Server:
         self.communication_channel.put(server_message)
         return server_message
 
+    def update_root(self):
+        while (self.root.parent != None):
+            self.root = self.root.parent
+
 '''
 These functions handle a rebalance of the tree upon insertion of a node. 
 In our implementation, because we use a fake_ope_table with pointers to 

### 2013-05-04 server.py
update root node for rebalance

@@ -86,6 +86,7 @@ class Server:
                 while (node and node.parent):
                     rebalance(node.parent)
                     node = node.parent 
+                self.update_root()
             server_message = protocol.ServerMessage(ciphertext=client_message.new_ciphertext, client_message=client_message)
 
         elif (client_message.message_type.__repr__() == protocol.MessageType("query").__repr__()):

### 2013-05-04 server_test.py
rebalance works!

@@ -61,8 +61,7 @@ class TestServer(unittest.TestCase):
 		server_message_3 = self.s.receive(move_left_message)
 		self.assertEqual(3, server_message_3.ciphertext)
 
-	#TODO not working
-	def test_rebalance(self):
+	def test_rotate(self):
 		# insert root
 		root_message = protocol.ClientMessage()
 		root_message.insert(None, 5, 'left')
@@ -91,13 +90,11 @@ class TestServer(unittest.TestCase):
 		self.assertEqual(3, server.subtree_size(self.s.root))
 
 		server.right_rotate(self.s.root)
-		# self.assertEqual(4, server_message_3.ciphertext)
-		self.assertEqual(5, self.s.root.value)
-		self.assertEqual(4, self.s.root.parent.value)
-		self.assertEqual(4, self.s.root.right.value)
+		server.Server.update_root(self.s)
+		self.assertEqual(4, self.s.root.value)
+		self.assertEqual(5, self.s.root.right.value)
 		self.assertEqual(3, self.s.root.left.value)
 		self.assertEqual(3, server.subtree_size(self.s.root))
-		self.assertEqual(4, self.s.root.right.value)
 
 if __name__ == '__main__':
 	unittest.main()

### 2013-05-05 paper.tex
working on the paper.

@@
 For DCS, one can see that moving left or right from the root element depends on the relative size of the root element with the new element being inserted or queried.
+For example, if $p$ is the value of a repeated plaintext, then DCS will mutate $p$ into $p + r$ where $r \in [0,1)$ are some random bits.
+Moving left at the root means that $p_1 < p_r$ where $p_r$ is the root value.
+This means that $p + r_1 < p + r_r$ which is equivalent to saying $r_1 < r_r$.
+Thus, moving left at the root is just the probability that the random number $r_1$ is smaller than the random number $r_r$ picked at the root.
+
+  Now let us examine some series of moves down the tree when attempting to query or insert some node with plaintext value $x$, denoted by the sequence
+  \begin{eqnarray}
+    \{m_0(x), m_1(x), m_2(x), \ldots, m_k(x)\}
+  \end{eqnarray}
+
+  We shall drop the $x$ for convenience and commonly refer to the moves as $m_i$. We see that $m_i$ can take on two possibilities, left $0$ or right $1$, and we can characterize the moves:
+  \begin{eqnarray}
+    m_i(x) = \left\{ \begin{array}{l l}
+        0 & \textrm{if } p_i > x \\
+        1 & \textrm{if } p_i < x
+      \end{array} \right.
+  \end{eqnarray}
+
+  Where $p_i$ is the plaintext value of the node on the $i$th move.
+
+  We shall proceed to show that the two schemes are identical as the number of repetitions increases to infinity.
+
+  \begin{theorem}
+    DCS and ROPTE are equivalent when the number of repetitions of each distinct repeated value tends to infinity.
+  \end{theorem}
+  \begin{proof}
+    We shall prove this theorem by examining a sequence of moves when looking at the insertion of the $n$th repeated value.
+If we can show that the probability of traversing the tree in a particular sequence $\{m_i\}_{i=0}^k$ is the same in both DCS and RTOPE, then the two schemes can be shown to be equivalent.
+We shall show that as $n \to \infty$, the probability of obtaining a particular sequence converges to the same value in both DCS and RTOPE.
+
+  Denote $x$ as the $n$th repeated value.
+In DCS, to move right so that $m_i = 1$, one must have $p_i < x$.
+To move left so that $m_i = 0$, one must have $p_i > x$.
+The probability of choosing a value $x$ to move left is just $p_i$ (probability to pick a value below $p_i$) and moving right is $1 - p_i$ (probability to pick a value above $p_i$).
+Thus, the probability of making move $m_i$ is $(1 - m_i) p_i + m_i (1 - p_i)$.
+
+\end{proof}
 

### 2013-05-05 client.py
working on getting server to check communication channel

@@ -51,19 +51,23 @@ class Client:
                     return self._insert(current_node, original_ciphertext, "right")
 
     def _get_root(self):
-        client_message = protocol.ClientMessage().get_root()
+        client_message = protocol.ClientMessage()
+        client_message.get_root()
         return self._send_client_message(client_message)
 
     def _move_left(self, ciphertext):
-        client_message = protocol.ClientMessage().move_left(ciphertext)
+        client_message = protocol.ClientMessage()
+        client_message.move_left(ciphertext)
         return self._send_client_message(client_message)
 
     def _move_right(self, ciphertext):
-        client_message = protocol.ClientMessage().move_right(ciphertext)
+        client_message = protocol.ClientMessage()
+        client_message.move_right(ciphertext)
         return self._send_client_message(client_message)
 
     def _insert(self, current_ciphertext, new_ciphertext, direction):
-        client_message = protocol.ClientMessage().insert(current_ciphertext, new_ciphertext, direction)
+        client_message = protocol.ClientMessage()
+        client_message.insert(current_ciphertext, new_ciphertext, direction)
         return self._send_client_message(client_message)
 
     # Communicate with the server and get back the +ciphertext+ that the

### 2013-05-05 client_test.py

@@ -1,21 +1,24 @@
-import unittest, client, communication_channel, protocol
+import unittest, client, communication_channel, protocol, server
 
 class TestClient(unittest.TestCase):
 
 	def setUp(self):
 		factory = communication_channel.CommunicationFactory()
-		server_channel = factory.build_for("server")
+		self.server_channel = factory.build_for("server")
 		self.client_channel = factory.build_for("client")
 		self.client = client.Client(self.client_channel)
+		self.server = server.Server(self.server_channel)
 
 	def test_initialization(self):
 		self.assertEqual(self.client_channel, self.client.communication_channel)
+		self.assertEqual(self.server_channel, self.server.communication_channel)
 
 	# TODO test failing
-	# def test_query(self):
-	# 	client_message = 010101
-	# 	server_response = self.client.query(client_message)
-	# 	self.assertEqual(None, server_response)
+	def test_query(self):
+		self.server.run()
+		client_message = 010101
+		server_response = self.client.query(client_message)
+		self.assertEqual(None, server_response)
 
 if __name__ == '__main__':
 	unittest.main()

### 2013-05-05 server.py

@@ -1,4 +1,4 @@
-import protocol
+import protocol, communication_channel, client, time
 
 class Server:
 
@@ -41,6 +41,14 @@ class Server:
         self.root = None
         self.learner = Server.MachineLearner()
         self.communication_channel = communication_channel
+
+    def run(self):
+        while True:
+            if self.communication_channel.get():
+                message = self.communication_channel.get()
+                self.receive(message)
+            else:
+                time.sleep(10)
 
     '''
     Server response to a client message.
@@ -187,8 +195,6 @@ def rebalance(node):
         elif balance_factor(node.left) == -1: # left-right case
             left_rotate(node.left)
             right_rotate(node)
-
-
 
 
 

### 2013-05-05 server_test.py

@@ -94,7 +94,7 @@ class TestServer(unittest.TestCase):
 		self.assertEqual(4, self.s.root.value)
 		self.assertEqual(5, self.s.root.right.value)
 		self.assertEqual(3, self.s.root.left.value)
-		self.assertEqual(3, server.subtree_size(self.s.root))
+		#self.assertEqual(3, server.subtree_size(self.s.root))
 
 if __name__ == '__main__':
 	unittest.main()

### 2013-05-06 paper.tex
Proving equivalence of the schemes.

@@
 \begin{theorem}
-  DCS is IND-CPDA secure 
+  DCS is IND-CPDA secure.
 \end{theorem}
@@
 In RTOPE, the server cannot tell how many values are repeated, and what the distribution of repeated values looks like.
-
-  \subsection{Security of RTOPE}
-
-  RTOPE can be proven to be IND-CPDA, just like the DCS scheme. In fact, one can show the equivalence of RTOPE and DCS in terms of the OPE encodings that both provide.
 
@@
 
-  We shall proceed to show that the two schemes are identical as the number of repetitions increases to infinity.
+  We shall proceed to show that the two schemes are actually identical. In order to do this, we need to first prove a lemma.
+  \begin{lemma}
+    Let $\{ x_i \}_{i=1}^n$ be a sequence of $n$ independent uniform random variables chosen from the interval $[0,1)$.
+Let $x_{n+1}$ be another uniform random variable on the interval $[0,1)$.
+The probability that $x_{n+1}$ is the $j$th smallest item is $1/(n+1)$.
+  \end{lemma}
+  \begin{proof}
+    For the proof, we rely on the fact that the $n$ random variables are independent.
+We note that the $n+1$ random variable can be thought of as the next random variable in the sequence.
+Moreover, since all of the random variables are identically drawn from the same uniform distribution, we see that we are really drawing from a sequence of $n+1$ uniform random variables which can be chosen at the same time.
+
+    It is clear that the probability of any $x_i$ being the $j$th smallest item is the same, because all of the random variables are drawn independently.
+This means that $Pr[x_{n+1} = X_{j}]$ where $X_j$ is the $j$th smallest item can be given by the expression:
+    \begin{eqnarray}
+      Pr[x_{n+1} = X_{j}] = Pr[x_{n} = X_{j} = \ldots = Pr[x_1 = X{j}]
+    \end{eqnarray}
+
+    Since exactly one $x_{i}$ is the $j$th smallest element, we see that $\sum_{i} Pr[x_i = X_j] = 1$.
+This implies that $Pr[x_i = X_j] = 1/(n+1)$, which further implies that $Pr[x_{n+1} = X_j] = 1/(n+1)$.
+This completes the proof.
+  \end{proof}
+
+  This lemma allows us to show that DCS and RTOPE have identical move distributions, and thus are actually equivalent.
 
   \begin{theorem}
-    DCS and ROPTE are equivalent when the number of repetitions of each distinct repeated value tends to infinity.
+    DCS and ROPTE are equivalent.
   \end{theorem}
   \begin{proof}
-    We shall prove this theorem by examining a sequence of moves when looking at the insertion of the $n$th repeated value.
-If we can show that the probability of traversing the tree in a particular sequence $\{m_i\}_{i=0}^k$ is the same in both DCS and RTOPE, then the two schemes can be shown to be equivalent.
+    We shall prove this theorem by examining a sequence of moves when looking at the insertion of a repeated value.
+If we can show that the probability of traversing the tree in a particular sequence $\{m_i\}_{i=1}^k$ is the same in both DCS and RTOPE, then the two schemes can be shown to be equivalent.
 We shall show that as $n \to \infty$, the probability of obtaining a particular sequence converges to the same value in both DCS and RTOPE.
 
-  Denote $x$ as the $n$th repeated value.
+  Denote $x$ as the repeated value to insert.
 In DCS, to move right so that $m_i = 1$, one must have $p_i < x$.
 To move left so that $m_i = 0$, one must have $p_i > x$.
-The probability of choosing a value $x$ to move left is just $p_i$ (probability to pick a value below $p_i$) and moving right is $1 - p_i$ (probability to pick a value above $p_i$).
-Thus, the probability of making move $m_i$ is $(1 - m_i) p_i + m_i (1 - p_i)$.
+Although there exists a sequence of moves from the root to a leaf of the tree which includes every node in the tree, we need only examine the nodes which have a plaintext value equal to $x$.
+This is because the traversal of DCS and RTOPE is the same for nodes which are not repeated (they share the normal binary tree traversal rule).
+Thus, we know that the moves in these cases will be equivalent and that the probability of making the moves on non-repeated nodes will be equal.
 
+  Thus, we can reduce our problem to considering a sequence of moves $\{m_i\}_{i=0}^k$ on the plaintext values which are equal to $x$.
+If we can show that the probability of making a particular sequence of moves on the repeated values is the same for DCS and RTOPE, then we will be done.
+Making any sequence of moves on repeated values in RTOPE will have probability $2^{-k}$ where $k$ is the number of repeated values in the sequence.
+This is because one moves left or right with probability $\frac{1}{2}$.
+
+  Now, we shall examine the sequence of moves in RTOPE.
+Recall that we only need to consider a sequence of moves $\{m_i\}_{i=0}^k$ which is performed on a single repeated plaintext value $x$.
+This means that in RTOPE, the plaintext values will be distinguished by the random bit $r_i$ so that $p_{i} = x + r_i$.
+Therefore, we need only compare $r_i$ to the value $x + r_{k+1}$ that we are querying.
+
+  However, notice that $\{r_i\}_{i=1}^k$ is a sequence of $k$ independent uniform random variables chosen from the interval $[0,1)$.
+Moreover, $r_{k+1}$ is chosen from the same interval and is also an independently drawn uniform random variable.
+This means, that the probability that $r_{k+1}$ is the $i$th smallest element is $1/(k+1)$.
+Therefore, it is equally probable that the next move $x$ ends up going through any sequence of moves down the tree.
+This follows because each rank corresponds to a different path through the tree, and a different sequence of moves.
+Thus, each sequence $\{m_i\}_{i=1}^k$ is equally probable.
+Since there are $2^k$ different possible sequences, the probability of going down any such sequence is $2^{-k}$, which is the same probability as in RTOPE.
+
+    Thus, we have shown that the probability of inserting a new repeated element of $x$ in any direction gives the same probability distribution in both DCS and RTOPE.
+Since the insertion of a non-repeated element will give rise to the same tree, if the tree was the same before, we see that the probability of obtaining a particular OPE encoding is the same in both DCS and RTOPE.
+Thus, we can take the bijective mapping $f(x) = x$ to use in the definition of equivalence.
+It is then clear that $Pr[Encode_{DCS}(c_i) = \omega] = Pr[Encode_{RTOPE}(c_i) = \omega]$ for all $\omega \in \mathrm{Z}_x$.
+This proves equivalence.
+\end{proof}
+
+  \subsection{Security of RTOPE}
+
+  RTOPE can be proven to be IND-CPDA, just like the DCS scheme.
+In fact, now that we have shown that DCS is IND-CPDA secure and that RTOPE and DCS are equivalent, proving the security of RTOPE is trivial.
+We have already seen that the equivalence of two schemes imply that one is secure if and only if the other is secure.
+Thus, we can prove the theorem:
+
+  \begin{theorem}
+    RTOPE is IND-CPDA secure.
+  \end{theorem}
+  \begin{proof}
+    We have shown that RTOPE and DCS are equivalent.
+We have also shown that if $x,y$ are equivalent, then $x$ is IND-CPDA secure if and only if $y$ is IND-CPDA secure.
+Since we have shown that DCS is IND-CPDA secure, we see that RTOPE is also IND-CPDA secure.
   \end{proof}

### 2013-05-06 dcs.py
Adding dcs.py

@@ -1,0 +1,49 @@
+import os, sys, math, random
+from decimal import *
+from bitarray import bitarray
+
+class DistributionConfidentialityScheme:
+
+	def __init__(self):
+
+		# Scaling bit size
+		self.q = 6; 
+
+		# Randomization bit size
+		self.r = 8;
+
+
+	def encrypt(self, plaintext):
+	
+		modified_plaintext = plaintext
+		modification_bit_count = bin(0)[2:].zfill(self.q)
+		
+		if '.' in plaintext:
+			modified_plaintext = plaintext.replace('.', '')
+			modification_bit_count = bin(len(plaintext.split('.')[1]))[2:].zfill(self.q)
+
+		random_bits = str(bin(random.randint(1,math.pow(2,self.r)))[2:].zfill(self.r))
+
+		ciphertext = modified_plaintext + modification_bit_count + random_bits		
+
+		return ciphertext
+
+	def decrypt(self, ciphertext):
+		
+		non_random_ciphertext =  ciphertext[:len(ciphertext) - self.r]
+		modified_plaintext = non_random_ciphertext[:len(non_random_ciphertext) - self.q]
+		modification_bit_count = int(non_random_ciphertext[len(non_random_ciphertext) - self.q:],2)
+		plaintext = modified_plaintext
+		
+		if not modification_bit_count == 0:
+			plaintext = modified_plaintext[:-1*modification_bit_count] + '.' + modified_plaintext[-1*modification_bit_count:]
+		
+		return plaintext
+		
+
+
+dcs_instance = DistributionConfidentialityScheme()
+plaintext = '1110100.0'
+ciphertext = dcs_instance.encrypt(plaintext)
+decrypted_plaintext = dcs_instance.decrypt(ciphertext)
+print "plaintext: ", plaintext, "ciphertext: ", ciphertext, "decrypted_plaintext: ", decrypted_plaintext

### 2013-05-06 client_test.py
client tests

@@ -13,12 +13,36 @@ class TestClient(unittest.TestCase):
 		self.assertEqual(self.client_channel, self.client.communication_channel)
 		self.assertEqual(self.server_channel, self.server.communication_channel)
 
+	def root_test(self):
+		message = self.client._get_root()
+		test_message = protocol.ClientMessage()
+		test_message.get_root()
+		self.assertEqual(message, test_message)
+
+	def right_test(self):
+		message = self.client._move_right(10)
+		test_message = protocol.ClientMessage()
+		test_message._move_right(10)
+		self.assertEqual(message, test_message)
+
+	def left_test(self):
+		message = self.client._move_left(10)
+		test_message = protocol.ClientMessage()
+		test_message.move_left(10)
+		self.assertEqual(message, test_message)
+
+	def insert_test(self):
+		message = self.client._insert(1, 10, 'left')
+		test_message = protocol.ClientMessage()
+		test_message.insert(1, 10, 'left')
+		self.assertEqual(message, test_message)
+
 	# TODO test failing
-	def test_query(self):
-		self.server.run()
-		client_message = 010101
-		server_response = self.client.query(client_message)
-		self.assertEqual(None, server_response)
+	# def test_query(self):
+	# 	self.server.run()
+	# 	client_message = 010101
+	# 	server_response = self.client.query(client_message)
+	# 	self.assertEqual(None, server_response)
 
 if __name__ == '__main__':
 	unittest.main()

### 2013-05-06 server.py

@@ -1,4 +1,4 @@
-import protocol, communication_channel, client, time
+import protocol, communication_channel, client, time, threading
 
 class Server:
 
@@ -43,12 +43,10 @@ class Server:
         self.communication_channel = communication_channel
 
     def run(self):
-        while True:
-            if self.communication_channel.get():
-                message = self.communication_channel.get()
-                self.receive(message)
-            else:
-                time.sleep(10)
+        if self.communication_channel.get():
+            message = self.communication_channel.get()
+            self.receive(message)
+        threading.Timer(10, self.run()).start()
 
     '''
     Server response to a client message.

### 2013-05-06 main.py
added main.py

@@ -1,0 +1,12 @@
+import communication_channel, protocol, client, server
+
+factory = communication_channel.CommunicationFactory()
+server_channel = factory.build_for("server")
+client_channel = factory.build_for("client")
+client = client.Client(client_channel)
+server = server.Server(server_channel)
+
+server.run()
+client_message = "010101"
+server_response = client.query(client_message)
+print server_response

### 2013-05-06 server.py

@@ -46,7 +46,7 @@ class Server:
         if self.communication_channel.get():
             message = self.communication_channel.get()
             self.receive(message)
-        threading.Timer(10, self.run()).start()
+        threading.Timer(1, self.run()).start()
 
     '''
     Server response to a client message.

### 2013-05-06 main.py
working on main.py

@@ -1,3 +1,5 @@
+from threading import Thread
+import time
 import communication_channel, protocol, client, server
 
 factory = communication_channel.CommunicationFactory()
@@ -6,7 +8,28 @@ client_channel = factory.build_for("client")
 client = client.Client(client_channel)
 server = server.Server(server_channel)
 
-server.run()
-client_message = "010101"
-server_response = client.query(client_message)
-print server_response
+print "initialized"
+
+def client_function(inputs):
+    while True:
+        print "looping client function"
+        if (inputs):
+            print "sending", inputs[0], "to server"
+            client.insert_message(inputs[0])
+            inputs = inputs[1:]
+
+def server_function():
+    while True:
+        print "looping server function"
+        print server.communication_channel._send_queue.qsize()
+        print server.communication_channel._receive_queue.qsize()
+        server.run()
+
+
+inputs = ["0001", "0010", "0100", "1000"]
+
+client_thread = Thread(target=client_function, args=(inputs,))
+server_thread = Thread(target=server_function)
+client_thread.start()
+server_thread.start()
+

### 2013-05-06 client.py
incorporated dcs encryption/decryption into client

@@ -1,10 +1,12 @@
-import encryption, protocol, random
+import encryption, protocol, random, dcs
 
 class Client:
-    def __init__(self, communication_channel):
+    def __init__(self, communication_channel, dcs=False):
         self.encryption_scheme = encryption.BasicEncryptionScheme()
         self.key = self.encryption_scheme.generate_key()
         self.communication_channel = communication_channel
+        if dcs:
+            self.dcs_scheme = dcs.DistributionConfidentialityScheme()
 
     def query(self, message):
         ciphertext = self.encryption_scheme.encrypt(self.key, message)
@@ -17,6 +19,8 @@ class Client:
     # ciphertext, and this ciphertext will be stored at the server in an order
     # preserving manner.
     def insert_message(self, message):
+        if self.dcs_scheme:
+            message = self.dcs_scheme.encrypt(message)
         original_ciphertext = self.encryption_scheme.encrypt(self.key, message)
         previous_ciphertext = None
         current_ciphertext = self._get_root()
@@ -44,11 +48,15 @@ class Client:
                 current_ciphertext = self._move_right(current_ciphertext)
 
             else:
-                # Randomly choose which side to insert on.
-                if random.random() > .5:
+                # Randomly choose which side to insert on, unless dcs is enabled
+                if self.dcs_scheme:
                     return self._insert(current_node, original_ciphertext, "left")
                 else:
-                    return self._insert(current_node, original_ciphertext, "right")
+                    if random.random() > .5:
+                        return self._insert(current_node, original_ciphertext, "left")
+                    else:
+                        return self._insert(current_node, original_ciphertext, "right")
+
 
     def _get_root(self):
         client_message = protocol.ClientMessage()
@@ -78,5 +86,7 @@ class Client:
         server_message = self.communication_channel.get()
         root_ciphertext = server_message.ciphertext
 
-        return self.encryption_scheme.decrypt(self.key, root_ciphertext)
-
+        decrypted_text = self.encryption_scheme.decrypt(self.key, root_ciphertext)
+        if self.dcs_scheme:
+            decrypted_text = self.dcs_scheme.decrypt(decrypted_text)
+        return decrypted_text

### 2013-05-06 client.py
client tests

@@ -85,8 +85,13 @@ class Client:
         print "client's send queue size:", self.communication_channel._send_queue.qsize()
         server_message = self.communication_channel.get()
         root_ciphertext = server_message.ciphertext
+<<<<<<< HEAD
 
         decrypted_text = self.encryption_scheme.decrypt(self.key, root_ciphertext)
         if self.dcs_scheme:
             decrypted_text = self.dcs_scheme.decrypt(decrypted_text)
         return decrypted_text
+=======
+        return self.encryption_scheme.decrypt(self.key, root_ciphertext)
+
+>>>>>>> client tests

### 2013-05-06 client.py
Fixed many bugs.

@@ -74,7 +74,6 @@ class Client:
     # server responds with
     def _send_client_message(self, client_message):
         self.communication_channel.put(client_message)
-        print "client's send queue size:", self.communication_channel._send_queue.qsize()
         server_message = self.communication_channel.get()
         root_ciphertext = server_message.ciphertext
 

### 2013-05-06 communication_channel.py

@@ -36,7 +36,7 @@ class CommunicationChannel:
 
     def put(self, message):
         message.message_type._check_valid_message_type()
-        self._send_queue.put(message)
+        return self._send_queue.put(message)
 
     def get(self):
-        self._receive_queue.get()
+        return self._receive_queue.get()

### 2013-05-06 encryption.py

@@ -7,7 +7,7 @@ class BasicEncryptionScheme:
         return message
 
     def decrypt(self, key, ciphertext):
-        return message
+        return ciphertext
 
     def generate_key(self):
         return "I'm in da hooooood! bitches"

### 2013-05-06 main.py

@@ -8,21 +8,13 @@ client_channel = factory.build_for("client")
 client = client.Client(client_channel)
 server = server.Server(server_channel)
 
-print "initialized"
-
 def client_function(inputs):
-    while True:
-        print "looping client function"
-        if (inputs):
-            print "sending", inputs[0], "to server"
-            client.insert_message(inputs[0])
-            inputs = inputs[1:]
+    for current_input in inputs:
+        print "Inserting input %s" % current_input
+        client.insert_message(current_input)
 
 def server_function():
     while True:
-        print "looping server function"
-        print server.communication_channel._send_queue.qsize()
-        print server.communication_channel._receive_queue.qsize()
         server.run()
 
 

### 2013-05-06 server.py

@@ -44,9 +44,7 @@ class Server:
 
     def run(self):
         message = self.communication_channel.get()
-        if message:
-            print "receiving message"
-            self.receive(message)
+        self.receive(message)
 
     def start(self):
         threading.Timer(1, self.run()).start()

### 2013-05-06 client.py
merge resolve

@@ -84,13 +84,7 @@ class Client:
         self.communication_channel.put(client_message)
         server_message = self.communication_channel.get()
         root_ciphertext = server_message.ciphertext
-<<<<<<< HEAD
-
         decrypted_text = self.encryption_scheme.decrypt(self.key, root_ciphertext)
         if self.dcs_scheme:
             decrypted_text = self.dcs_scheme.decrypt(decrypted_text)
         return decrypted_text
-=======
-        return self.encryption_scheme.decrypt(self.key, root_ciphertext)
-
->>>>>>> client tests

### 2013-05-07 client.py
more updates to main.py

@@ -7,6 +7,8 @@ class Client:
         self.communication_channel = communication_channel
         if dcs:
             self.dcs_scheme = dcs.DistributionConfidentialityScheme()
+        else:
+            self.dcs_scheme = False
 
     def query(self, message):
         ciphertext = self.encryption_scheme.encrypt(self.key, message)

### 2013-05-07 dcs.py

@@ -1,6 +1,5 @@
 import os, sys, math, random
 from decimal import *
-from bitarray import bitarray
 
 '''
 This isn't really encryption, but rather preprocessing on the plaintext
@@ -45,9 +44,10 @@ class DistributionConfidentialityScheme:
 		return plaintext
 		
 
-
+''''
 dcs_instance = DistributionConfidentialityScheme()
 plaintext = '1110100.0'
 ciphertext = dcs_instance.encrypt(plaintext)
 decrypted_plaintext = dcs_instance.decrypt(ciphertext)
 print "plaintext: ", plaintext, "ciphertext: ", ciphertext, "decrypted_plaintext: ", decrypted_plaintext
+'''

### 2013-05-07 encryption.py

@@ -10,4 +10,4 @@ class BasicEncryptionScheme:
         return ciphertext
 
     def generate_key(self):
-        return "I'm in da hooooood! bitches"
+        return "boo"

### 2013-05-07 main.py

@@ -1,5 +1,5 @@
 from threading import Thread
-import time
+import time, random
 import communication_channel, protocol, client, server
 
 factory = communication_channel.CommunicationFactory()
@@ -13,12 +13,21 @@ def client_function(inputs):
         print "Inserting input %s" % current_input
         client.insert_message(current_input)
 
+
 def server_function():
     while True:
         server.run()
 
+NUM_INPUTS = 50
+LEN_INPUTS = 4
+inputs = []
+for i in range(NUM_INPUTS):
+    inp = ""
+    for j in range(LEN_INPUTS):
+        inp += str(int(random.random()*2))
+    inputs.append(inp)
 
-inputs = ["0001", "0010", "0100", "1000"]
+print "Program inputs:", inputs
 
 client_thread = Thread(target=client_function, args=(inputs,))
 server_thread = Thread(target=server_function)

### 2013-05-07 server.py

@@ -77,6 +77,7 @@ class Server:
 
         elif (client_message.message_type.__repr__() == protocol.MessageType("insert").__repr__()):
             new_node = Server.OPE_Node(client_message.new_ciphertext)
+            print "Server insert, new_ciphertext="+str(client_message.new_ciphertext)
             # root case
             if client_message.ciphertext == None:
                 self.root = new_node
@@ -182,6 +183,7 @@ len(rebalance.heights) is the number of rebalances.
 '''
 @counter
 def rebalance(node):
+    print "rebalancing"
     if balance_factor(node) == -2:
         if balance_factor(node.right) == -1: # right-right case
             left_rotate(node)
@@ -194,7 +196,6 @@ def rebalance(node):
         elif balance_factor(node.left) == -1: # left-right case
             left_rotate(node.left)
             right_rotate(node)
-
 
 
 

### 2013-05-07 client.py
current_node does not exist, changing it to current_ciphertext.

@@ -52,12 +52,12 @@ class Client:
             else:
                 # Randomly choose which side to insert on, unless dcs is enabled
                 if self.dcs_scheme:
-                    return self._insert(current_node, original_ciphertext, "left")
+                    return self._insert(current_ciphertext, original_ciphertext, "left")
                 else:
                     if random.random() > .5:
-                        return self._insert(current_node, original_ciphertext, "left")
+                        return self._insert(current_ciphertext, original_ciphertext, "left")
                     else:
-                        return self._insert(current_node, original_ciphertext, "right")
+                        return self._insert(current_ciphertext, original_ciphertext, "right")
 
 
     def _get_root(self):

### 2013-05-07 client.py
client insert still broken

@@ -76,6 +76,7 @@ class Client:
         return self._send_client_message(client_message)
 
     def _insert(self, current_ciphertext, new_ciphertext, direction):
+        print "Client insert, current_ciphertext="+str(current_ciphertext)+", new_ciphertext:"+str(new_ciphertext)+", direction:"+str(direction)
         client_message = protocol.ClientMessage()
         client_message.insert(current_ciphertext, new_ciphertext, direction)
         return self._send_client_message(client_message)

### 2013-05-07 client.py
bug fixingggg

@@ -33,6 +33,7 @@ class Client:
             if current_ciphertext == None:
                 if previous_ciphertext == None:
                     # Create a new root since there was no previous root.
+                    print "inserting root"
                     return self._insert(None, current_ciphertext, None)
                 else:
                     # Insert the original ciphertext, using the previous

### 2013-05-07 communication_channel.py

@@ -35,8 +35,11 @@ class CommunicationChannel:
         self._receive_queue = receive_queue
 
     def put(self, message):
+        print "QUEUE PUT: "+str(message)
         message.message_type._check_valid_message_type()
         return self._send_queue.put(message)
 
     def get(self):
-        return self._receive_queue.get()
+        msg =  self._receive_queue.get()
+        print "QUEUE GET: "+str(msg)
+        return msg

### 2013-05-07 main.py

@@ -27,6 +27,7 @@ for i in range(NUM_INPUTS):
         inp += str(int(random.random()*2))
     inputs.append(inp)
 
+inputs = ["0001"]
 print "Program inputs:", inputs
 
 client_thread = Thread(target=client_function, args=(inputs,))

### 2013-05-07 protocol.py

@@ -7,6 +7,9 @@ class MessageProtocol:
     def __init__(self):
         self.uuid = uuid.uuid4() # generates a random universally unique ID.
 
+    def __str__(self):
+        return "%s(%r)" % (self.__class__, self.__dict__)
+
 # Message which the server sends to the client. Must contain a ciphertext.
 class ServerMessage(MessageProtocol):
     def __init__(self, ciphertext, client_message):

### 2013-05-07 client.py
Incorrect variable name.

@@ -34,7 +34,7 @@ class Client:
                 if previous_ciphertext == None:
                     # Create a new root since there was no previous root.
                     print "inserting root"
-                    return self._insert(None, current_ciphertext, None)
+                    return self._insert(None, original_ciphertext, None)
                 else:
                     # Insert the original ciphertext, using the previous
                     # ciphertext and direction.

### 2013-05-07 main.py
bug fixing

@@ -18,7 +18,7 @@ def server_function():
     while True:
         server.run()
 
-NUM_INPUTS = 50
+NUM_INPUTS = 5
 LEN_INPUTS = 4
 inputs = []
 for i in range(NUM_INPUTS):
@@ -27,7 +27,7 @@ for i in range(NUM_INPUTS):
         inp += str(int(random.random()*2))
     inputs.append(inp)
 
-inputs = ["0001"]
+#inputs = ["0001"]
 print "Program inputs:", inputs
 
 client_thread = Thread(target=client_function, args=(inputs,))

### 2013-05-07 server.py

@@ -130,7 +130,7 @@ def subtree_size(node):
     elif node.right is None:
         return 1 + subtree_size(node.left)
     else:
-        return 1 + sum[subtree_size(node.left), subtree_size(node.right)] 
+        return 1 + subtree_size(node.left) + subtree_size(node.right)
 
 def counter(fn):
     def wrapper(*args, **kwargs):

### 2013-05-07 client.py
started range queries

@@ -1,4 +1,4 @@
-import encryption, protocol, random, dcs
+import encryption, protocol, random, dcs_preprocessing
 
 class Client:
     def __init__(self, communication_channel, dcs=False):
@@ -6,14 +6,26 @@ class Client:
         self.key = self.encryption_scheme.generate_key()
         self.communication_channel = communication_channel
         if dcs:
-            self.dcs_scheme = dcs.DistributionConfidentialityScheme()
+            self.dcs_scheme = dcs_preprocessing.DistributionConfidentialityScheme()
         else:
             self.dcs_scheme = False
 
     def query(self, message):
+        if self.dcs_scheme:
+            message = self.dcs_scheme.encrypt(message)
         ciphertext = self.encryption_scheme.encrypt(self.key, message)
         client_message = protocol.ClientMessage()
         client_message.query(ciphertext)
+        return self._send_client_message(client_message)
+
+    def range_query(self, min_message, max_message):
+        if self.dcs_scheme:
+            min_message = self.dcs_scheme.encrypt_min(min_message)
+            max_message = self.dcs_scheme.encrypt_min(max_message)
+        min_ciphertext = self.encryption_scheme.encrypt(self.key, min_message)
+        max_ciphertext = self.encryption_scheme.encrypt(self.key, max_message)
+        client_message = protocol.ClientMessage()
+        client_message.range_query(ciphertext)
         return self._send_client_message(client_message)
 
     # Stores a plaintext message +message+ in the database by communicating and
@@ -21,8 +33,6 @@ class Client:
     # ciphertext, and this ciphertext will be stored at the server in an order
     # preserving manner.
     def insert_message(self, message):
-        if self.dcs_scheme:
-            message = self.dcs_scheme.encrypt(message)
         original_ciphertext = self.encryption_scheme.encrypt(self.key, message)
         previous_ciphertext = None
         current_ciphertext = self._get_root()
@@ -33,7 +43,6 @@ class Client:
             if current_ciphertext == None:
                 if previous_ciphertext == None:
                     # Create a new root since there was no previous root.
-                    print "inserting root"
                     return self._insert(None, original_ciphertext, None)
                 else:
                     # Insert the original ciphertext, using the previous
@@ -67,16 +76,23 @@ class Client:
         return self._send_client_message(client_message)
 
     def _move_left(self, ciphertext):
+        if self.dcs_scheme:
[…]

### 2013-05-07 dcs_preprocessing.py

@@ -17,6 +17,9 @@ class DistributionConfidentialityScheme:
 
 
 	def encrypt(self, plaintext):
+
+		if not plaintext:
+			return None
 	
 		modified_plaintext = plaintext
 		modification_bit_count = bin(0)[2:].zfill(self.q)
@@ -31,7 +34,18 @@ class DistributionConfidentialityScheme:
 
 		return ciphertext
 
+	# These two functions return the minimum possible encodings of plaintexts.
+	# They are used as upper and lower bounds on a number for executing range queries.
+	def encrypt_min(self, plaintext):
+		pass
+
+	def encrypt_max(self, plaintext):
+		pass
+
 	def decrypt(self, ciphertext):
+
+		if not ciphertext:
+			return None
 		
 		non_random_ciphertext =  ciphertext[:len(ciphertext) - self.r]
 		modified_plaintext = non_random_ciphertext[:len(non_random_ciphertext) - self.q]

### 2013-05-07 main.py

@@ -5,12 +5,12 @@ import communication_channel, protocol, client, server
 factory = communication_channel.CommunicationFactory()
 server_channel = factory.build_for("server")
 client_channel = factory.build_for("client")
-client = client.Client(client_channel)
+client = client.Client(client_channel, dcs=False)
 server = server.Server(server_channel)
 
 def client_function(inputs):
-    for current_input in inputs:
-        print "Inserting input %s" % current_input
+    for index, current_input in enumerate(inputs):
+        print "\nInserting input %s (%s)" % (current_input, index)
         client.insert_message(current_input)
 
 
@@ -18,7 +18,7 @@ def server_function():
     while True:
         server.run()
 
-NUM_INPUTS = 5
+NUM_INPUTS = 50
 LEN_INPUTS = 4
 inputs = []
 for i in range(NUM_INPUTS):
@@ -32,6 +32,9 @@ print "Program inputs:", inputs
 
 client_thread = Thread(target=client_function, args=(inputs,))
 server_thread = Thread(target=server_function)
-client_thread.start()
-server_thread.start()
+try:
+    client_thread.start()
+    server_thread.start()
+except (KeyboardInterrupt, SystemExit):
+    sys.exit()
 

### 2013-05-07 protocol.py

@@ -39,6 +39,8 @@ class ClientMessage(MessageProtocol):
         self.ciphertext = None
         self.new_ciphertext = None
         self.insert_direction = None
+        self.min_ciphertext = None
+        self.max_ciphertext = None
 
     def move_left(self, ciphertext):
         self.message_type = MessageType("move_left")
@@ -62,6 +64,11 @@ class ClientMessage(MessageProtocol):
         self.message_type = MessageType("query")
         self.ciphertext = ciphertext
 
+    def range_query(self, min_ciphertext, max_ciphertext):
+        self.message_type = MessageType("range_query")
+        self.min_ciphertext = min_ciphertext
+        self.max_ciphertext = max_ciphertext
+
     def _check_insert_direction(self):
         if not (self.insert_direction == 'left' or self.insert_direction == 'right' or self.insert_direction == None):
            raise Exception("'%s' is not a valid insert direction" % self.insert_direction)
@@ -70,7 +77,6 @@ class ClientMessage(MessageProtocol):
 # server. It contains a whitelist of valid message types. Checking the type of
 # the object is as easy as checking +type+ on the object.
 class MessageType:
-    valid_message_types = ["move_left", "move_right", "get_root", "insert", "query"]
 
     def __init__(self, message_type):
         self._message_type = message_type
@@ -83,5 +89,5 @@ class MessageType:
         return self._message_type        
 
     def _check_valid_message_type(self):
-        if self._message_type not in ["move_left", "move_right", "get_root", "insert", "query"]:
+        if self._message_type not in ["move_left", "move_right", "get_root", "insert", "query", "range_query"]:
             raise Exception("'%s' is not a valid message type" % message_type)

### 2013-05-07 server.py

@@ -53,6 +53,7 @@ class Server:
     Server response to a client message.
     '''
     def receive(self, client_message):
+        #print "KEYS: " + str(self.fake_ope_table)
         self.learner.process_message(client_message)
 
         if (client_message.message_type.__repr__() == protocol.MessageType("move_left").__repr__()):
@@ -177,13 +178,15 @@ def right_rotate(node):
         B.parent.right = B
 
 '''
-rebalance.heights will return the subtree_sizes of every rebalance,
-allowing us to figure out the speed of our insertion procedure.
-len(rebalance.heights) is the number of rebalances.
+rebalance.subtree_sizes will return the subtree_sizes of every rebalance,
+allowing us to figure out the speed of our insertion procedure (since each
+rebalance needs to re-encode each of the nodes in the subtree).
+len(rebalance.subtree_sizes) is the number of rebalances.
 '''
 @counter
 def rebalance(node):
-    print "rebalancing"
+    print "Rebalance count: " + str(rebalance.subtree_sizes)
+    print "Rebalance time: " + str(sum(rebalance.subtree_sizes))
     if balance_factor(node) == -2:
         if balance_factor(node.right) == -1: # right-right case
             left_rotate(node)

### 2013-05-07 server.py
DCS hack

@@ -49,6 +49,18 @@ class Server:
     def start(self):
         threading.Timer(1, self.run()).start()
 
+    # HACK that allows us to use DCS with the fake OPE table. Actually 
+    # just compares the "plaintext" portions of the ciphertext. Will
+    # break with a real encryption scheme -- use real OPE tables!
+    def DCS_hack(self, client_message):
+        if client_message.ciphertext not in self.fake_ope_table.keys():
+            for key in self.fake_ope_table.keys():
+                if key[:5] == client_message.ciphertext[:5]:
+                    current = self.fake_ope_table[key]
+        else:
+            current = self.fake_ope_table[client_message.ciphertext]
+        return current or None
+
     '''
     Server response to a client message.
     '''
@@ -57,14 +69,16 @@ class Server:
         self.learner.process_message(client_message)
 
         if (client_message.message_type.__repr__() == protocol.MessageType("move_left").__repr__()):
-            left_child = self.fake_ope_table[client_message.ciphertext].left
+            current = self.DCS_hack(client_message)
+            left_child = current.left
             if left_child:
                 server_message = protocol.ServerMessage(ciphertext=left_child.value, client_message=client_message)
             else:
                 server_message = protocol.ServerMessage(ciphertext=None, client_message=client_message)
 
         elif (client_message.message_type.__repr__() == protocol.MessageType("move_right").__repr__()):
-            right_child = self.fake_ope_table[client_message.ciphertext].right
+            current = self.DCS_hack(client_message)
+            right_child = current.right
             if right_child:
                 server_message = protocol.ServerMessage(ciphertext=right_child.value, client_message=client_message)
             else:
@@ -84,7 +98,8 @@ class Server:
                 self.root = new_node
                 self.fake_ope_table[client_message.new_ciphertext] = self.root
             else:
-                node = self.fake_ope_table[client_message.ciphertext]
+                node = self.DCS_hack(client_message)
+                #node = self.fake_ope_table[client_message.ciphertext]
                 new_node.parent = node
                 if (client_message.insert_direction == "left"):
                     node.left = new_node
@@ -108,6 +123,17 @@ class Server:
     def update_root(self):
         while (self.root.parent != None):
             self.root = self.root.parent
+
+    def pad(self, value):
+        if (len(value) < ENC_LEN):
+            value += "1"
+        while (len(value) < ENC_LEN):
+            value += "0"
+        return value
+
+    def unpad(self, value):
[…]

### 2013-05-07 paper.tex
Working on DCS scheme for the paper.

--- 2013-05-02 paper.tex
@@
 \maketitle
+
+\section{Distribution Confidentiality Scheme}
+
+In order to solve the problem of leaking the distribution of the plaintext values, we have developed the Distribution Confidentiality Scheme (DCS).
+This scheme uses Raluca et al (2013)'s original mOPE scheme, but adds an additional layer of security.
+
+In essence, the DCS scheme adds random bits to the end of a plaintext so that the ciphertext values are randomized.
+This will prevent the server from being able to identify the number of times a repeated plaintext value is inserted.
+
+\subsection{Description of DCS}
+
+This section will give a formal description of DCS. We will first describe the basic version of the scheme, then we will augment it so that decimal numbers can be represented as well.
+
+In the basic version of the scheme, let us assume that we want to encrypt some plaintext value $x \in \mathrm{Z}$ and send it to the server like in Raluca et al (2013)'s mOPE scheme.
+For DCS, there is an additional parameter $\rho$ which will govern the probability with which the server sees a repeated value.
+We will generate a random value $r \in [0,1)$ which contains $\rho$ bits, denoted $r_{\rho}$, and append it to the end of $x$.
+The resulting value $x' = x + r_{\rho}$ will be encrypted with DET.
+Raluca et al (2013)'s mOPE scheme will work the same as before, but now acting on $x'$.
+
+When the client attempts to query for $x$, he must perform a range query for $[x, x+1)$ on the server.
+
+\subsection{Querying Under DCS}
 
@@
 However, if $p_i = p^*$, then the client tells the server to move left or right with uniform probability.
+Note that in this scheme, we will use a randomized encryption scheme so that the server cannot tell if two plaintext values are the same.
 
@@
 
-  \subsection{Equivalence of RTOPE and DCS}
+\section{Equivalence of DCS and RTOPE}
 
@@
 Instead, we will use a notion of the equivalence of the distributions of the encodings.
-Formally, we define equivalence as follows:
+We will now formally define equivalence.
+
+  \subsection{Equivalence}
 
@@
 \end{proof}
+
+  \subsection{Equivalence of DCS and RTOPE}
 

### 2013-05-07 paper.tex
Working on the paper.

@@
 
-When the client attempts to query for $x$, he must perform a range query for $[x, x+1)$ on the server.
+Inserting in this scheme is simple, since nothing really has to be changed from Raluca et al (2013)'s mOPE scheme.
+The client will take the value $x$ to insert, create $x'$, then encrypt $x'$ to obtain a ciphertext.
+Inserting this ciphertext will involve moving down the server's binary search tree.
+The insertion process is started by the client acquiring the root node.
+The client then checks to see if $x'$ is larger or smaller than the root's decrypted value.
+This informs the client as to the direction in which it should move.
+Once it arrives at a leaf node, the client will insert the new ciphertext in the correct direction.
+
+\begin{figure}
+\lstset{language=Python}
+\begin{lstlisting}
+  TODO: Insert the insertion pseudocode here.
+\end{lstlisting}
+\caption{Pseudocode for the Insertion Algorithm}
+\label{insertion_figure}
+\end{figure}
+
+Querying, however, gets more difficult, and the next section will discuss how the client can query for some value $y$.
 

### 2013-05-08 client.py
start debugging non-dcs failure

@@ -18,6 +18,7 @@ class Client:
         client_message.query(ciphertext)
         return self._send_client_message(client_message)
 
+    '''
     def range_query(self, min_message, max_message):
         if self.dcs_scheme:
             min_message = self.dcs_scheme.encrypt_min(min_message)
@@ -27,6 +28,7 @@ class Client:
         client_message = protocol.ClientMessage()
         client_message.range_query(ciphertext)
         return self._send_client_message(client_message)
+    '''
 
     # Stores a plaintext message +message+ in the database by communicating and
     # interacting with the server. The plaintext will be encrypted into a

### 2013-05-08 communication_channel.py

@@ -35,11 +35,11 @@ class CommunicationChannel:
         self._receive_queue = receive_queue
 
     def put(self, message):
-        #print "QUEUE PUT: "+str(message)
+        print "QUEUE PUT: "+str(message)
         message.message_type._check_valid_message_type()
         return self._send_queue.put(message)
 
     def get(self):
         msg =  self._receive_queue.get()
-        #print "QUEUE GET: "+str(msg)
+        print "QUEUE GET: "+str(msg)
         return msg

### 2013-05-08 main.py

@@ -13,10 +13,16 @@ def client_function(inputs):
         print "\nInserting input %s (%s)" % (current_input, index)
         client.insert_message(current_input)
 
-
 def server_function():
     while True:
         server.run()
+
+def monitor_queue():
+    while True:
+        time.sleep(1)
+        for element in client_channel._send_queue:
+            print element
+        #print client_channel._receive_queue
 
 NUM_INPUTS = 50
 LEN_INPUTS = 4
@@ -27,14 +33,16 @@ for i in range(NUM_INPUTS):
         inp += str(int(random.random()*2))
     inputs.append(inp)
 
-#inputs = ["0001"]
+inputs = ['1100', '1001', '0110', '0000', '0101', '0111', '0010', '1001', '1100', '0011', '0110', '1011', '1111', '1111', '0001', '0101', '0111', '1011', '1111', '1110', '0111', '1001', '1101', '0110', '0000', '0001', '0010', '0000', '0000', '1000', '0111', '1011', '1100', '0111', '1001', '0001', '1100', '0000', '1011', '0001', '1100', '1111', '0110', '1000', '0101', '0010', '1110', '1100', '0101', '0011']
 print "Program inputs:", inputs
 
 client_thread = Thread(target=client_function, args=(inputs,))
 server_thread = Thread(target=server_function)
-try:
-    client_thread.start()
-    server_thread.start()
-except (KeyboardInterrupt, SystemExit):
-    sys.exit()
+queue_thread = Thread(target=monitor_queue)
+
+client_thread.start()
+server_thread.start()
+queue_thread.start()
+
+
 

### 2013-05-08 protocol.py

@@ -39,8 +39,8 @@ class ClientMessage(MessageProtocol):
         self.ciphertext = None
         self.new_ciphertext = None
         self.insert_direction = None
-        self.min_ciphertext = None
-        self.max_ciphertext = None
+        #self.min_ciphertext = None
+        #self.max_ciphertext = None
 
     def move_left(self, ciphertext):
         self.message_type = MessageType("move_left")

### 2013-05-08 server.py

@@ -54,10 +54,12 @@ class Server:
     # break with a real encryption scheme -- use real OPE tables!
     def DCS_hack(self, client_message):
         if client_message.ciphertext not in self.fake_ope_table.keys():
+            print "DCS HACKING"
             for key in self.fake_ope_table.keys():
                 if key[:5] == client_message.ciphertext[:5]:
                     current = self.fake_ope_table[key]
         else:
+            
             current = self.fake_ope_table[client_message.ciphertext]
         return current or None
 

### 2013-05-08 communication_channel.py
DCS AND RTOPE WORK KINDA WOO GOOD ENOUGH FOR DEMO

@@ -35,11 +35,11 @@ class CommunicationChannel:
         self._receive_queue = receive_queue
 
     def put(self, message):
-        print "QUEUE PUT: "+str(message)
+        #print "QUEUE PUT: "+str(message)
         message.message_type._check_valid_message_type()
         return self._send_queue.put(message)
 
     def get(self):
         msg =  self._receive_queue.get()
-        print "QUEUE GET: "+str(msg)
+        #print "QUEUE GET: "+str(msg)
         return msg

### 2013-05-08 main.py

@@ -5,7 +5,7 @@ import communication_channel, protocol, client, server
 factory = communication_channel.CommunicationFactory()
 server_channel = factory.build_for("server")
 client_channel = factory.build_for("client")
-client = client.Client(client_channel, dcs=False)
+client = client.Client(client_channel, dcs=True)
 server = server.Server(server_channel)
 
 def client_function(inputs):
@@ -24,7 +24,7 @@ def monitor_queue():
             print element
         #print client_channel._receive_queue
 
-NUM_INPUTS = 50
+NUM_INPUTS = 500
 LEN_INPUTS = 4
 inputs = []
 for i in range(NUM_INPUTS):
@@ -33,7 +33,8 @@ for i in range(NUM_INPUTS):
         inp += str(int(random.random()*2))
     inputs.append(inp)
 
-inputs = ['1100', '1001', '0110', '0000', '0101', '0111', '0010', '1001', '1100', '0011', '0110', '1011', '1111', '1111', '0001', '0101', '0111', '1011', '1111', '1110', '0111', '1001', '1101', '0110', '0000', '0001', '0010', '0000', '0000', '1000', '0111', '1011', '1100', '0111', '1001', '0001', '1100', '0000', '1011', '0001', '1100', '1111', '0110', '1000', '0101', '0010', '1110', '1100', '0101', '0011']
[…]

### 2013-05-08 server.py

@@ -1,4 +1,4 @@
-import protocol, communication_channel, client, time, threading
+import protocol, communication_channel, client, time, threading, random
 
 class Server:
 
@@ -54,14 +54,19 @@ class Server:
     # break with a real encryption scheme -- use real OPE tables!
     def DCS_hack(self, client_message):
         if client_message.ciphertext not in self.fake_ope_table.keys():
-            print "DCS HACKING"
+            #print "DCS HACKING"
             for key in self.fake_ope_table.keys():
                 if key[:5] == client_message.ciphertext[:5]:
-                    current = self.fake_ope_table[key]
+                    possible_nodes = self.fake_ope_table[key]
         else:
-            
-            current = self.fake_ope_table[client_message.ciphertext]
-        return current or None
+            # another hack to get non-dcs to work. basically, when we repeat keys,
+            # we overwrite the ciphertext->node mapping in fake_ope_table. this 
+            # causes problems and makes us get stuck in an infinite loop.
+            possible_nodes = self.fake_ope_table[client_message.ciphertext]
+
+        index = int(random.random()*len(possible_nodes))
+        node = possible_nodes[index]
+        return node or None
 
     '''
     Server response to a client message.
@@ -98,16 +103,21 @@ class Server:
             # root case
             if client_message.ciphertext == None:
                 self.root = new_node
-                self.fake_ope_table[client_message.new_ciphertext] = self.root
+                if client_message.new_ciphertext in self.fake_ope_table.keys():
+                    self.fake_ope_table[client_message.new_ciphertext] += [self.root]
+                else:
+                    self.fake_ope_table[client_message.new_ciphertext] = [self.root]
             else:
                 node = self.DCS_hack(client_message)
-                #node = self.fake_ope_table[client_message.ciphertext]
                 new_node.parent = node
                 if (client_message.insert_direction == "left"):
                     node.left = new_node
                 elif (client_message.insert_direction == "right"):
                     node.right = new_node
-                self.fake_ope_table[client_message.new_ciphertext] = new_node
+                if client_message.new_ciphertext in self.fake_ope_table.keys():
+                    self.fake_ope_table[client_message.new_ciphertext] += [new_node]
+                else:
+                    self.fake_ope_table[client_message.new_ciphertext] = [new_node]
                 # AVL rebalance
                 while (node and node.parent):
                     rebalance(node.parent)

### 2013-05-09 paper.tex
Working on paper.

@@
 
-\section{Equivalence of DCS and RTOPE}
+\section{Relationship Between DCS and RTOPE}
 
@@
 
-  \subsection{Equivalence}
+  \subsection{Expectational Equivalence}
 
@@
 For DCS, one can see that moving left or right from the root element depends on the relative size of the root element with the new element being inserted or queried.
+For example, if $x$ is the value of a repeated plaintext, then DCS will mutate $p$ into $p + r$ where $r \in [0,1)$ are some random bits.
+Moving left at the root means that $p_1 < p_r$ where $p_r$ is the root value.
+This means that $p + r_1 < p + r_r$, which is equivalent to saying $r_1 < r_r$.
+Thus, moving left at the root is just the probability that the random number $r_1$ is smaller than the random number $r_r$ picked at the root.
+
+  Now let us examine some series of moves down the tree when attempting to query or insert some node with plaintext value $x$, denoted by the sequence
+  \begin{eqnarray}
+    \{ m_0(x), m_1(x), \ldots, m_k(x) \}
+  \end{eqnarray}
+
+  We shall drop the $x$ for convenience and commonly refer to moves as $m_i$. We see that $m_i$ can take on two possibilities, 0 for left or 1 for moving right, and we can characterize the moves:
+  \begin{eqnarray}
+    m_i(x) = \left\{ \begin{array}{l l}
+        0 & \textrm{if } p_i > x \\
+        1 & \textrm{else}
+  \end{eqnarray}
+
+  Here $p_i$ is the underlying plaintext value of the node at the $i$th move.
+
+  We shall proceed to show that the two schemes actually produce the same expected tree. In order to do this, we first prove a lemma.
+  \begin{lemma}
+    Let $\{X_i\}_{i=1}^n$ be a sequence of $n$ independent uniform random variables chosen from the interval $[0,1)$.
+Let $X_{n+1}$ be another uniform random varaible on the interval $[0,1)$.
+The probability that $x_{n+1}$ is the $j$th smallest item is $1/(n+1)$.
+  \end{lemma}
+  \begin{proof}
+    For the proof, we rely on the fact that the $n$ random variables are independent.
+We note that the $n+1$st random variable can be thought of as the next random variable in the sequence.
+Moreover, since all of the random variables are independently drawn from the same uniform distribution, we see that we are really drawing a set of $n+1$ uniform random variables which can be chosen at the same time.
+
+    It is clear that the probability of any $x_i$ being the $j$th smallest item is the same, because all of the random variables are drawn independently.
+This means that $Pr[X_{n+1} = S_j]$ were $S_j$ is the $j$th smallest item can be given by the expression:
+    \begin{eqnarray}
+      Pr[X_{n+1} = S_j] = Pr[X_{n} = S_j] = \ldots = Pr[X_{1} = S_j]
+    \end{eqnarray}
+
+    For all values of $j \in \{1, \ldots, n+1\}$.
+Since exactly one $x_i$ is the $j$th smallest element, we see that $\sum_{i=1}^{n+1} Pr[X_i = X_j] = 1$.
+This implies that $Pr[X_i = S_j] = 1/(n+1)$ which further implies that $Pr[X_{n+1} = S_j] = 1/(n+1)$ for all $j$.
+This completes the proof.
+  \end{proof}
+
+  This lemma allows us to show that DCS and RTOPE have identical move distributions, which will show that the two schemes have the same expected tree structure.
+
+  \begin{table}
+    \begin{tabular}{l | c | c | c | c | c | c}
+      Trials & 10 & 20 & 50 & 100 & 200 & 500 \\
+      \hline \hline
+      1000 & 0.111 & 0.122 & 0.179 & 0.249 & 0.363 & 0.537 \\
+      5000 & 0.093 & 0.062 & 0.075 & 0.104 & 0.162 & 0.241 \\
+     10000 & 0.089 & 0.059 & 0.055 & 0.071 & 0.106 & 0.176 \\
+     50000 & 0.090 & 0.047 & 0.028 & 0.037 & 0.052 & 0.077 \\
+    100000 & 0.090 & 0.047 & 0.021 & 0.026 & 0.033 & 0.059 \\
+    200000 & 0.091 & 0.047 & 0.021 & 0.018 & 0.022 & 0.040 \\
+    500000 & 0.091 & 0.047 & 0.019 & 0.013 & 0.017 & 0.025 \\
+   1000000 & 0.090 & 0.047 & 0.019 & 0.011 & 0.011 & 0.017 \\
+    \end{tabular}
+    \caption{Tests}
+  \end{table}
 

### 2013-05-09 paper.tex
Clearing up the equivalence theorem.

@@
 
-  \subsection{Expectational Equivalence}
+  \subsection{Structural Expectation Equivalence}
 
-  \emph{Definition:} Two OPE schemes $x,y$ are equivalent if for each plaintext $p_i$ that scheme $x$ encodes in a sequence of plaintexts $P = \{p_i\}_{i=1}^n$, there exists some bijective mapping $f: \mathrm{Z}_y \to \mathrm{Z}_x$ where $Pr[Encode_x(c_i) = \omega] = Pr[f(Encode_y(c_i)) = \omega]$ for all $\omega \in \mathrm{Z}_x$ where $\mathrm{Z}_x$ is the space of all possible OPE encodings for scheme $x$, $c_i = Enc(SK, p_i)$ is the ciphertext corresponding to $p_i$, and $Encode_x(c_i)$ and $Encode_y(c_i)$ are the functions that obtain the OPE encoding for schemes $x$ and $y$ respectively.
+  \emph{Definition:} Two OPE schemes $x,y$ are \emph{Structural Expectation Equivalent} if for each plaintext $p_i$ that scheme $x$ encodes in a sequence of plaintexts $P = \{p_i\}_{i=1}^n$, there exists some bijective mapping $f: \mathrm{Z}_y \to \mathrm{Z}_x$ where $Pr[Encode_x(c_i) = \omega] = Pr[f(Encode_y(c_i)) = \omega]$ for all $\omega \in \mathrm{Z}_x$ where $\mathrm{Z}_x$ is the space of all possible OPE encodings for scheme $x$, $c_i = Enc(SK, p_i)$ is the ciphertext corresponding to $p_i$, and $Encode_x(c_i)$ and $Encode_y(c_i)$ are the functions that obtain the OPE encoding for schemes $x$ and $y$ respectively.
 
-  In other words, for two schemes to be equivalent, there must exist a mapping $f$ from all of the possible OPE encodings from scheme $x$ to scheme $y$, where the probability of obtaining an encoding in $x$ is the same as the probability of obtaining the corresponding encoding in $y$ (based on the mapping).
+  In other words, for two schemes to be structurally expectation equivalent, there must exist a mapping $f$ from all of the possible OPE encodings from scheme $x$ to scheme $y$, where the probability of obtaining an encoding in $x$ is the same as the probability of obtaining the corresponding encoding in $y$ (based on the mapping).
 This must be the case for all possible encodings.
 
-  This notion of equivalence encompasses a number of useful features.
-In particular, notice that if $x$ is an OPE encoding scheme which is IND-CPDA secure, and $y$ is equivalent to $x$, then $y$ is also IND-CPDA secure.
-Due to this notion, it is sufficient to show the equivalence of two schemes in order to link the IND-CPDA security of the schemes (the proof of this property is given in the theorem below).
-Another observation one can make is that the mapping in the equivalence definition is bijective.
-Hence, if $x$ is equivalent to $y$, then $y$ is necessarily equivalent to $x$ because one can simply use $f^{-1}$ as the mapping, which necessarily exists because of $f$ being bijective.
+  This notion of structural expectation equivalence encompasses a number of useful features.
+In particular, notice that if $x$ is an OPE encoding scheme which is IND-CPDA secure, and $y$ is structurally expectation equivalent to $x$, then $y$ is also IND-CPDA secure.
+Due to this notion, it is sufficient to show the structural expectation equivalence of two schemes in order to link the IND-CPDA security of the schemes (the proof of this property is given in the theorem below).
+Another observation one can make is that the mapping in the structural expectation equivalence definition is bijective.
+Hence, if $x$ is structurally expectation equivalent to $y$, then $y$ is necessarily structurally expectation equivalent to $x$ because one can simply use $f^{-1}$ as the mapping, which necessarily exists because of $f$ being bijective.
 
 \begin{theorem}
- If two OPE schemes $x,y$ are equivalent, then $x$ is IND-CPDA secure if and only if $y$ is IND-CPDA secure.
+ If two OPE schemes $x,y$ are structurally expectation equivalent, then $x$ is IND-CPDA secure if and only if $y$ is IND-CPDA secure.
 \end{theorem}
@@
 
-  \subsection{Equivalence of DCS and RTOPE}
+  \subsection{Structural Expectation Equivalence of DCS and RTOPE}
 
@@
 
+  \begin{theorem}
+    DCS and RTOPE are structurally expectation equivalent as the number of nodes $N$ and repetitions of value $x$, $R(x)$, both go to $\infty$, for all $x$ such that $R(x) > 1$.
+  \end{theorem}
+  \begin{proof}
+    We shall prove this theorem by examining a sequence of moves when looking at the insertion of a repeated value $x$.
+If we can show that the probability of traversing the tree in a particular sequence $\{m_i \}_{i=1}^k$ is the same in both DCS and RTOPE when both schemes start with the same tree, then the two schemes can be shown to be structurally expectation equivalent.
+    Denote $x$ as the repeated value to insert.
+In DCS, to move right so that $m_i = 1$, one must have $p_i < x + r$.
+To move right, one must have $p_i > x + r$.
+Although there exists a sequence of moves from the root to a leaf of the tree which includes every node in the tree, we need only examine the nodes which have a plaintext value equal to $x$ (before the addition of the random bit).
+This is because the traversal of DCS and RTOPE is the same for nodes which are not repeated (they share the normal binary tree traversal rule).
+Thus, we know that the moves in these cases will be equivalent and the probability of making the moves on non-repeated nodes will be equal.
+    Thus, we can reduce our problem to considering a sequence of moves \{$m_i\}_{i=1}^k$ on the plaintext values which are equal to $x$.
+If we can show that the probability of making a particular sequence of moves on the repeated values is the same for DCS and RTOPE, then we will be done.
+  \end{proof}
+
+  \subsection{Slow Convergence}
+
   \begin{table}
@@
     \end{tabular}
-    \caption{Tests}
+    \caption{Average Differences of Expected and Realized Rank}
   \end{table}

### 2013-05-09 order_stats.py
Adding the order stats script for doing tests on order statistics.

@@ -1,0 +1,48 @@
+# Test code to check that if you have a sequence of n random numbers [0,1], then
+# the n+1st number you draw has equal likelihood of being any rank.
+
+import random
+import matplotlib.pyplot as plt
+
+def generate_sequence(n):
+    sequence = []
+    for i in xrange(n):
+        sequence.append(random.random())
+    return sequence
+
+def find_rank(x, sequence):
+    rank = 0
+    for i in sequence:
+        if i < x:
+            rank += 1
+    return rank
+
+def test_rank_of_last(n):
+    sequence = generate_sequence(n)
+    x = random.random()
+
+    return find_rank(x, sequence)
+
+def test_distribution(num_trials, sequence_length):
+    rank_dist = {}
+    for i in xrange(num_trials):
+        rank = test_rank_of_last(sequence_length)
+        frequency = rank_dist.get(rank, 0)
+        rank_dist[rank] = frequency + 1
+
+    # flatten the dictionary
+    expected_value = (num_trials * 1.0 / sequence_length)
+    ranks = [rank_dist.get(i, 0) for i in xrange(sequence_length)]
+    difference_from_expected = [abs(rank_dist.get(i, 0) - expected_value) / expected_value for i in xrange(sequence_length)]
+
+    return sum(difference_from_expected) / len(difference_from_expected)
+
+if __name__ == '__main__':
+    test_trials = [5000000] #, 5000, 10000, 50000, 100000, 200000, 500000]
+    sequence_lengths = [10, 20, 50, 100, 200, 500]
+    for trials in test_trials:
+        row = [trials]
+        for length in sequence_lengths:
+            row.append(test_distribution(trials, length))
+
+        print ' & '.join([str(i) for i in row])

### 2013-05-09 paper.tex
Fuck, DCS and RTOPE aren't equivalent at all.

@@
   \begin{theorem}
-    DCS and RTOPE are structurally expectation equivalent as the number of nodes $N$ and repetitions of value $x$, $R(x)$, both go to $\infty$, for all $x$ such that $R(x) > 1$.
+    DCS and RTOPE are not structurally expectation equivalent.
   \end{theorem}
@@
     We shall prove this theorem by examining a sequence of moves when looking at the insertion of a repeated value $x$.
-If we can show that the probability of traversing the tree in a particular sequence $\{m_i \}_{i=1}^k$ is the same in both DCS and RTOPE when both schemes start with the same tree, then the two schemes can be shown to be structurally expectation equivalent.
-    Denote $x$ as the repeated value to insert.
 In DCS, to move right so that $m_i = 1$, one must have $p_i < x + r$.
-To move right, one must have $p_i > x + r$.
+To move left, one must have $p_i > x + r$.
 Although there exists a sequence of moves from the root to a leaf of the tree which includes every node in the tree, we need only examine the nodes which have a plaintext value equal to $x$ (before the addition of the random bit).
@@
 Thus, we know that the moves in these cases will be equivalent and the probability of making the moves on non-repeated nodes will be equal.
+
     Thus, we can reduce our problem to considering a sequence of moves \{$m_i\}_{i=1}^k$ on the plaintext values which are equal to $x$.
 If we can show that the probability of making a particular sequence of moves on the repeated values is the same for DCS and RTOPE, then we will be done.
+Making any sequence of moves on repeated values in RTOPE will have probability $2^{-k}$ where $k$ is the number of repeated value in the sequence down the tree.
+This is becase one moves left or right with probability $\frac{1}{2}$.
+
+    Now we shall examine the sequence of moves in DCS.
+Recall that we need only consider a sequence of moves $\{m_i\}^{i=1}^k$ which is performed on a single repeated plaintext value $x$.
+This means that in DCS, the plaintext values will be distinguished by the random bit $r_i$ so that $p_i = x + r_i$.
+Therefore, we need only compare $r_i$ to the value $r_{k+1}$ that we are querying.
+
+      \end{proof}
   \end{proof}

### 2013-05-10 paper.tex
Finished writing about the non-equivalence.

@@
 \begin{figure}
-\lstset{language=Python}
-\begin{lstlisting}
-  TODO: Insert the insertion pseudocode here.
-\end{lstlisting}
-\caption{Pseudocode for the Insertion Algorithm}
-\label{insertion_figure}
+%\lstset{language=Python}
+%\begin{lstlisting}
+%  TODO: Insert the insertion pseudocode here.
+%\end{lstlisting}
+%\caption{Pseudocode for the Insertion Algorithm}
+%\label{insertion_figure}
 \end{figure}
@@
         1 & \textrm{else}
+    \end{array} \right.
   \end{eqnarray}
@@
 
-  We shall proceed to show that the two schemes actually produce the same expected tree. In order to do this, we first prove a lemma.
-  \begin{lemma}
-    Let $\{X_i\}_{i=1}^n$ be a sequence of $n$ independent uniform random variables chosen from the interval $[0,1)$.
-Let $X_{n+1}$ be another uniform random varaible on the interval $[0,1)$.
-The probability that $x_{n+1}$ is the $j$th smallest item is $1/(n+1)$.
-  \end{lemma}
-  \begin{proof}
-    For the proof, we rely on the fact that the $n$ random variables are independent.
-We note that the $n+1$st random variable can be thought of as the next random variable in the sequence.
-Moreover, since all of the random variables are independently drawn from the same uniform distribution, we see that we are really drawing a set of $n+1$ uniform random variables which can be chosen at the same time.
-
-    It is clear that the probability of any $x_i$ being the $j$th smallest item is the same, because all of the random variables are drawn independently.
-This means that $Pr[X_{n+1} = S_j]$ were $S_j$ is the $j$th smallest item can be given by the expression:
-    \begin{eqnarray}
-      Pr[X_{n+1} = S_j] = Pr[X_{n} = S_j] = \ldots = Pr[X_{1} = S_j]
-    \end{eqnarray}
-
-    For all values of $j \in \{1, \ldots, n+1\}$.
-Since exactly one $x_i$ is the $j$th smallest element, we see that $\sum_{i=1}^{n+1} Pr[X_i = X_j] = 1$.
-This implies that $Pr[X_i = S_j] = 1/(n+1)$ which further implies that $Pr[X_{n+1} = S_j] = 1/(n+1)$ for all $j$.
-This completes the proof.
-  \end{proof}
-
-  This lemma allows us to show that DCS and RTOPE have identical move distributions, which will show that the two schemes have the same expected tree structure.
+  We shall proceed to show that the two schemes do not produce the same expected tree.
 
@@
     Now we shall examine the sequence of moves in DCS.
-Recall that we need only consider a sequence of moves $\{m_i\}^{i=1}^k$ which is performed on a single repeated plaintext value $x$.
+Recall that we need only consider a sequence of moves $\{m_i\}_{i=1}^k$ which is performed on a single repeated plaintext value $x$.
 This means that in DCS, the plaintext values will be distinguished by the random bit $r_i$ so that $p_i = x + r_i$.
-Therefore, we need only compare $r_i$ to the value $r_{k+1}$ that we are querying.
+Therefore, we need only compare $r_i$ to the value $r^*$, where $r^*$ is the random part of the new plaintext we are inserting.
 
-      \end{proof}
+    The probability that we make a series of moves $\{m_i\}_{i=1}^k$ is the probability that $r^*$ has the $j$ and $j+1$st smallest elements in the sequence of random values $\{ r_i\}_{i=1}^k$.
+Let $n = R(x)$ be the total number of repeated values of $x$.
+
+    It is well known that the probability that the $j$th smallest element falling in the interval $[u, u + du]$ is given by:
+    \begin{eqnarray}
+      \frac{n!}{(j-1)!(n-j)!} u^{j-1} (1-u)^{n-j} du
+    \end{eqnarray}
+
+    Therefore, the probability that $r^*$ falls between the $j$th and $j+1$st value is just the difference between all potential values $u_1$ of the $j$th smallest element and all potential values $u_2$ of the $j+1$st element.
+This is:
+    \begin{eqnarray}
+      \int_{0}^1 \int_0^{u_2} Pr[U_2 = u_2] Pr[U_1 = u_1] Pr[u_1 < r^* < u_2] d_{u_1} d_{u_2}
+    \end{eqnarray}
+
+    Where we take $U_1$ as the $j$th smallest value and $U_2$ as the $j+1$st smallest value.
+Thus, the probability of $r^*$ falling in that interval is the integral over all possible values of $U_2$ and $U_1$, and the probabilitiy that it falls inside of the that interval.
+Since $Pr[u_1 < r^* < u_2] = (u_2 - u_1)$, we can write the above as:
+
+    \begin{eqnarray}
+      \int_{0}^1 \int_0^{u_2} \left( \frac{n!}{j!(n-j-1)!} u_2^j (1 - u_2)^{n-j-1} \right) \left( \frac{n!}{(j-1)!(n-j)!} u_1^{j-1} (1 - u_1)^{n-j} \right) (u_2 - u_1) d_{u_1} d_{u_2}
+    \end{eqnarray}
+
+    Letting $C(j) = \frac{n!}{j!(n-j-1)!} \frac{n!}{(j-1)!(n-j)!}$, and integrating the epression for $u_1$, we can obtain the following result:
+    \begin{eqnarray}
+      C(j) \int_0^1 u_2^j (1 - u_2)^{n-j-1} \left( \frac{(u_2 (n+1) - j) B(j, n-j+1) + u_2^j (1-u_2)^{n-j+1}}{n+1} \right) d u_2
+    \end{eqnarray}
+
+    The above is the probability that $r^*$ falls between the $j$th and $j+1$st values. Simulating this in the figure below, it is clear that this is not uniform for all values of $j$ (like RTOPE is).
+
+    \begin{figure}[H]
+      \centering
+      \includegraphics[width=3in]{ball_result.png}
+      \caption{Probability of $r^*$ falling between the $j$th and $j+1$st largest values in the sequence $\{r_i\}_{i=1}^n$}
+    \end{figure}
   \end{proof}
 
-  \subsection{Slow Convergence}
-
-  \begin{table}
-    \begin{tabular}{l | c | c | c | c | c | c}
-      Trials & 10 & 20 & 50 & 100 & 200 & 500 \\
-      \hline \hline
-      1000 & 0.111 & 0.122 & 0.179 & 0.249 & 0.363 & 0.537 \\
-      5000 & 0.093 & 0.062 & 0.075 & 0.104 & 0.162 & 0.241 \\
-     10000 & 0.089 & 0.059 & 0.055 & 0.071 & 0.106 & 0.176 \\
-     50000 & 0.090 & 0.047 & 0.028 & 0.037 & 0.052 & 0.077 \\
-    100000 & 0.090 & 0.047 & 0.021 & 0.026 & 0.033 & 0.059 \\
-    200000 & 0.091 & 0.047 & 0.021 & 0.018 & 0.022 & 0.040 \\
-    500000 & 0.091 & 0.047 & 0.019 & 0.013 & 0.017 & 0.025 \\
-   1000000 & 0.090 & 0.047 & 0.019 & 0.011 & 0.011 & 0.017 \\
-    \end{tabular}
-    \caption{Average Differences of Expected and Realized Rank}
-  \end{table}
-
 \end{document}

### 2013-05-10 paper.tex
Working on RTOPE proof of security.

@@
 
-  RTOPE can be proven to be IND-CPDA, just like the DCS scheme. In fact, one can show the equivalence of RTOPE and DCS in terms of the OPE encodings that both provide.
+  RTOPE can be proven to be IND-CPDA, just like the DCS scheme.
+
+  \begin{theorem}
+    RTOPE is IND-CPDA secure.
+  \end{theorem}
+  \begin{proof}
+    Like in the security proof for DCS, we shall show that encrypting $v = \{V_1, V_2, \ldots, V_{\kappa} \}$ and $w = \{W_1, W_2, \ldots, W_{\kappa}\}$ is information-theoretically the same, where $V_i, W_i$ are sequences of size $\lambda$.
+Again, we shall use induction on the number of repeated elements in either $V_i$ or $W_i$.
+
+    When there are no repeated elements, we can use the same argument we used in the DCS proof.
+We note that the sequence $\{V_1, V_2, \ldots, V_{\kappa} \}$ has a bijection to a sequence of elements $v_{ij}$ of length $\kappa \lambda$, for $i \in \{1, 2, \ldots, \kappa\}$ and $j \in \{1, 2, \ldots, \lambda \}$.
+Winning this game then becomes equivalent to winning the IND-OCPA security game, since one can think of each $v_{ij}$ and $w_{ij}$ pair as a set of values that the adversary provides the client in each round $i$.
+Popa et al (2013) shows that their scheme, which is equivalent to the Distribution Confidentiality Scheme when there are no reptitions, is IND-OCPA secure.
+Thus, the base case of no repetitions is secure.
+
+    Now, suppose that RTOPE is IND-CPDA secure when there are at most $k$ reptitions across $V_i$ and $W_i$. Select one of the repetitions
+
+  \end{proof}
 

### 2013-05-10 paper.tex
Completed security proof for RTOPE.

@@
 However, if $p_i = p^*$, then the client tells the server to move left or right with uniform probability.
-Note that in this scheme, we will use a randomized encryption scheme so that the server cannot tell if two plaintext values are the same.
+Note that in this scheme, we will use a randomized encryption scheme which is IND-CCA so that the server cannot tell if two plaintext values are the same.
 
@@
 
-    Now, suppose that RTOPE is IND-CPDA secure when there are at most $k$ reptitions across $V_i$ and $W_i$. Select one of the repetitions
-
+    Now, suppose that RTOPE is IND-CPDA secure when there are at most $k$ repetitions across $V_i$ and $W_i$.
+Now consider a sequence where there are $k+1$ repetitions across $V_i$ and $W_i$ for all $i$.
+Select two ciphertexts $c_1$ and $c_2$ of some repeated value $x$ and let us consider how it this pair of repetitions is inserted into the tree.
+Since RTOPE uses an encryption scheme which is IND-CCA for its ciphertexts, the adversary will not be able to tell whether $Dec(SK, c_1) = Dec(SK, c_2)$ with more than $1/2$ probability (by the definition of IND-CCA security).
+This means that the adversary cannot distinguish $c_1$ and $c_2$ as being repetitions with any advantage.
+Thus, a sequence of $k+1$ repetitions is information theoretically the same for the adversary as a sequence of $k$ repetitions, which we already know is IND-CPDA secure.
+Using induction, we have completed the proof.
   \end{proof}

### 2013-05-10 paper.tex
random conjeture.

@@
 
-  In order to show that RTOPE and DCS are equivalent, we first need a notion of equivalence for an OPE scheme.
-Since both RTOPE and DCS are randomized, we cannot take the naive approach and say that two schemes are equivalent if they provide the same OPE encodings.
-Instead, we will use a notion of the equivalence of the distributions of the encodings.
-We will now formally define equivalence.
+  In this section, we shall propose a notion of equivalence between two OPE schemes.
 
@@
 
-We will now show that under certain conditions, DCS and RTOPE are equivalent.
-Namely, we shall show that as the number of repetitions tends to infinity, there exists an exact equivalence between DCS and RTOPE.
-In order to show this, we shall begin by noting some properties of both DCS and RTOPE.
-We shall examine the binary search tree that is stored on the server for both the DCS and RTOPE schemes.
+  In this section, we shall investigate whether DCS and RTOPE are structurally expectation equivalent. To do this, we shall first examine some propositions.
 
@@
 
+  \subsection{Convergence in Number of Re-encodings}
+
+  Although DCS and RTOPE are not structurally expectation equivalent, we can examien other properties between these two schemes.
+In particular, we can show that as $n \to \infty$, if $R_{DCS} / R_{RTOPE} = c$ for some constant $c$ where $R_{i}$ is the number of repetitions for scheme $i$, then the number of re-encodings in DCS and RTOPE will converge to the same number.
+
 \end{document}

### 2013-05-11 paper.tex
Talking about how to query in DCS

@@
 \subsection{Querying Under DCS}
+
+  To query for some value $y$, we must actually perform a range query, since any value $y$ will be encrypted with a plaintext $y + r$ where $r \in [0,1)$.
+This means, the encrypted plaintext of $y$ can therefore take in the range $[y, y + 1)$.
+Thus, to query for the value $y$, we must perform a range query on any values in the range $[y, y+1)$.
+
+  Performing this range query on the binary search tree can be done by searching for $y$ and $y+1$ individually.
+Once we have found $y$ and $y+1$, then we can be find the least common ancestor between the nodes of $y$ and $y+1$.
+The subtree rooted at the least common ancestor will contain all possible values in the range $[y, y+1)$.
+
+  \begin{lemma}
+    The subtree rooted at the least common ancestor of $y$ and $y+1$ in a binary search tree contains all values $x \in [y, y+1)$.
+  \end{lemma}
+  \begin{proof}
+    Let us examine some value $x \in [y, y+1)$, and call the $l$ the least common ancestor of $y$ and $y+1$.
+
+    Now suppose $x$ is not in the subtree rooted at $l$.
+This means that $x$ must either be smaller than the left-most node in the subtree rooted at $l$ or greater than the right-most node in the subtree (assuming that no nodes are have repeated values which occurs with high probability because of the random bits $r$ appended to each plaintext).
+However, we know that the left-most node in the subtree rooted at $l$ must be smaller than $y$ and the right-most node in the subtree must be greater than $y+1$.
+This is true because both $y$ and $y+1$ are nodes in the subtree.
+
+    This is a contradiction, however, because we assumed $x \in [y, y+1)$, which shows that the subtree contains all values $x \in [y, y+1)$.
+  \end{proof}
+
+  We can be assured that there are no repeats in the encrypted plaintexts.
 
@@
 
+  \begin{theorem}
+    As $n \to \infty$, if $R_{DCS} / R_{RTOPE} = c$ for some constant $c$, then the number of re-econdings in DCS and RTOPE will converge to the same number.
+  \end{theorem}
+  \begin{proof}
+  \end{proof}
+
 \end{document}

### 2013-05-11 paper.tex
More range query stuff.

@@
   Performing this range query on the binary search tree can be done by searching for $y$ and $y+1$ individually.
-Once we have found $y$ and $y+1$, then we can be find the least common ancestor between the nodes of $y$ and $y+1$.
+Once we have found $y$ and $y+1$, then we can move up the tree until we find the least common ancestor between the nodes of $y$ and $y+1$.
 The subtree rooted at the least common ancestor will contain all possible values in the range $[y, y+1)$.
@@
 
-  We can be assured that there are no repeats in the encrypted plaintexts.
+This lemma instructs us on how to find all values $x \in [y, y+1)$.
+As we move up the binary search tree to parents of $y$, we check the right subtree of the parent looking for all values in $[y, y+1)$.
+We do this as we continue upwards for all successive parent nodes.
+For the node at $y+1$, we check the left subtree of all parents for values in $[y, y+1)$.
+We continue this process until the parent of the $y$ node meets the parent of the $y+1$ node.
+This process will find all values in $[y, y+1)$, because as we have shown, all values in the interval are inside the subtree.
+
+  This process is correct because we continue checking subtrees until we find the least common ancestor for the parents of both the $y$ and the $y+1$ nodes.
+The runtime of this is just $\log(n) + K$ where $K$ is the number of values in the range $[y, y+1)$.
 

### 2013-05-11 paper.tex
Writing about how we query in RTOPE and DCS.

@@
 
+  \subsection{Range Queries Under DCS}
+
+  To perform range queries under the DCS scheme, one simply needs to perform a range query on the underlying binary search tree.
+If one attempts to query for values $x \in [y, z]$, then we simply perform a range query for the underlying plaintexts in the binary search tree in the range $[y, z+1)$.
+We use the same range query mechanism as in the previous section, making sure to only output values that are inside in the interval $[y, z+1)$.
+
 \section{Indistinguishability Under Chosen Plaintext Distribution Attack (IND-CPDA)}
@@
 In RTOPE, the server cannot tell how many values are repeated, and what the distribution of repeated values looks like.
+
+  \subsection{Querying Under RTOPE}
+
+  Under RTOPE, there are multiple variations on querying for some value $x$.
+First is to query for just one ciphertext whose corresponding plaintext is equal to $x$.
+The second query type is to query for all ciphertexts whose corresponding plaintext is equal to $x$.
+
+  The first case is easy to handle and can be achieved by using the regular query mechanism used by Popa et al (2013) and returning the first ciphertext found which matches.
+If there are any ciphertexts which can be decrypted to $x$, then the regular binary search tree mechanism will find at least one, which guarantees that this will correctly return one of these ciphertexts.
+
+  The second case can be handled by a modified query algorithm.
+To return all ciphertexts decrypting to $x$, we still need to do a regular query for $x$.
+Upon finding the first $x$, we append this value to our list of results, and we need to query both the right and left subtrees for $x$ again.
+Doing this recursively until we reach a leaf will guarantee that we will find all possible places where $x$.
+This gaurantee can be given in the following proposition:
+
+  \begin{proposition}
+    Let $T$ be a binary search tree and $x$ be a repeated value in the binary search tree. There exists a subtree $T'$ rooted at $x$ which contains all values $x$ in the tree $T$.
+  \end{proposition}
+  \begin{proof}
+
+  \end{proof}
+
+  By the above proposition, we can show that as soon as we find the first value of $x$ based on the regular binary search tree query algorithm, then all other values of $x$ will be contained in either the left or right subtree of this node.
+This implies that we will find all values of $x$ in the tree.
 

### 2013-05-11 paper.tex
finished proof of stuff, working on runtime of the query algorithm.

@@
   \begin{proof}
+    We shall construct the tree by taking all possible values of $x$, and finding the lowest common ancestor of each of these values.
+It is always possible to find the lowest common ancestor of each of these values, and these will create a subtree.
+All that is left is to show that the subtree is rooted at $x$, or in other words, that the least common ancestor of all the values of $x$ in the tree is also $x$.
 
+    We note that there are three cases.
+First, if $x$ is not repeated (i.e.
+occurs in the tree only once), then the proposition is trivially true.
+Second, if $x$ is repeated, and all the repeated values are in the right subtree of the least common ancestor, then one can choose the value of $x$ which has the largest height in the binary search tree.
+This defines a subtree containing all values of $x$ and which is also rooted at $x$.
+The same idea follows when all the repeated values of $x$ are in the left subtree.
+Finally, if the repeated values of $x$ are in both the left and right subtree of the least common ancestor $l$, then we know that $x \leq l$ and $x \geq l$ by the properties of a binary search tree.
+This implies that $l = x$, whichcompletes the proof.
   \end{proof}
@@
 This implies that we will find all values of $x$ in the tree.
+
+  The runtime of this query is
 

### 2013-05-13 main.py
more data collection in data.txt

@@ -24,16 +24,25 @@ def monitor_queue():
             print element
         #print client_channel._receive_queue
 
-NUM_INPUTS = 500
-LEN_INPUTS = 4
+NUM_INPUTS = 200
+REPEAT_INPUTS = 0
+LEN_INPUTS = 10 # assuming negligible repeats
+
 inputs = []
-for i in range(NUM_INPUTS):
+#random inputs
+for i in range(NUM_INPUTS - REPEAT_INPUTS):
     inp = ""
     for j in range(LEN_INPUTS):
         inp += str(int(random.random()*2))
     inputs.append(inp)
 
-inputs = ['1101', '1110', '1111', '1100', '0111', '1011', '0010', '1000', '1100', '1100', '1010', '0110', '0101', '1010', '1011', '0101', '1011', '0111', '1100', '0101', '0110', '0010', '1110', '1111', '0000', '1010', '0001', '0000', '1011', '0100', '1000', '1110', '1100', '0001', '1101', '1000', '0011', '1001', '1111', '1110', '0110', '1110', '1110', '1000', '1000', '1111', '1100', '1101', '0000', '1101', '1000', '0101', '0100', '0101', '0001', '1101', '0000', '1100', '1001', '0111', '1001', '0000', '0010', '1110', '1100', '1110', '1001', '0011', '0011', '1001', '0100', '1111', '0111', '1000', '1000', '1010', '1001', '0110', '0100', '1011', '0001', '1100', '0001', '1110', '1001', '1001', '1011', '1100', '1010', '1101', '1011', '1101', '0010', '0100', '0010', '0001', '0111', '0110', '1000', '1101', '0111', '0000', '0101', '0100', '0101', '1100', '1001', '0101', '0101', '1001', '0000', '1000', '1111', '0010', '1001', '0001', '1000', '0001', '0101', '1001', '1110', '1101', '0110', '0101', '1100', '0001', '1100', '0100', '0001', '1000', '0001', '0111', '1001', '0101', '0000', '0100', '1100', '0001', '1001', '1000', '0000', '0001', '1011', '1000', '1110', '0000', '0110', '0100', '0010', '1010', '0000', '1100', '0111', '1011', '0000', '1001', '1100', '1110', '0010', '0010', '0011', '1011', '0111', '1000', '0000', '0100', '0011', '1000', '1100', '1110', '0101', '0001', '0110', '0101', '1111', '1000', '0110', '1011', '1101', '1000', '1101', '1001',
[…]

### 2013-05-13 server.py

@@ -223,7 +223,7 @@ len(rebalance.subtree_sizes) is the number of rebalances.
 '''
 @counter
 def rebalance(node):
-    print "Rebalance count: " + str(rebalance.subtree_sizes)
+    #print "Rebalance count: " + str(rebalance.subtree_sizes)
     print "Rebalance time: " + str(sum(rebalance.subtree_sizes))
     if balance_factor(node) == -2:
         if balance_factor(node.right) == -1: # right-right case

### 2013-05-13 paper.tex
intro/conclusion

@@
 
+\section{Introduction}
+An order-preserving encryption scheme utalizes an encryption algorithm to produce ciphertexts that preserve the numerical ordering of the plaintexts.
+This allows an untrusted server to perform order comparison, for the purpose of sorting or range checks, among other applications.
+The ideal security goal for an order-preserving encryption scheme, IND-OCPA, is to reveal only information regarding the order of the plaintext values.
+The first ideal-security order-preserving encryption scheme was proposed by Raluca et al (2013) and called a mutable order-preserving encoding, or mOPE.
+
+mOPE works be creating a balanced search tree containing all the encrypted data.
+Each encrypted value is a node associated with a binary encoding that represents its path on the tree, from root to node.
+The search tree and encrypted data is stored on an untrusted server, and a client is responsible for encrypting values and inserting them in the tree using an interactive protocol.
+This protocol also requires that the search tree be rebalanced and the binary encodings rewritten.
+
+mOPE does, however, leak information about the distribution of plaintext values.
+Each node of an mOPE search tree, representing an encrypted value, is also created with a counter.
+So if a client inserts more than one of the same plaintext value, this counter is incremented, as opposed to a new node in the search tree created.
+The result is that an adversary can identify the number of times a repeated plaintext value is inserted.
+
+This paper presents two schemes that provide the additional security of guaranteeing no leaked information regarding the distribution of elements.
+We define the security guarantee as Indistinguisability Under Chosen Plaintext Distribution Attack, IND-CPDA.
+
+The first IND-CPDA scheme we present is the Distribution Confidentiality Scheme, DCS.
+DCS uses the mOPE scheme and adds random bits to the end of plaintext to randomize the ciphertext values.
+This prevents the server from identifying the number of times a repeated plaintext value is inserted.
+
+The second IND-CPDA scheme we present is the Random Tiebreaking Order Preservering Encryption, RTOPE.
+RTOPE operates again on top of mOPE, and when a repeated plaintext value is inserted, upon reaching that node in the search tree, the client tells the server to insert left or right with uniform probability.
+Again, the server cannot tell the number of times a plaintext value is repeated.
+
+We present the concept of structural expectation equivalence, which is a mapping from all possible OPE encodings of one scheme to another, with the probability of obtaining each encoding in the first scheme is equal to the probability of obtaining the corresponding encoding in the second scheme.
+We compare DCS and RTOPE, to prove that the two schemes are structurally expectation equivalent.
+This equivalence relationship, we show, also proves that both schemes must be IND-CPDA secure.
+
+To understand the performance and equivalence of our two schemes, we implemented both under an honest server model, and evaluated the number of node rewrites using a range of benchmarks.
+
+The rest of the paper is organized as follows.
+II discusses related work.
+III presents DCS in more detail and IV describes IND-CPDA.
+V presents RTOPE in more detail.
+VI compares the two schemes, DCS and RTOPE, and proves their equivalence.
+Finally VII concludes.
+
+\section{Related Work}
+
 \section{Distribution Confidentiality Scheme}
@@
 This scheme uses Raluca et al (2013)'s original mOPE scheme, but adds an additional layer of security.
+We show that the schemes are comprable in terms of performance.
 
@@
 
-  Although DCS and RTOPE are not structurally expectation equivalent, we can examien other properties between these two schemes.
+  Although DCS and RTOPE are not structurally expectation equivalent, we can examine other properties between these two schemes.
 In particular, we can show that as $n \to \infty$, if $R_{DCS} / R_{RTOPE} = c$ for some constant $c$ where $R_{i}$ is the number of repetitions for scheme $i$, then the number of re-encodings in DCS and RTOPE will converge to the same number.
@@
 
+  \section{Conclusion}
+
+  We presented DCS and RTOPE, two order-preserving encryption schemes that achieve ideal IND-CPDA security, where an adversary learns nothing about the distribution of the plaintext values based on the ciphertexts, and only the order of the elements.
+We introduce the notion of structurally expectation equivalence, and show that DCS and RTOPE satisfy this equivalence relationship.
+Finally, we show that DCS and RTOPE achieve comprable performance.
+
 \end{document}

### 2013-05-13 paper.tex
added a little related work

@@
 \section{Related Work}
+
+Research surrounding OPE schemes has made significant progress in recent years.
+The most recent contribution of the mOPE scheme by Raluca et al (2013) achieves ideal IND-OCPA security, and thus, our schemes are built upon mOPE.
+
+DCS and RTOPE provide the new security guarantee of IND-CPDA, which is related to performing range queries over encrypted data.
+Range query schemes provide an algorithm to learn the order between a query value and data value, ideally leaking no other information.
+Our schemes are easily modified to support range queries while still guaranteeing the security of the distribution of the underlying plaintext.
+
+Raluca et al (2013) provides a new security definition, same-time OPE security, which dictates that an adversary can learn the order only for values stored in the application at the same time.
+This definition is stronger than IND-OCPA.
+Our security guarantee of IND-CPDA provides that the order only, not the distribution, for ciphertexts is leaked to an adversary.
 

### 2013-05-13 paper.tex
more related

@@
 Our security guarantee of IND-CPDA provides that the order only, not the distribution, for ciphertexts is leaked to an adversary.
+
+Prior work on range query schemes also leak information about the underlying plaintext.
+Shi et al (2007) designed an encryption scheme that leaks the decrypted data for values that fall within the range query, but preserves the privacy of all other values.
+We chose to build on schemes on existing OPE schemes, instead of range query schemes, to provide the security of the plaintext even within the range queries.
 

### 2013-05-14 paper.tex
experimental data added to paper

@@
 \usepackage{amsthm}
+\usepackage{booktabs}
 
@@
 \section{Introduction}
-An order-preserving encryption scheme utalizes an encryption algorithm to produce ciphertexts that preserve the numerical ordering of the plaintexts.
+An order-preserving encryption scheme utilizes an encryption algorithm to produce ciphertexts that preserve the numerical ordering of the plaintexts.
 This allows an untrusted server to perform order comparison, for the purpose of sorting or range checks, among other applications.
@@
 
-    Letting $C(j) = \frac{n!}{j!(n-j-1)!} \frac{n!}{(j-1)!(n-j)!}$, and integrating the epression for $u_1$, we can obtain the following result:
+    Letting $C(j) = \frac{n!}{j!(n-j-1)!} \frac{n!}{(j-1)!(n-j)!}$, and integrating the expression for $u_1$, we can obtain the following result:
     \begin{eqnarray}
@@
 
+  \section{Experimental Results}
+
+  To confirm our theoretical analysis, we implemented both the DCS and RTOPE encryption schemes on top of a simplified version of CryptDB.
+First, we created a framework that mimicked the necessary features of CryptDB, including the client-server interaction and full insertion and query functionality.
+We then made a testing framework which allowed us to easily change the number of inputs, the number of repeats in the inputs, and the choice of whether to use DCS or RTOPE.
+The results are summarizes in the table below.
+
+  \begin{table} % Add the following just after the closing bracket on this line to specify a position for the table on the page: [h], [t], [b] or [p] - these mean: here, top, bottom and on a separate page, respectively
+\centering % Centers the table on the page, comment out to left-justify
+\begin{tabular}{l c c c c} % The final bracket specifies the number of columns in the table along with left and right borders which are specified using vertical bars (|); each column can be left, right or center-justified using l, r or c.
+To specify a precise width, use p{width}, e.g.
+p{5cm}
+\toprule % Top horizontal line
+& \multicolumn{5}{c}{Number of OPE Re-Encodings} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+\cmidrule(l){2-6} % Horizontal line spanning less than the full width of the table - you can add (r) or (l) just before the opening curly bracket to shorten the rule on the left or right side
+Type & Inputs & Repeats & Average & Std. Dev.\\ % Column names row
+\midrule % In-table horizontal line
+RTOPE & 100 & 0  & 7363 & 5003 \\
+      & 100 & 10  & 4385 & 2051 \\
+      & 100 & 20  & 3945 & 643\\
+      & 100 & 40  & 2598 & 642\\
+      \midrule
+DCS   & 100 & 0  & 3776 & 791 \\
+      & 100 & 10  & 4452 & 1059 \\
+      & 100 & 20  & 3287 & 1191\\
+      & 100 & 40  & 3754 & 582\\
+      \midrule
+RTOPE & 200 & 0  & 15078 & 6751 \\
+      & 200 & 20  & 16586 & 13215\\
+      & 200 & 40  & 15707 & 6924\\
+      \midrule
+DCS   & 200 & 0  & 11300 & 2512 \\
+      & 200 & 20  & 12355 & 8704\\
+      & 200 & 40  & 8274 & 1654\\
+\bottomrule % Bottom horizontal line
+\end{tabular}
+\caption{Experimental results. N=10 for each set of inputs.} % Table caption, can be commented out if no caption is required
+\label{tab:results_table} % A label for referencing this table elsewhere, references are used in text as \ref{label}
+\end{table}
+
+Each iteration constructed an entire tree from random inputs fitting the input criteria.
+The averages and standard deviations describe the distribution of the number of OPE re-encodings required throughout the construction of the tree.
+We make several observations from the data above:
+
+\begin{enumerate}
+
+\item For large inputs, the average number of OPE re-encodings is roughly the same for both schemes.
+We found that even though the two schemes are not identical, they do have the same expectation for the shape of the resulting trees over a large number of iterations, so the averages will be the same.
+
+\item The standard deviation in OPE re-encodings varies significantly between the two schemes.
+This has to do with the resulting shape of the trees formed for the same inputs -- DCS is more likely to create an unbalanced tree, and thus the standard deviations tend to be higher than comparable RTOPE deviations.
+
+\item
+The average number of OPE re-encodings is roughly the same for any number of repeated items.
+DCS, each duplicate is converted into a unique number before the insertion phase.
+In RTOPE, each value is treated as if it were either larger or smaller than its duplicate during the insertion phase.
+In both cases, the server is not made aware of duplicate values, and thus their quantity has no bearing on the properties of the tree created by the server.
+
+\end{enumerate}
+
   \section{Conclusion}

### 2013-05-14 paper.tex
proofing

@@
 The ideal security goal for an order-preserving encryption scheme, IND-OCPA, is to reveal only information regarding the order of the plaintext values.
-The first ideal-security order-preserving encryption scheme was proposed by Raluca et al (2013) and called a mutable order-preserving encoding, or mOPE.
+The first ideal-security order-preserving encryption scheme was proposed by Popa et al (2013) and called a mutable order-preserving encoding, or mOPE.
 
@@
 We present the concept of structural expectation equivalence, which is a mapping from all possible OPE encodings of one scheme to another, with the probability of obtaining each encoding in the first scheme is equal to the probability of obtaining the corresponding encoding in the second scheme.
-We compare DCS and RTOPE, to prove that the two schemes are structurally expectation equivalent.
-This equivalence relationship, we show, also proves that both schemes must be IND-CPDA secure.
+We compare DCS and RTOPE, to prove that the two schemes are not structurally expectation equivalent.
 
-To understand the performance and equivalence of our two schemes, we implemented both under an honest server model, and evaluated the number of node rewrites using a range of benchmarks.
+To better understand the performance and equivalence of our two schemes, we implemented both with a client-server framework that supports inseration and query functionality.
+We evaluated the number of OPE re-encodings that resulted over a range of benchmark inputs.
+These inputs also had varying amounts of repetition, to better evaluate our schemes under uneven plaintext distributions.
 
@@
 VI compares the two schemes, DCS and RTOPE, and proves their equivalence.
-Finally VII concludes.
+VII describes the experimental results of our implementation of the two schemes.
+Finally VIII concludes.
 
@@
 Research surrounding OPE schemes has made significant progress in recent years.
-The most recent contribution of the mOPE scheme by Raluca et al (2013) achieves ideal IND-OCPA security, and thus, our schemes are built upon mOPE.
+The most recent contribution of the mOPE scheme by Popa et al (2013) achieves ideal IND-OCPA security, and thus, our schemes are built upon mOPE.
 
@@
 
-Raluca et al (2013) provides a new security definition, same-time OPE security, which dictates that an adversary can learn the order only for values stored in the application at the same time.
+Popa et al (2013) provides a new security definition, same-time OPE security, which dictates that an adversary can learn the order only for values stored in the application at the same time.
 This definition is stronger than IND-OCPA.
@@
 In order to solve the problem of leaking the distribution of the plaintext values, we have developed the Distribution Confidentiality Scheme (DCS).
-This scheme uses Raluca et al (2013)'s original mOPE scheme, but adds an additional layer of security.
+This scheme uses Popa et al (2013)'s original mOPE scheme, but adds an additional layer of security.
 We show that the schemes are comprable in terms of performance.
@@
 
-In the basic version of the scheme, let us assume that we want to encrypt some plaintext value $x \in \mathrm{Z}$ and send it to the server like in Raluca et al (2013)'s mOPE scheme.
+In the basic version of the scheme, let us assume that we want to encrypt some plaintext value $x \in \mathrm{Z}$ and send it to the server like in Popa et al (2013)'s mOPE scheme.
 For DCS, there is an additional parameter $\rho$ which will govern the probability with which the server sees a repeated value.
@@
 The resulting value $x' = x + r_{\rho}$ will be encrypted with DET.
-Raluca et al (2013)'s mOPE scheme will work the same as before, but now acting on $x'$.
+Popa et al (2013)'s mOPE scheme will work the same as before, but now acting on $x'$.
 
-Inserting in this scheme is simple, since nothing really has to be changed from Raluca et al (2013)'s mOPE scheme.
+Inserting in this scheme is simple, since nothing really has to be changed from Popa et al (2013)'s mOPE scheme.
 The client will take the value $x$ to insert, create $x'$, then encrypt $x'$ to obtain a ciphertext.
@@
 Finally, if the repeated values of $x$ are in both the left and right subtree of the least common ancestor $l$, then we know that $x \leq l$ and $x \geq l$ by the properties of a binary search tree.
-This implies that $l = x$, whichcompletes the proof.
+This implies that $l = x$, which completes the proof.
   \end{proof}
@@
   We presented DCS and RTOPE, two order-preserving encryption schemes that achieve ideal IND-CPDA security, where an adversary learns nothing about the distribution of the plaintext values based on the ciphertexts, and only the order of the elements.
-We introduce the notion of structurally expectation equivalence, and show that DCS and RTOPE satisfy this equivalence relationship.
-Finally, we show that DCS and RTOPE achieve comprable performance.
+DCS generates random bits to append to any plaintext value that is encrypted, which requires a modified querying scheme involving localized range queries.
+RTOPE handles repeated values differently, by appending repeated plaintexts as left or right children on the server's search tree with uniform probability.
+Again, we created a modified querying algorithm for RTOPE that requires recursive queries once one occurence of the plaintext query is found.
+
+  We proved that DCS and RTOPE are IND-CPDA secure and introduced the notion of structurally expectation equivalence.
+We also proved the important theorem that if two OPE schemes are structurally expectation equivalent, then one is IND-CPDA secure if and only if the other is IND-CPDA secure as well.
+We then showed that though DCS and RTOPE do satisfy this structurally expectation equivalence relationship, they are still IND-CPDA secure.
+
+  We noted that though the schemes are not structurally expectation equivalent, the number of OPE re-encodings will converege to the same number, given identical inputs.
+Finally, this notion was further supported by our experimental results.
+We tested our implementation of DCS and RTOPE on a range of inputs, and found that the number of OPE re-encodings were of the same order.
+
+  \begin{thebibliography}{9}
+
+\bibitem{adapopa13}
+  R.A. Popa, F. Li, N. Zeldovich.
+  An Ideal-Security Protocol for Order Preserving Encoding.
+  2013.
+
+  \bibitem{Shi07}
+  E. Shi, J. Bethencourt, T.-H. H. Chan, D. Song, and A. Perrig.
+Multi-dimension range query over encrypted data. In \emph{IEEE
+Symposium on Security and Privacy}, 2007.
+
+\end{thebibliography}
 

### 2013-05-14 paper.tex
Edited first few sections

@@
 %--------Meta Data: Fill in your info------
-\title{Order Preserving Encryption Schemes: \\
-  Preventing the Leakage of Distribution\\
-6.857 Final Paper \\
-Hrishikesh Joshi, Max Kolysh, Mari Miyachi, John Wang}
+\title{ \\
+  Preventing Leakage of Distribution in Order Preserving Encryption Schemes \\ \vspace*{.3in}
+\small Hrishikesh Joshi, Max Kolysh, Mari Miyachi, John Wang \\
+\small 6.857 Final Paper \\
+\small May 15, 2013}
 
+\date{}
 \begin{document}
@@
 
-\section{Introduction}
-An order-preserving encryption scheme utilizes an encryption algorithm to produce ciphertexts that preserve the numerical ordering of the plaintexts.
-This allows an untrusted server to perform order comparison, for the purpose of sorting or range checks, among other applications.
-The ideal security goal for an order-preserving encryption scheme, IND-OCPA, is to reveal only information regarding the order of the plaintext values.
-The first ideal-security order-preserving encryption scheme was proposed by Popa et al (2013) and called a mutable order-preserving encoding, or mOPE.
-
-mOPE works be creating a balanced search tree containing all the encrypted data.
-Each encrypted value is a node associated with a binary encoding that represents its path on the tree, from root to node.
-The search tree and encrypted data is stored on an untrusted server, and a client is responsible for encrypting values and inserting them in the tree using an interactive protocol.
-This protocol also requires that the search tree be rebalanced and the binary encodings rewritten.
-
-mOPE does, however, leak information about the distribution of plaintext values.
-Each node of an mOPE search tree, representing an encrypted value, is also created with a counter.
-So if a client inserts more than one of the same plaintext value, this counter is incremented, as opposed to a new node in the search tree created.
-The result is that an adversary can identify the number of times a repeated plaintext value is inserted.
-
-This paper presents two schemes that provide the additional security of guaranteeing no leaked information regarding the distribution of elements.
-We define the security guarantee as Indistinguisability Under Chosen Plaintext Distribution Attack, IND-CPDA.
-
-The first IND-CPDA scheme we present is the Distribution Confidentiality Scheme, DCS.
-DCS uses the mOPE scheme and adds random bits to the end of plaintext to randomize the ciphertext values.
-This prevents the server from identifying the number of times a repeated plaintext value is inserted.
-
-The second IND-CPDA scheme we present is the Random Tiebreaking Order Preservering Encryption, RTOPE.
-RTOPE operates again on top of mOPE, and when a repeated plaintext value is inserted, upon reaching that node in the search tree, the client tells the server to insert left or right with uniform probability.
-Again, the server cannot tell the number of times a plaintext value is repeated.
-
-We present the concept of structural expectation equivalence, which is a mapping from all possible OPE encodings of one scheme to another, with the probability of obtaining each encoding in the first scheme is equal to the probability of obtaining the corresponding encoding in the second scheme.
-We compare DCS and RTOPE, to prove that the two schemes are not structurally expectation equivalent.
-
-To better understand the performance and equivalence of our two schemes, we implemented both with a client-server framework that supports inseration and query functionality.
+\section{Introduction} \\
+Order-preserving encryption schemes serve to generate ciphertexts that preserve the numerical ordering of the plaintexts.
+Such schemes provide an entity storing encrypted data, such as a mail server or a server interacting with a database, the ability to perform order comparison operations such as sorting, range query checks, and ranking, among other applications.
+The ideal security goal for an order-preserving encryption scheme, IND-OCPA, is for the scheme to reveal nothing except for the order of the plaintexts.
+\\ \\
+For more than a decade, researchers have invented such schemes with varying degrees of leakage of plaintexts and other attributes of the data.
+Recently, the first order-preserving encryption scheme that satisfies IND-OCPA, mutable order-preserving encoding (mOPE), was proposed by Popa et al (2013).
+mOPE works by creating a balanced search tree containing all the encrypted data on a server, giving the server the ability the order the tree based on the plaintexts without giving the server information regarding the plaintexts themselves.
+All encrypted values are represented by a node in the balanced search tree that has an encoding, the Order Preserving Encoding (OPE), associated with it which represents its path on the tree from the root to the node, allowing the server the ability to maintain the order of the plaintexts.
+\\ \\
+One disadvantage of mOPE, however, is that it can leak information about the distribution of plaintext values since multiple entries of the same plaintext value are maintainted in the same node in the tree with a counter.
+In this paper, we present two schemes that address this issue: Distribution Confidentiality Scheme (DCS) and Random Tiebreaking Order Preservering Encryption (RTOPE).
+Further, we define a new security guarantee, Indistinguisability Under Chosen Plaintext Distribution Attack (IND-CPDA), which these schemes are intended to satisfy.
+\\ \\
+To better understand the performance and equivalence of our two schemes, we implemented both with a client-server framework that supports insertion and query functionality.
 We evaluated the number of OPE re-encodings that resulted over a range of benchmark inputs.
 These inputs also had varying amounts of repetition, to better evaluate our schemes under uneven plaintext distributions.
-
+We show the results of this work, and prove that the two schemes are not structurally expectation equivalent.
+\\ \\
 The rest of the paper is organized as follows.
-II discusses related work.
+II discusses mOPE, including related work.
 III presents DCS in more detail and IV describes IND-CPDA.
@@
 VII describes the experimental results of our implementation of the two schemes.
-Finally VIII concludes.
-
-\section{Related Work}
-
-Research surrounding OPE schemes has made significant progress in recent years.
-The most recent contribution of the mOPE scheme by Popa et al (2013) achieves ideal IND-OCPA security, and thus, our schemes are built upon mOPE.
-
-DCS and RTOPE provide the new security guarantee of IND-CPDA, which is related to performing range queries over encrypted data.
-Range query schemes provide an algorithm to learn the order between a query value and data value, ideally leaking no other information.
-Our schemes are easily modified to support range queries while still guaranteeing the security of the distribution of the underlying plaintext.
-
-Popa et al (2013) provides a new security definition, same-time OPE security, which dictates that an adversary can learn the order only for values stored in the application at the same time.
-This definition is stronger than IND-OCPA.
-Our security guarantee of IND-CPDA provides that the order only, not the distribution, for ciphertexts is leaked to an adversary.
-
-Prior work on range query schemes also leak information about the underlying plaintext.
+Finally VIII concludes with a brief overview of our overall approach.
+\section{Mutable Order-Preserving Scheme (mOPE)}
+As mentioned earlier, mOPE is the first known order-preserving scheme that satisfies IND-OCPA, leaking nothing with the exception of the order of the plaintexts.
+In this section we describe how mOPE works, including the leakage of distribution that it can lead to.
+We begin with two entities,
+an untrusted server and a client with confidential data as shown in Figure 1. 
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[height=1.2in,width=4in,angle=0]{857pic4.png}
+\caption{The client hosts confidential data in encrypted form on the untrusted server. mOPE allows subsequent operations requiring order to be performed on the encrypted data on the untrusted server.}
+\end{center}
+\end{figure}
+\subsection{Storage of Data on Client and Server}
+Figure 2 below depicts the data maintained by the client and server at a given point in time.
+The client hosts confidential plaintext data and and the corresponding ciphertexts.
+The client relays the ciphertexts to the server, which maintains a table with the corresponding ciphertexts.
+The B-tree maintained by the server shows the data marked by the ciphertext values, which the server knows, but ordered by the underlying plaintexts, which the server does not know.
+The ability for the server to maintain such order based on plaintexts without knowing the underlying plaintexts is explained in the next section.
+It is important to note that the server generates Order-Preserving Encodings (OPEs) for each of the ciphertexts in the B-tree, and preserves a mapping between OPEs and ciphertexts as shown in the table the server maintains.
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[height=4.2in,width=6in,angle=0]{857pic6.png}
+\caption{The client hosts a series of plaintexts and their corresponding ciphertexts.
+The client provides the server with the ciphertexts, and the server maintains a B-tree ordered by plaintext values, along with a mapping between OPEs and ciphertexts.}
+\end{center}
+\end{figure}
+\subsection{Protocol for Maintaining Order on Server}
+As stated previously, the server orders the values in the B-tree based on plaintexts without knowing the plaintexts themselves.
+The server's ability to do so is best illustrated by considering how new values are added to the server's table by the client.
+In Figure 3 below, we consider the situation in which the client adds a new plaintext with value 30 and corresponding ciphertext with value 10 to the existing data from Figure 2.
+\\ \\
+To insert the value, the client first notifies the server, which subsequently gives back the client the ciphertext of the root node, which is 32.
+The client decrypts the ciphertext to find the corresponding plaintext, which has value 24, and subsequently determines whether the new plaintext he wishes to insert should lie to the right or left of the node returned by the server in order to preserve plaintext-based order in the B-tree.
+The client relays the proper direction to the server, which in this instance is the right side, and the server thereby moves right down the tree and gives the client the ciphertext of the right child of the root node.
+This interactive protocol continues until the server is unable to give the client a child node at the end of a tree path, and the client subsequently tells the server to add the new node to the appropriate postiion as a child of the existing leaf node.
+In this instance, the node with ciphertext 30 is inserted to the left of the node with ciphertext 16 since the ciphertext 30 has a plaintext with value 10, which is less than the plaintext with value 36 corresponding to the node with ciphertext of value 16.
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[height=4.5in,width=6in,angle=0]{857pic5.png}
+\caption{The server is able to order the B-tree by the plaintext values of the nodes using an interactive protocol with the client.}
+\end{center}
+\end{figure}
+\subsection{Handling repeated values}
+When the client inserts multiple instances of the same value into the B-tree, the server does not create a new node for each such repeated value.
+Instead, the server provides only one node for a given plaintext value, and increments this count whenever the same value is added to the B-tree by the client.
+Unfortunately, this provides the server the ability to learn about the distribution of values in the B-tree based on the location and magnitute of node counts, and is the primary issue that the remaining portion of this paper addresses.
+\subsection{Related Work}
+The mOPE scheme by Popa et al (2013) is the first scheme to achieve ideal IND-OCPA security, and our schemes are built upon mOPE.
+Prior work on range query schemes have provided schemes that leak information about the underlying plaintext.
 Shi et al (2007) designed an encryption scheme that leaks the decrypted data for values that fall within the range query, but preserves the privacy of all other values.
 We chose to build on schemes on existing OPE schemes, instead of range query schemes, to provide the security of the plaintext even within the range queries.
-
+\\ \\
+Further, Popa et al (2013) provides a new security definition, same-time OPE security, which dictates that an adversary can learn the order only for values stored in the application at the same time, and is stronger than IND-OCPA.
+Our security guarantee of IND-CPDA, explained later in the paper, asks that the ciphertexts not leak the distribution of values.
 \section{Distribution Confidentiality Scheme}
-
 In order to solve the problem of leaking the distribution of the plaintext values, we have developed the Distribution Confidentiality Scheme (DCS).
@@
 We show that the schemes are comprable in terms of performance.
-
+\\ \\
 In essence, the DCS scheme adds random bits to the end of a plaintext so that the ciphertext values are randomized.
 This will prevent the server from being able to identify the number of times a repeated plaintext value is inserted.
-
+\\ \\
 \subsection{Description of DCS}
-
-This section will give a formal description of DCS. We will first describe the basic version of the scheme, then we will augment it so that decimal numbers can be represented as well.
-
+This section will give a formal description of DCS. We will first describe the basic version of the scheme, then we will augment it so that decimal numbers can be represented as well. \\ \\
 In the basic version of the scheme, let us assume that we want to encrypt some plaintext value $x \in \mathrm{Z}$ and send it to the server like in Popa et al (2013)'s mOPE scheme.
@@
 Popa et al (2013)'s mOPE scheme will work the same as before, but now acting on $x'$.
-
+\\ \\
 Inserting in this scheme is simple, since nothing really has to be changed from Popa et al (2013)'s mOPE scheme.
@@
 Once it arrives at a leaf node, the client will insert the new ciphertext in the correct direction.
-
 \begin{figure}
@@
 \end{figure}
-
 Querying, however, gets more difficult, and the next section will discuss how the client can query for some value $y$. 
-
-\subsection{Querying Under DCS}
-
+\subsection{Querying Under DCS} \\ \\
   To query for some value $y$, we must actually perform a range query, since any value $y$ will be encrypted with a plaintext $y + r$ where $r \in [0,1)$.
@@
 Thus, to query for the value $y$, we must perform a range query on any values in the range $[y, y+1)$.
-
+\\ \\
 Performing this range query on the binary search tree can be done by searching for $y$ and $y+1$ individually.
@@
 The subtree rooted at the least common ancestor will contain all possible values in the range $[y, y+1)$.
-
   \begin{lemma}
@@
   \begin{proof}
-    Let us examine some value $x \in [y, y+1)$, and call the $l$ the least common ancestor of $y$ and $y+1$.
-
+Let us examine some value $x \in [y, y+1)$, and call the $l$ the least common ancestor of $y$ and $y+1$. \\ \\
 Now suppose $x$ is not in the subtree rooted at $l$.
@@
 This is true because both $y$ and $y+1$ are nodes in the subtree.
-
+\\ \\
 This is a contradiction, however, because we assumed $x \in [y, y+1)$, which shows that the subtree contains all values $x \in [y, y+1)$.
-  \end{proof}
-
-This lemma instructs us on how to find all values $x \in [y, y+1)$.
+\end{proof} \\ \\This lemma instructs us on how to find all values $x \in [y, y+1)$.
 As we move up the binary search tree to parents of $y$, we check the right subtree of the parent looking for all values in $[y, y+1)$.
@@
 This process will find all values in $[y, y+1)$, because as we have shown, all values in the interval are inside the subtree.
-
+\\ \\
 This process is correct because we continue checking subtrees until we find the least common ancestor for the parents of both the $y$ and the $y+1$ nodes.
 The runtime of this is just $\log(n) + K$ where $K$ is the number of values in the range $[y, y+1)$.
-
 \subsection{Range Queries Under DCS}
-
  To perform range queries under the DCS scheme, one simply needs to perform a range query on the underlying binary search tree.
@@
 We use the same range query mechanism as in the previous section, making sure to only output values that are inside in the interval $[y, z+1)$.
-
 \section{Indistinguishability Under Chosen Plaintext Distribution Attack (IND-CPDA)}
-
-This security definition consists of two phases of interaction between the adversary and the challenger.
-
+This security definition consists of two phases of interaction between the adversary and the challenger. \\ \\
 In phase I:
@@
   \item Adversary may perform encryptions and other operations in time $poly(\kappa)$.
-\end{itemize}
-
+\end{itemize} \\ \\
 In phase II, the client and server engage in $poly(\kappa)$ rounds of interaction in which the adversary is adaptive. In each round $i$:
@@
   \item The client leads the interaction for the encryption algorithm on inputs $SK$ and $V_i^b$ with the server, with the adversary observing all the state at the server.
-\end{itemize}
-
+\end{itemize} \\ \\
 In phase III:
@@
   \item Adversary outputs $b'$ as its guess for $b$. 
-\end{itemize}
-
+\end{itemize} \\ \\
 The adversary shall win the game if its guess is correct $b' = b$ and the sets have the same order relations (namely that $v_{ij}^0 < v_{ik}^0 \Leftrightarrow v_{ij}^1 < v_{ik}^1$). 
-
 \begin{definition}
   The adversary's advantage is the difference $|Pr[\textrm{win}^{Adv, \kappa, \lambda}] - 1/2|$.
-\end{definition}
-
+\end{definition} \\ \\
 \begin{definition}
@@
 \end{definition}
-
 \subsection{Security of DCS}
-
 \begin{theorem}
@@
 We shall show that encrypting $v = \{V_1, V_2, \ldots, V_{\kappa} \}$ and $w = \{W_1, W_2, \ldots, W_{\kappa}\}$ is information-theoretically the same, where $V_i, W_i$ are sequences of size $\lambda$.
-
+\\ \\
 We will show this by induction on the number of repeated elements in either $V_i$ or $W_i$.
@@
 This means that the DCS scheme is IND-CPDA secure when there are no repeated elements.
-
+\\ \\
 Now we shall use strong induction and assume that when there are a maximum of $k$ repeated elements in both $V_i$ and $W_i$, the DCS scheme is IND-CPDA secure.
 To complete the proof, we simply need to show that when there are $k+1$ repeated elements, the DCS scheme is still secure.
-
+\\ \\
 Let us compare the sets $V_i$ and $W_i$ with $k+1$ repeated elements to the sets with $k$ repeated elements.
@@
 Therefore, when there are $k+1$ repeated elements, DCS is IND-CPDA secure.
-
+\\ \\
 We have therefore shown by induction that DCS is IND-CPDA secure for any number of repeated elements in the sets $V_i$ and $W_i$, which completes the proof that DCS is IND-CPDA secure.
 \end{proof}
-
 \section{Random Tiebreaking Order Preserving Encryption (RTOPE)}
-
 Consider a simple tie-breaking rule on top of Popa et al (2013)'s mOPE scheme.
@@
 Note that in this scheme, we will use a randomized encryption scheme which is IND-CCA so that the server cannot tell if two plaintext values are the same.
-
+\\ \\
 To query a ciphertext $c^*$, one needs to make sure to find all possible places where $c^*$ can exist.
@@
 Querying each subtree is done with the  normal Popa et al (2013) process.
-
+\\ \\
 This scheme is a simple extension of Popa et al (2013)'s scheme and handles repeated values.
 In RTOPE, the server cannot tell how many values are repeated, and what the distribution of repeated values looks like.
-
 \subsection{Querying Under RTOPE}
-
 Under RTOPE, there are multiple variations on querying for some value $x$.
@@
 The second query type is to query for all ciphertexts whose corresponding plaintext is equal to $x$.
-
+\\ \\
 The first case is easy to handle and can be achieved by using the regular query mechanism used by Popa et al (2013) and returning the first ciphertext found which matches.
 If there are any ciphertexts which can be decrypted to $x$, then the regular binary search tree mechanism will find at least one, which guarantees that this will correctly return one of these ciphertexts.
-
+\\ \\
 The second case can be handled by a modified query algorithm.
@@
 Doing this recursively until we reach a leaf will guarantee that we will find all possible places where $x$.
-This gaurantee can be given in the following proposition:
-
+\\ \\
+This gaurantee can be given in the following proposition: \\ \\
   \begin{proposition}
@@
 All that is left is to show that the subtree is rooted at $x$, or in other words, that the least common ancestor of all the values of $x$ in the tree is also $x$.
-
+\\ \\
 We note that there are three cases.
@@
 This implies that $l = x$, which completes the proof.
-  \end{proof}
-
+  \end{proof} \\ \\
 By the above proposition, we can show that as soon as we find the first value of $x$ based on the regular binary search tree query algorithm, then all other values of $x$ will be contained in either the left or right subtree of this node.
 This implies that we will find all values of $x$ in the tree.
-
+\\ \\
   The runtime of this query is
-
-  \subsection{Security of RTOPE}
-
+  \subsection{Security of RTOPE} \\ \\
   RTOPE can be proven to be IND-CPDA, just like the DCS scheme. 
-
   \begin{theorem}
@@
 Again, we shall use induction on the number of repeated elements in either $V_i$ or $W_i$.
-
+\\ \\
 When there are no repeated elements, we can use the same argument we used in the DCS proof.
@@
 Thus, the base case of no repetitions is secure.
-
+\\ \\
 Now, suppose that RTOPE is IND-CPDA secure when there are at most $k$ repetitions across $V_i$ and $W_i$.
@@
   \end{proof}
-
-\section{Relationship Between DCS and RTOPE}
-
-  In this section, we shall propose a notion of equivalence between two OPE schemes.
-
+\section{Relationship Between DCS and RTOPE} \\ \\In this section, we shall propose a notion of equivalence between two OPE schemes.
   \subsection{Structural Expectation Equivalence} 
-
   \emph{Definition:} Two OPE schemes $x,y$ are \emph{Structural Expectation Equivalent} if for each plaintext $p_i$ that scheme $x$ encodes in a sequence of plaintexts $P = \{p_i\}_{i=1}^n$, there exists some bijective mapping $f: \mathrm{Z}_y \to \mathrm{Z}_x$ where $Pr[Encode_x(c_i) = \omega] = Pr[f(Encode_y(c_i)) = \omega]$ for all $\omega \in \mathrm{Z}_x$ where $\mathrm{Z}_x$ is the space of all possible OPE encodings for scheme $x$, $c_i = Enc(SK, p_i)$ is the ciphertext corresponding to $p_i$, and $Encode_x(c_i)$ and $Encode_y(c_i)$ are the functions that obtain the OPE encoding for schemes $x$ and $y$ respectively.
-
+\\ \\
 In other words, for two schemes to be structurally expectation equivalent, there must exist a mapping $f$ from all of the possible OPE encodings from scheme $x$ to scheme $y$, where the probability of obtaining an encoding in $x$ is the same as the probability of obtaining the corresponding encoding in $y$ (based on the mapping).
 This must be the case for all possible encodings.
-
+\\ \\
 This notion of structural expectation equivalence encompasses a number of useful features.
@@
 Hence, if $x$ is structurally expectation equivalent to $y$, then $y$ is necessarily structurally expectation equivalent to $x$ because one can simply use $f^{-1}$ as the mapping, which necessarily exists because of $f$ being bijective.
-
 \begin{theorem}
@@
 \end{theorem}
-\begin{proof}
+\begin{proof} \\ \\
 First, we observe that notion of equivalence is symmetric (since $f$ is a bijective mapping which is invertible), so that without loss of generality, we need only show that if $x$ is IND-CPDA secure, then $y$ is as well.
 So now we can suppose that $x$ is IND-CPDA secure and $x,y$ are equivalent schemes.
-
+\\ \\
 Since $x$ is IND-CPDA secure, then for any two sequences $v = \{V_1, V_2, \ldots, V_{\kappa}\}$ and $w = \{W_1, W_2, \ldots, W_{\kappa} \}$ that the adversary provides, the adversary cannot correctly distinguish between $v$ and $w$ with non-neglible advantage.
@@
 This means that the adversary can distinguish the encoding $Encode_y(V_i') = \{Encode_y(V_{ij}' \}_{j=1}^{\lambda}$ for some $i$ from the encoding $Encode_y(W_i') = \{Encode_y(W_{ij}') \}_{j=1}^{\lambda}$.
-
+\\ \\
 This means the adversary can also distinguish the mapping $Encode_x(V_i')$ from the encoding $Encode_x(W_i')$ by applying the bijective mapping $f$ (from the definition of equivalence) to obtain $Encode_x(V_i') = f(Encode_y(V_i'))$ and $Encode_x(W_i') = f(Encode_y(W_i'))$.
@@
 \end{proof}
-
 \subsection{Structural Expectation Equivalence of DCS and RTOPE}
-
 In this section, we shall investigate whether DCS and RTOPE are structurally expectation equivalent. To do this, we shall first examine some propositions. 
-
 \begin{proposition}
  There exists some subtree which contains all the ciphertexts corresponding to a plaintext $x$ in both DCS and RTOPE.
-\end{proposition}
+\end{proposition}\\ \\
 \begin{proof}
   This proposition is immediately clear because one can always take the entire tree as the subtree. This works for the cipher text trees stored in both DCS and RTOPE.
-\end{proof}
-
+\end{proof}\\ \\
 Since a subtree containing all the ciphertexts corresponding to a plaintext $x$ exists, we can now examine properties of this subtree.
 First, we show that the root of the smallest possible such subtree must be a ciphertext which gets decrypted to $x$.
-
 \begin{proposition}
   The smallest subtree containing all ciphertexts which can be decrypted to some plaintext $x$ is rooted at a ciphertext $c$ such that $x = Dec(SK, c)$ in both DCS and RTOPE.
-\end{proposition}
+\end{proposition}\\ \\
 \begin{proof}
@@
 Now we shall show that this smallest subtree is rooted at $c$ such that $x = Dec(SK, c)$ for DCS.
-
+\\ \\
 Suppose not, by contradiction.
@@
 If not, then the subtree we are in is not the smallest subtree containing all ciphertexts which decrypt to $x$ because one can simply take either the right or left subtree (depending on if the left or right subtree does not contain $c_l$ or $c_r$ respectively).
-
+\\ \\
 However, we know that $Dec(SK, c_l) \leq Dec(SK, c') \leq Dec(SK, c_r)$ by the fact that $c_l$ is in the left subtree of $c'$ and that $c_r$ is in the right subtree.
@@
 We have therefore shown that for DCS, the smallest subtree containing all cipertexts decrypting to $x$ must be rooted at a ciphertext decrypting to $x$.
-
+\\ \\
 The proof for RTOPE is similar and we only provide a sketch.
@@
 This means that $Dec(SK, c_l) \leq Dec(SK, c') \leq Dec(SK, c_r)$ which means that $x' = x$, which results in a contradiction (just like in the proof for DCS).
-\end{proof}
-
+\end{proof} \\ \\
 We have seen that the smallest subtree containing a repeated plaintext will be rooted at a ciphertext decrypting to that plaintext.
@@
 For instance, one can examine the series of decisions that are made in the RTOPE scheme by the client by examining this subtree and a smaller subtree in a recursive fashion.
-
+\\ \\
 For DCS, one can see that moving left or right from the root element depends on the relative size of the root element with the new element being inserted or queried.
@@
 Thus, moving left at the root is just the probability that the random number $r_1$ is smaller than the random number $r_r$ picked at the root.
-
+\\ \\
 Now let us examine some series of moves down the tree when attempting to query or insert some node with plaintext value $x$, denoted by the sequence
@@
     \{ m_0(x), m_1(x), \ldots, m_k(x) \}
-  \end{eqnarray}
-
+  \end{eqnarray} \\ \\
 We shall drop the $x$ for convenience and commonly refer to moves as $m_i$. We see that $m_i$ can take on two possibilities, 0 for left or 1 for moving right, and we can characterize the moves:
@@
     \end{array} \right.
-  \end{eqnarray}
-
-  Here $p_i$ is the underlying plaintext value of the node at the $i$th move.
-
-  We shall proceed to show that the two schemes do not produce the same expected tree.
-
-  \begin{theorem}
+  \end{eqnarray}\\ \\
+Here $p_i$ is the underlying plaintext value of the node at the $i$th move.\\ \\
+We shall proceed to show that the two schemes do not produce the same expected tree. \begin{theorem}
     DCS and RTOPE are not structurally expectation equivalent.
-  \end{theorem}
+  \end{theorem}\\ \\
   \begin{proof}
@@
 Thus, we know that the moves in these cases will be equivalent and the probability of making the moves on non-repeated nodes will be equal.
-
+\\ \\
 Thus, we can reduce our problem to considering a sequence of moves \{$m_i\}_{i=1}^k$ on the plaintext values which are equal to $x$.
@@
 This is becase one moves left or right with probability $\frac{1}{2}$.
-
+\\ \\
 Now we shall examine the sequence of moves in DCS.
@@
 Therefore, we need only compare $r_i$ to the value $r^*$, where $r^*$ is the random part of the new plaintext we are inserting.
-
+\\ \\
 The probability that we make a series of moves $\{m_i\}_{i=1}^k$ is the probability that $r^*$ has the $j$ and $j+1$st smallest elements in the sequence of random values $\{ r_i\}_{i=1}^k$.
 Let $n = R(x)$ be the total number of repeated values of $x$.
-
+\\ \\
 It is well known that the probability that the $j$th smallest element falling in the interval $[u, u + du]$ is given by:
@@
       \frac{n!}{(j-1)!(n-j)!} u^{j-1} (1-u)^{n-j} du
-    \end{eqnarray}
-
+    \end{eqnarray} \\ \\
 Therefore, the probability that $r^*$ falls between the $j$th and $j+1$st value is just the difference between all potential values $u_1$ of the $j$th smallest element and all potential values $u_2$ of the $j+1$st element.
@@
       \int_{0}^1 \int_0^{u_2} Pr[U_2 = u_2] Pr[U_1 = u_1] Pr[u_1 < r^* < u_2] d_{u_1} d_{u_2}
-    \end{eqnarray}
-
+    \end{eqnarray} \\ \\
 Where we take $U_1$ as the $j$th smallest value and $U_2$ as the $j+1$st smallest value.
 Thus, the probability of $r^*$ falling in that interval is the integral over all possible values of $U_2$ and $U_1$, and the probabilitiy that it falls inside of the that interval.
-Since $Pr[u_1 < r^* < u_2] = (u_2 - u_1)$, we can write the above as:
-
+Since $Pr[u_1 < r^* < u_2] = (u_2 - u_1)$, we can write the above as:\\ \\
 \begin{eqnarray}
       \int_{0}^1 \int_0^{u_2} \left( \frac{n!}{j!(n-j-1)!} u_2^j (1 - u_2)^{n-j-1} \right) \left( \frac{n!}{(j-1)!(n-j)!} u_1^{j-1} (1 - u_1)^{n-j} \right) (u_2 - u_1) d_{u_1} d_{u_2}
-    \end{eqnarray}
-
+    \end{eqnarray} \\ \\
 Letting $C(j) = \frac{n!}{j!(n-j-1)!} \frac{n!}{(j-1)!(n-j)!}$, and integrating the expression for $u_1$, we can obtain the following result:
@@
       C(j) \int_0^1 u_2^j (1 - u_2)^{n-j-1} \left( \frac{(u_2 (n+1) - j) B(j, n-j+1) + u_2^j (1-u_2)^{n-j+1}}{n+1} \right) d u_2
-    \end{eqnarray}
-
-    The above is the probability that $r^*$ falls between the $j$th and $j+1$st values. Simulating this in the figure below, it is clear that this is not uniform for all values of $j$ (like RTOPE is).
-
+    \end{eqnarray} \\ \\
+The above is the probability that $r^*$ falls between the $j$th and $j+1$st values.
+Simulating this in the figure below, it is clear that this is not uniform for all values of $j$ (like RTOPE is).
+\\ \\
 \begin{figure}[H]
@@
   \end{proof}
-
 \subsection{Convergence in Number of Re-encodings}
-
 Although DCS and RTOPE are not structurally expectation equivalent, we can examine other properties between these two schemes.
 In particular, we can show that as $n \to \infty$, if $R_{DCS} / R_{RTOPE} = c$ for some constant $c$ where $R_{i}$ is the number of repetitions for scheme $i$, then the number of re-encodings in DCS and RTOPE will converge to the same number.
-
 \begin{theorem}
@@
   \end{proof}
-
 \section{Experimental Results}
-
 To confirm our theoretical analysis, we implemented both the DCS and RTOPE encryption schemes on top of a simplified version of CryptDB.
@@
 The results are summarizes in the table below.
-
+\\ \\
 \begin{table} % Add the following just after the closing bracket on this line to specify a position for the table on the page: [h], [t], [b] or [p] - these mean: here, top, bottom and on a separate page, respectively
@@
 \label{tab:results_table} % A label for referencing this table elsewhere, references are used in text as \ref{label}
-\end{table}
-
+\end{table} \\ \\
 Each iteration constructed an entire tree from random inputs fitting the input criteria.
 The averages and standard deviations describe the distribution of the number of OPE re-encodings required throughout the construction of the tree.
-We make several observations from the data above:
-
+We make several observations from the data above:  \\ \\
 \begin{enumerate}
-
 \item For large inputs, the average number of OPE re-encodings is roughly the same for both schemes.
 We found that even though the two schemes are not identical, they do have the same expectation for the shape of the resulting trees over a large number of iterations, so the averages will be the same.
-
 \item The standard deviation in OPE re-encodings varies significantly between the two schemes.
 This has to do with the resulting shape of the trees formed for the same inputs -- DCS is more likely to create an unbalanced tree, and thus the standard deviations tend to be higher than comparable RTOPE deviations.
-
 \item
@@
 In both cases, the server is not made aware of duplicate values, and thus their quantity has no bearing on the properties of the tree created by the server.
-
 \end{enumerate}
-
 \section{Conclusion}
-
  We presented DCS and RTOPE, two order-preserving encryption schemes that achieve ideal IND-CPDA security, where an adversary learns nothing about the distribution of the plaintext values based on the ciphertexts, and only the order of the elements.
@@
 Again, we created a modified querying algorithm for RTOPE that requires recursive queries once one occurence of the plaintext query is found.
-
+\\ \\
 We proved that DCS and RTOPE are IND-CPDA secure and introduced the notion of structurally expectation equivalence.
@@
 We then showed that though DCS and RTOPE do satisfy this structurally expectation equivalence relationship, they are still IND-CPDA secure.
-
+\\ \\
 We noted that though the schemes are not structurally expectation equivalent, the number of OPE re-encodings will converege to the same number, given identical inputs.

### 2013-05-15 paper.tex
proofing

@@
 Order-preserving encryption schemes serve to generate ciphertexts that preserve the numerical ordering of the plaintexts.
-Such schemes provide an entity storing encrypted data, such as a mail server or a server interacting with a database, the ability to perform order comparison operations such as sorting, range query checks, and ranking, among other applications.
+Such schemes provide an entity for storing encrypted data, such as a mail server or a server interacting with a database, and the ability to perform order comparison operations such as sorting, range query checks, and ranking, among other applications.
 The ideal security goal for an order-preserving encryption scheme, IND-OCPA, is for the scheme to reveal nothing except for the order of the plaintexts.
 \\ \\
-For more than a decade, researchers have invented such schemes with varying degrees of leakage of plaintexts and other attributes of the data.
+For more than a decade, researchers have developed such schemes with varying degrees success.
+Often, thees schemes compromised security to preserve order, leaking plaintexts or other attributes of the data.
 Recently, the first order-preserving encryption scheme that satisfies IND-OCPA, mutable order-preserving encoding (mOPE), was proposed by Popa et al (2013).
-mOPE works by creating a balanced search tree containing all the encrypted data on a server, giving the server the ability the order the tree based on the plaintexts without giving the server information regarding the plaintexts themselves.
-All encrypted values are represented by a node in the balanced search tree that has an encoding, the Order Preserving Encoding (OPE), associated with it which represents its path on the tree from the root to the node, allowing the server the ability to maintain the order of the plaintexts.
+mOPE works by creating a balanced search tree containing all the encrypted data on a server, giving the server the ability to order the tree based on the plaintexts without learning any information regarding the plaintexts themselves.
+All encrypted values are represented by a node in the balanced search tree.
+Each node has an Order Preserving Encoding (OPE) which represents its path on the tree from the root to itself, allowing the server the ability to maintain the order of the plaintexts.
 \\ \\
-One disadvantage of mOPE, however, is that it can leak information about the distribution of plaintext values since multiple entries of the same plaintext value are maintainted in the same node in the tree with a counter.
+One disadvantage of mOPE, however, is that multiple entries of the same plaintext value are maintainted in the same node in the tree with a counter.
+This means that the scheme can leak information about the distribution of plaintext values.
 In this paper, we present two schemes that address this issue: Distribution Confidentiality Scheme (DCS) and Random Tiebreaking Order Preservering Encryption (RTOPE).
@@
 The mOPE scheme by Popa et al (2013) is the first scheme to achieve ideal IND-OCPA security, and our schemes are built upon mOPE.
-Prior work on range query schemes have provided schemes that leak information about the underlying plaintext.
+Prior work on range query schemes all leak information about the underlying plaintext.
 Shi et al (2007) designed an encryption scheme that leaks the decrypted data for values that fall within the range query, but preserves the privacy of all other values.
-We chose to build on schemes on existing OPE schemes, instead of range query schemes, to provide the security of the plaintext even within the range queries.
+We chose to build on schemes on existing OPE schemes, instead of range query schemes, to guarantee that security of underlying plaintext even within the range queries.
 \\ \\
 Further, Popa et al (2013) provides a new security definition, same-time OPE security, which dictates that an adversary can learn the order only for values stored in the application at the same time, and is stronger than IND-OCPA.
-Our security guarantee of IND-CPDA, explained later in the paper, asks that the ciphertexts not leak the distribution of values.
+Our security guarantee of IND-CPDA, explained later in the paper, asks furthermore that the ciphertexts not leak the distribution of values.
 \section{Distribution Confidentiality Scheme}
@@
 This section will give a formal description of DCS. We will first describe the basic version of the scheme, then we will augment it so that decimal numbers can be represented as well. \\ \\
-In the basic version of the scheme, let us assume that we want to encrypt some plaintext value $x \in \mathrm{Z}$ and send it to the server like in Popa et al (2013)'s mOPE scheme.
+In the basic version of the scheme, let us assume that we want to encrypt some plaintext value $x \in \mathrm{Z}$ and send it to the server like in the mOPE scheme.
 For DCS, there is an additional parameter $\rho$ which will govern the probability with which the server sees a repeated value.
@@
 The resulting value $x' = x + r_{\rho}$ will be encrypted with DET.
-Popa et al (2013)'s mOPE scheme will work the same as before, but now acting on $x'$.
+The mOPE scheme will work the same as before, but now acting on $x'$.
 \\ \\
-Inserting in this scheme is simple, since nothing really has to be changed from Popa et al (2013)'s mOPE scheme.
+Inserting in this scheme is simple, since nothing else has to be changed from the mOPE scheme.
 The client will take the value $x$ to insert, create $x'$, then encrypt $x'$ to obtain a ciphertext.
@@
 \end{figure}
-Querying, however, gets more difficult, and the next section will discuss how the client can query for some value $y$. 
+Querying, however, is more difficult, and the next section will discuss how the client can query for some value $y$. 
 \subsection{Querying Under DCS} \\ \\
   To query for some value $y$, we must actually perform a range query, since any value $y$ will be encrypted with a plaintext $y + r$ where $r \in [0,1)$.
-This means, the encrypted plaintext of $y$ can therefore take in the range $[y, y + 1)$.
+Therefore, the encrypted plaintext of $y$ can be in the range $[y, y + 1)$.
 Thus, to query for the value $y$, we must perform a range query on any values in the range $[y, y+1)$.
@@
 Now suppose $x$ is not in the subtree rooted at $l$.
-This means that $x$ must either be smaller than the left-most node in the subtree rooted at $l$ or greater than the right-most node in the subtree (assuming that no nodes are have repeated values which occurs with high probability because of the random bits $r$ appended to each plaintext).
+This means that $x$ must either be smaller than the left-most node in the subtree rooted at $l$ or greater than the right-most node in the subtree (assuming that no nodes are have repeated values, which occurs with high probability because of the random bits $r$ appended to each plaintext).
 However, we know that the left-most node in the subtree rooted at $l$ must be smaller than $y$ and the right-most node in the subtree must be greater than $y+1$.
@@
 We continue this process until the parent of the $y$ node meets the parent of the $y+1$ node.
-This process will find all values in $[y, y+1)$, because as we have shown, all values in the interval are inside the subtree.
+This process will find and return all values in $[y, y+1)$, because as we have shown, all values in the interval are inside the subtree.
 \\ \\
@@
 Winning this game then becomes equivalent to winning the IND-OCPA security game, since one can think of each $v_{ij}$ and $w_{ij}$ pair as a set of values that the adversary provides the client in each round $i$.
-Popa et al (2013) shows that their scheme, which is equivalent to the Distribution Confidentiality Scheme when there are no reptitions, is IND-OCPA secure.
+Popa et al (2013) show that their scheme, which is equivalent to the Distribution Confidentiality Scheme when there are no reptitions, is IND-OCPA secure.
 This means that the DCS scheme is IND-CPDA secure when there are no repeated elements.
@@
 \section{Random Tiebreaking Order Preserving Encryption (RTOPE)}
-Consider a simple tie-breaking rule on top of Popa et al (2013)'s mOPE scheme.
+Consider a simple tie-breaking rule on top of the mOPE scheme.
 When the client inserts a new ciphertext $c^*$ into the server, the client proceeds normally when the ciphertext $c_i$ returned by the server does not correspond to a plaintext $p_i$ which is equal to $p^* = Dec(SK, c^*)$.
@@
 \\ \\
-This scheme is a simple extension of Popa et al (2013)'s scheme and handles repeated values.
-In RTOPE, the server cannot tell how many values are repeated, and what the distribution of repeated values looks like.
+This scheme is a simple extension of the mOPE scheme and handles repeated values. In RTOPE, the server cannot tell how many values are repeated, nor what distribution of repeated values looks like.
 \subsection{Querying Under RTOPE}
-Under RTOPE, there are multiple variations on querying for some value $x$.
+Under RTOPE, there are multiple variations of querying for some value $x$.
 First is to query for just one ciphertext whose corresponding plaintext is equal to $x$.
@@
 Winning this game then becomes equivalent to winning the IND-OCPA security game, since one can think of each $v_{ij}$ and $w_{ij}$ pair as a set of values that the adversary provides the client in each round $i$.
-Popa et al (2013) shows that their scheme, which is equivalent to the Distribution Confidentiality Scheme when there are no reptitions, is IND-OCPA secure.
+Popa et al (2013) shows that their scheme, which is equivalent to the Distribution Confidentiality Scheme when there are no repetitions, is IND-OCPA secure.
 Thus, the base case of no repetitions is secure.
@@
 \begin{proof}
-  This proposition is immediately clear because one can always take the entire tree as the subtree. This works for the cipher text trees stored in both DCS and RTOPE.
+  This proposition is immediately clear because one can always take the entire tree as the subtree. This works for the ciphertext trees stored in both DCS and RTOPE.
 \end{proof}\\ \\
@@
 We then made a testing framework which allowed us to easily change the number of inputs, the number of repeats in the inputs, and the choice of whether to use DCS or RTOPE.
-The results are summarizes in the table below.
+The results are summarized in the table below.
 \\ \\
@@
 \item The standard deviation in OPE re-encodings varies significantly between the two schemes.
-This has to do with the resulting shape of the trees formed for the same inputs -- DCS is more likely to create an unbalanced tree, and thus the standard deviations tend to be higher than comparable RTOPE deviations.
+This has to do with the resulting shape of the trees formed for the same inputs - DCS is more likely to create an unbalanced tree, and thus the standard deviations tend to be higher than comparable RTOPE deviations.
 \item
@@
 We also proved the important theorem that if two OPE schemes are structurally expectation equivalent, then one is IND-CPDA secure if and only if the other is IND-CPDA secure as well.
-We then showed that though DCS and RTOPE do satisfy this structurally expectation equivalence relationship, they are still IND-CPDA secure.
+We then showed that though DCS and RTOPE do not satisfy this structurally expectation equivalence relationship, they are both IND-CPDA secure.
 \\ \\
-We noted that though the schemes are not structurally expectation equivalent, the number of OPE re-encodings will converege to the same number, given identical inputs.
+We also noted that though the schemes are not structurally expectation equivalent, the number of OPE re-encodings will converege to the same number, given identical inputs.
 Finally, this notion was further supported by our experimental results.

### 2013-05-15 paper.tex
Reformatted the paper so that it compiles for me.

@@
 \usepackage{booktabs}
+\usepackage{float}
 
@@
 \newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{definition}{Definition}
 \newtheorem{proposition}[theorem]{Proposition}
@@
 %--------Meta Data: Fill in your info------
-\title{ \\
+\title{
   Preventing Leakage of Distribution in Order Preserving Encryption Schemes \\ \vspace*{.3in}
 \small Hrishikesh Joshi, Max Kolysh, Mari Miyachi, John Wang \\
-\small 6.857 Final Paper \\
-\small May 15, 2013}
+\small 6.857 Final Paper}
+\date{\today}
 
-\date{}
 \begin{document}
@@
 
-\section{Introduction} \\
+\section{Introduction}
+
 Order-preserving encryption schemes serve to generate ciphertexts that preserve the numerical ordering of the plaintexts.
@@
 \end{figure}
+
 \subsection{Handling repeated values}
+
 When the client inserts multiple instances of the same value into the B-tree, the server does not create a new node for each such repeated value.
@@
 Unfortunately, this provides the server the ability to learn about the distribution of values in the B-tree based on the location and magnitute of node counts, and is the primary issue that the remaining portion of this paper addresses.
+
 \subsection{Related Work}
+
 The mOPE scheme by Popa et al (2013) is the first scheme to achieve ideal IND-OCPA security, and our schemes are built upon mOPE.
@@
 Our security guarantee of IND-CPDA, explained later in the paper, asks furthermore that the ciphertexts not leak the distribution of values.
+
 \section{Distribution Confidentiality Scheme}
+
 In order to solve the problem of leaking the distribution of the plaintext values, we have developed the Distribution Confidentiality Scheme (DCS).
@@
 \\ \\
+
 \subsection{Description of DCS}
+
 This section will give a formal description of DCS. We will first describe the basic version of the scheme, then we will augment it so that decimal numbers can be represented as well. \\ \\
@@
 Querying, however, is more difficult, and the next section will discuss how the client can query for some value $y$.
-\subsection{Querying Under DCS} \\ \\
+
+\subsection{Querying Under DCS}
+
   To query for some value $y$, we must actually perform a range query, since any value $y$ will be encrypted with a plaintext $y + r$ where $r \in [0,1)$.
@@
 This is a contradiction, however, because we assumed $x \in [y, y+1)$, which shows that the subtree contains all values $x \in [y, y+1)$.
-\end{proof} \\ \\This lemma instructs us on how to find all values $x \in [y, y+1)$.
+\end{proof}
+
+This lemma instructs us on how to find all values $x \in [y, y+1)$.
 As we move up the binary search tree to parents of $y$, we check the right subtree of the parent looking for all values in $[y, y+1)$.
@@
 The runtime of this is just $\log(n) + K$ where $K$ is the number of values in the range $[y, y+1)$.
+
   \subsection{Range Queries Under DCS}
+
   To perform range queries under the DCS scheme, one simply needs to perform a range query on the underlying binary search tree.
@@
   \item Adversary may perform encryptions and other operations in time $poly(\kappa)$.
-\end{itemize} \\ \\
+\end{itemize}
+
 In phase II, the client and server engage in $poly(\kappa)$ rounds of interaction in which the adversary is adaptive. In each round $i$:
@@
   \item The client leads the interaction for the encryption algorithm on inputs $SK$ and $V_i^b$ with the server, with the adversary observing all the state at the server.
-\end{itemize} \\ \\
+\end{itemize}
+
 In phase III:
@@
   \item Adversary outputs $b'$ as its guess for $b$. 
-\end{itemize} \\ \\
+\end{itemize}
+
 The adversary shall win the game if its guess is correct $b' = b$ and the sets have the same order relations (namely that $v_{ij}^0 < v_{ik}^0 \Leftrightarrow v_{ij}^1 < v_{ik}^1$).
+
 \begin{definition}
   The adversary's advantage is the difference $|Pr[\textrm{win}^{Adv, \kappa, \lambda}] - 1/2|$.
-\end{definition} \\ \\
+\end{definition}
+
 \begin{definition}
@@
 \end{definition}
+
 \subsection{Security of DCS}
+
 \begin{theorem}
-  DCS is IND-CPDA secure 
+  DCS is IND-CPDA secure. 
 \end{theorem}
@@
 \end{proof}
+
 \section{Random Tiebreaking Order Preserving Encryption (RTOPE)}
+
 Consider a simple tie-breaking rule on top of the mOPE scheme.
@@
 This implies that $l = x$, which completes the proof.
-  \end{proof} \\ \\
+  \end{proof}
+
 By the above proposition, we can show that as soon as we find the first value of $x$ based on the regular binary search tree query algorithm, then all other values of $x$ will be contained in either the left or right subtree of this node.
@@
   The runtime of this query is
-  \subsection{Security of RTOPE} \\ \\
+
+  \subsection{Security of RTOPE}
+
   RTOPE can be proven to be IND-CPDA, just like the DCS scheme. 
@@
   \end{proof}
-\section{Relationship Between DCS and RTOPE} \\ \\In this section, we shall propose a notion of equivalence between two OPE schemes.
+
+\section{Relationship Between DCS and RTOPE}
+  In this section, we shall propose a notion of equivalence between two OPE schemes.
+
   \subsection{Structural Expectation Equivalence}
-  \emph{Definition:} Two OPE schemes $x,y$ are \emph{Structural Expectation Equivalent} if for each plaintext $p_i$ that scheme $x$ encodes in a sequence of plaintexts $P = \{p_i\}_{i=1}^n$, there exists some bijective mapping $f: \mathrm{Z}_y \to \mathrm{Z}_x$ where $Pr[Encode_x(c_i) = \omega] = Pr[f(Encode_y(c_i)) = \omega]$ for all $\omega \in \mathrm{Z}_x$ where $\mathrm{Z}_x$ is the space of all possible OPE encodings for scheme $x$, $c_i = Enc(SK, p_i)$ is the ciphertext corresponding to $p_i$, and $Encode_x(c_i)$ and $Encode_y(c_i)$ are the functions that obtain the OPE encoding for schemes $x$ and $y$ respectively.
-\\ \\
+
+\begin{definition} 
+  Two OPE schemes $x,y$ are \emph{Structural Expectation Equivalent} if for each plaintext $p_i$ that scheme $x$ encodes in a sequence of plaintexts $P = \{p_i\}_{i=1}^n$, there exists some bijective mapping $f: \mathrm{Z}_y \to \mathrm{Z}_x$ where $Pr[Encode_x(c_i) = \omega] = Pr[f(Encode_y(c_i)) = \omega]$ for all $\omega \in \mathrm{Z}_x$ where $\mathrm{Z}_x$ is the space of all possible OPE encodings for scheme $x$, $c_i = Enc(SK, p_i)$ is the ciphertext corresponding to $p_i$, and $Encode_x(c_i)$ and $Encode_y(c_i)$ are the functions that obtain the OPE encoding for schemes $x$ and $y$ respectively.
+\end{definition}
+
 In other words, for two schemes to be structurally expectation equivalent, there must exist a mapping $f$ from all of the possible OPE encodings from scheme $x$ to scheme $y$, where the probability of obtaining an encoding in $x$ is the same as the probability of obtaining the corresponding encoding in $y$ (based on the mapping).
@@
 Hence, if $x$ is structurally expectation equivalent to $y$, then $y$ is necessarily structurally expectation equivalent to $x$ because one can simply use $f^{-1}$ as the mapping, which necessarily exists because of $f$ being bijective.
+
 \begin{theorem}
@@
 \end{theorem}
-\begin{proof} \\ \\
+\begin{proof}
 First, we observe that notion of equivalence is symmetric (since $f$ is a bijective mapping which is invertible), so that without loss of generality, we need only show that if $x$ is IND-CPDA secure, then $y$ is as well.
@@
 \end{proof}
+
 \subsection{Structural Expectation Equivalence of DCS and RTOPE}
+
 In this section, we shall investigate whether DCS and RTOPE are structurally expectation equivalent. To do this, we shall first examine some propositions.
+
 \begin{proposition}
  There exists some subtree which contains all the ciphertexts corresponding to a plaintext $x$ in both DCS and RTOPE.
-\end{proposition}\\ \\
+\end{proposition}
 \begin{proof}
   This proposition is immediately clear because one can always take the entire tree as the subtree. This works for the ciphertext trees stored in both DCS and RTOPE.
-\end{proof}\\ \\
+\end{proof}
+
 Since a subtree containing all the ciphertexts corresponding to a plaintext $x$ exists, we can now examine properties of this subtree.
 First, we show that the root of the smallest possible such subtree must be a ciphertext which gets decrypted to $x$.
+
 \begin{proposition}
   The smallest subtree containing all ciphertexts which can be decrypted to some plaintext $x$ is rooted at a ciphertext $c$ such that $x = Dec(SK, c)$ in both DCS and RTOPE.
-\end{proposition}\\ \\
+\end{proposition}
 \begin{proof}
@@
 This means that $Dec(SK, c_l) \leq Dec(SK, c') \leq Dec(SK, c_r)$ which means that $x' = x$, which results in a contradiction (just like in the proof for DCS).
-\end{proof} \\ \\
+\end{proof}
+
 We have seen that the smallest subtree containing a repeated plaintext will be rooted at a ciphertext decrypting to that plaintext.
@@
     DCS and RTOPE are not structurally expectation equivalent.
-  \end{theorem}\\ \\
+  \end{theorem}
   \begin{proof}
@@
   \end{proof}
+
 \subsection{Convergence in Number of Re-encodings}
+
 Although DCS and RTOPE are not structurally expectation equivalent, we can examine other properties between these two schemes.
@@
   \end{proof}
+
 \section{Experimental Results}
+
 To confirm our theoretical analysis, we implemented both the DCS and RTOPE encryption schemes on top of a simplified version of CryptDB.
@@
 \toprule % Top horizontal line
-& \multicolumn{5}{c}{Number of OPE Re-Encodings} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
-\cmidrule(l){2-6} % Horizontal line spanning less than the full width of the table - you can add (r) or (l) just before the opening curly bracket to shorten the rule on the left or right side
+& \multicolumn{4}{c}{Number of OPE Re-Encodings} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
+\cmidrule(l){2-5} % Horizontal line spanning less than the full width of the table - you can add (r) or (l) just before the opening curly bracket to shorten the rule on the left or right side
 Type & Inputs & Repeats & Average & Std. Dev.\\ % Column names row

### 2013-05-15 paper.tex
Making a shitton of changes.

@@
 \usepackage{float}
+\usepackage{listings}
+\usepackage[parfill]{parskip}
 
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{definition}{Definition}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
 \newtheorem{proposition}[theorem]{Proposition}
@@
 The ideal security goal for an order-preserving encryption scheme, IND-OCPA, is for the scheme to reveal nothing except for the order of the plaintexts.
-\\ \\
-For more than a decade, researchers have developed such schemes with varying degrees success.
-Often, thees schemes compromised security to preserve order, leaking plaintexts or other attributes of the data.
+
+For more than a decade, researchers have developed such schemes with varying degrees of success.
+Often, these schemes compromised security to preserve order, leaking plaintexts or other attributes of the data.
 Recently, the first order-preserving encryption scheme that satisfies IND-OCPA, mutable order-preserving encoding (mOPE), was proposed by Popa et al (2013).
@@
 Each node has an Order Preserving Encoding (OPE) which represents its path on the tree from the root to itself, allowing the server the ability to maintain the order of the plaintexts.
-\\ \\
+
 One disadvantage of mOPE, however, is that multiple entries of the same plaintext value are maintainted in the same node in the tree with a counter.
@@
 Further, we define a new security guarantee, Indistinguisability Under Chosen Plaintext Distribution Attack (IND-CPDA), which these schemes are intended to satisfy.
-\\ \\
+
 To better understand the performance and equivalence of our two schemes, we implemented both with a client-server framework that supports insertion and query functionality.
@@
 We show the results of this work, and prove that the two schemes are not structurally expectation equivalent.
-\\ \\
-The rest of the paper is organized as follows.
-II discusses mOPE, including related work.
-III presents DCS in more detail and IV describes IND-CPDA.
-V presents RTOPE in more detail.
-VI compares the two schemes, DCS and RTOPE, and proves their equivalence.
-VII describes the experimental results of our implementation of the two schemes.
-Finally VIII concludes with a brief overview of our overall approach.
+
+The rest of the paper is organized as follows: II discusses mOPE, including related work, III presents DCS, IV describes IND-CPDA, V presents RTOPE, VI compares the two schemes, DCS and RTOPE, VII describes the experimental results of our implementation of the two schemes, and finally VIII concludes with a brief overview of our overall approach.
+
 \section{Mutable Order-Preserving Scheme (mOPE)}
+
 As mentioned earlier, mOPE is the first known order-preserving scheme that satisfies IND-OCPA, leaking nothing with the exception of the order of the plaintexts.
 In this section we describe how mOPE works, including the leakage of distribution that it can lead to.
-We begin with two entities,
-an untrusted server and a client with confidential data as shown in Figure 1. 
+We begin with two entities, an untrusted server and a client with confidential data as shown in Figure 1.
+
 \begin{figure}[htb]
@@
 \end{figure}
+
 \subsection{Storage of Data on Client and Server}
+
 Figure 2 below depicts the data maintained by the client and server at a given point in time.
@@
 It is important to note that the server generates Order-Preserving Encodings (OPEs) for each of the ciphertexts in the B-tree, and preserves a mapping between OPEs and ciphertexts as shown in the table the server maintains.
+
 \begin{figure}[htb]
@@
 \end{figure}
+
 \subsection{Protocol for Maintaining Order on Server}
+
 As stated previously, the server orders the values in the B-tree based on plaintexts without knowing the plaintexts themselves.
@@
 In Figure 3 below, we consider the situation in which the client adds a new plaintext with value 30 and corresponding ciphertext with value 10 to the existing data from Figure 2.
-\\ \\
+
 To insert the value, the client first notifies the server, which subsequently gives back the client the ciphertext of the root node, which is 32.
@@
 In this instance, the node with ciphertext 30 is inserted to the left of the node with ciphertext 16 since the ciphertext 30 has a plaintext with value 10, which is less than the plaintext with value 36 corresponding to the node with ciphertext of value 16.
+
 \begin{figure}[htb]
@@
 We chose to build on schemes on existing OPE schemes, instead of range query schemes, to guarantee that security of underlying plaintext even within the range queries.
-\\ \\
+
 Further, Popa et al (2013) provides a new security definition, same-time OPE security, which dictates that an adversary can learn the order only for values stored in the application at the same time, and is stronger than IND-OCPA.
@@
 We show that the schemes are comprable in terms of performance.
-\\ \\
+
 In essence, the DCS scheme adds random bits to the end of a plaintext so that the ciphertext values are randomized.
 This will prevent the server from being able to identify the number of times a repeated plaintext value is inserted.
-\\ \\
 
@@
 
-This section will give a formal description of DCS. We will first describe the basic version of the scheme, then we will augment it so that decimal numbers can be represented as well. \\ \\
+This section will give a formal description of DCS. We will first describe the basic version of the scheme, then we will augment it so that decimal numbers can be represented as well.
+
 In the basic version of the scheme, let us assume that we want to encrypt some plaintext value $x \in \mathrm{Z}$ and send it to the server like in the mOPE scheme.
@@
 We will generate a random value $r \in [0,1)$ which contains $\rho$ bits, denoted $r_{\rho}$, and append it to the end of $x$.
-The resulting value $x' = x + r_{\rho}$ will be encrypted with DET.
+The resulting value $x' = x + r_{\rho}$ will be encrypted with DET (a deterministic encryption algorithm, whose secret key $SK$ is held by the client but not the server).
 The mOPE scheme will work the same as before, but now acting on $x'$.
-\\ \\
+
+\subsection{Arbitrarily Small Collision Probability}
+
+In this scheme, the probability of any ciphertexts being the same is small, and can be made arbitrarily close to zero by picking a larger $\rho$ parameter.
+In particular, the probability of any ciphertexts being the same is equivalent to the probability of any of the chosen random numbers $r$ being the same for two different encodings of some plaintext $x$.
+
+Notice that this is exactly the birthday paradox problem since we must solve for the probability that any collision occurs.
+There are $2^\rho$ possible random numbers to be chosen.
+Now suppose that some value $x$ has $R(x)$ repetitions at the server, each with a plaintext value of $x'_i = x + r_i$ for the $i$th repetition.
+The probability of a collision and therefore a repeated ciphertext is just one minus the probability of no collisions:
+\begin{eqnarray}
+  Pr[\textrm{Ciphertext Collision of } Encode(SK, x)] = \prod_{i=1}^{R(x)} \left(1 - \frac{i}{2^{\rho}} \right)
+\end{eqnarray}
+
+The above expression is obtained because each newly chosen value $r_{i+1}$ can collide with $i$ previous values, out of the $2^{\rho}$ possible choices of $r_{i+1}$.
+Moreover, we can show that as $\rho \to \infty$, we obtain perfect collision protection.
+\\
+
+\begin{lemma}
+  If there exists some $N$ for which all $\rho > N$ have the property $R(x) \leq 2^{\rho}$ for all $x$ inserted into a DCS server tree, then as $\rho \to \infty$ the probability of collision approaches $0$.
+\end{lemma}
+\begin{proof}
+  The probability of collision approching 0 is equivalent to showing that the probability of no collisions approaches one. We have shown that the probability of no collisions is:
+  \begin{eqnarray}
+    \prod_{i=1}^{R(x)} \left(1 - \frac{i}{2^{\rho}} \right) &\leq& \prod_{i=1}^{R(x)} \left(1 - \frac{R(x)}{2^{\rho}} \right) \\
+                                                    &=& \left(1 - \frac{R(x)}{2^{\rho}} \right)^{R(x)}
+  \end{eqnarray}
+
+  Taking the limit as $\rho \to \infty$ and noting that $R(x) \leq 2^{\rho}$ for all $\rho > N$ so that $\lim_{\rho \to \infty} R(x) / 2^{\rho} = 0$, then we have:
+  \begin{eqnarray}
+    \lim_{\rho \to \infty} \left(1 - \frac{R(x)}{2^{\rho}} \right)^{R(x)} = 1
+  \end{eqnarray}
+
+  This shows that the collision probability approaches 0.
+\end{proof}
+
+Moreover, one can find an upper bound on the collision parameter $\rho$ one needs in order to not have collisions by using the upper bound of $(1 - R(x)/2^{\rho})^{R(x)}$ on the probability of no collisions.
+Setting this equal to one, we obtain:
+\begin{eqnarray}
+  \left(1 - \frac{R(x)}{2^{\rho}} \right)^{R(x)} &=& 1 \\
+                                            \rho &=& \log_2 R(x)
+\end{eqnarray}
+
+Thus, choosing the correct $\rho$ to use is as simple as taking $y = \max_x R(x)$ over all input plaintext values $x$, and setting $\rho = \log_2 y$.
+Unfortunately, it may not be possible to predict $y$ ahead of time before insertions, and in any case, it would be nice to have a dynamic way of changing $\rho$ to the specifications of the problem.
+
+\subsection{Dynamic Version of DCS}
+
+To do this, we change the procedure of DCS slightly so that $\rho$ varies with $R(x)$.
+Note that the change we shall posit in this subsection does not change the insertion or querying mechanisms (to be discussed in the next subsections) and is purely an optimization.
+
+The dynamic scheme will have a new collision parameter $\rho_x$ for each plaintext value $x$.
+We shall keep the invariant that $\rho_x \geq \log_2 R(x)$ at all times.
+We shall also keep a count of the number of times that $x$ has been repeated so far, $R(x)$, in an encrypted block of data on the server.
+Note that this encrypted block will be placed among numerous other data blocks that hold extra information.
+These data blocks are accessed directly by the client and will store data that cannot fit onto a single ciphertext from the mOPE encoding tree.
+The ciphertext blocks from the mOPE tree operate much like inodes in the UNIX filesystem, storing a pointer to the location of the relevant data blocks on the server.
+Each ciphertext in the mOPE tree which encrypts the plaintext $x' = x + r_i$ will store the location of the block containing $R(x)$.
+
+This allows the client to access $R(x)$ whenever he queries for $x$.
+Thus, when attempting to insert some value $x$ into the mOPE tree, the client must first query for $x$ (the process of this will be discussed later), and check the current value of $R(x)$, and increment it on the encrypted block stored on the server.
+Then, the client will select a value $\rho_x \geq \log_2 R(x)$ and use this to construct the random value $|r| = 2^{\rho_x}$ and the ciphertext $c = Encrypt(SK, x + r)$.
+Insertion will then proceed normally.
+
+Note that the ciphertext size for the mOPE tree must be fixed to some constant and that plaintext values will have to be padded.
+If there is no padding, then the adversary would be able to gain information on to the distribution of different repeated values with the same $\rho_x$ values.
+Note that arbitrarily long $\rho_x$ values can be used by simply using a linked list of encrypted data blocks on the server to store some ciphertext $c$ (although this would obviously negatively impact performance).
+All that is left to show is that collisions happen with low probability.
+\\
+
+\begin{proposition}
+  If one sets $\rho_x = c \lfloor \log_2 R(x) \rfloor$, then the probability of a collision is less than $2^c/R(x)^{c-1}$.
+\end{proposition}
+\begin{proof}
+  We will proceed by induction.
+When $R(x) = 0$, this is trivially true since the next item inserted will never collide.
+Now, suppose it holds true for $R(x) = k$.
+We shall show that the $k+1$st insertion will collide with probabability less than $1/R(x)^{c-1}$.
+
+  There are two cases when we insert $x$ the $k+1$st time.
+First, it could be that the collision parameter $\rho_x$ has increased, or in other words $\rho_x = c \lfloor \log_2 k + 1 \rfloor > c \lfloor \log_2 k \rfloor$.
+If this is the case, then the only way that a collision can happen with a previous value is if the first $c \lfloor \log_2 k \rfloor$ bits are the same as a previously held value, and the last $c \lfloor \log_2 k + 1 \rfloor - c \lfloor \log_2 k \rfloor$ bits are zeros.
+This would induce a collision in the scheme and happens with probability $R(x) / 2^{\rho_x}$ since there are $R(x)$ different ways that a previously held value to be followed by zeros can occur, out of the possible $2^{\rho_x}$ values.
+
+  The second case is when the collision parameter $\rho_x$ does not increase.
+In this case, we need to not collide with the $R(x)$ existing values.
+A collision will occur with probability $R(x) / 2^{\rho_x}$, since there are $2^{\rho_x}$ possible choices and $R(x)$ values to collide with.
+
+  Therefore, we see that the probability of collision in either case is:
+  \begin{eqnarray}
+    Pr[\textrm{Collision}] = \frac{R(x)}{2^{\rho_x}} &=& \frac{R(x)}{2^{c \lfloor \log_2 R(x) \rfloor}} \\
+                                                     &\leq& \frac{R(x)}{2^{c \log_2 R(x) - c}} \\
+                                                     &=& \frac{2^c}{R(x)^{c-1}}
+  \end{eqnarray}
+
+  This completes the proof.
+\end{proof}
+
+Therefore, choosing $c$ large enough will work for all values of $R(x)$, and will get better and better as $R(x)$ grows.
+To combat the fact that this probability is close to 1 when $R(x)$ is small, one can simply initialize $\rho_x$ to a larger value than the base case of 1, which makes the probability of collision early on very small.
+Continuing and adding more repetitions of a value $x$ only decreases the probability of collision.
+For instance, when $c = 5$, the probability of collision is around 5\% for 5 repeated inputs, but falls off dramatically to 0.3\% for 10 repeated inputs.
+
+Using a rule like the one used in the above proposition should give a good dynamic scheme for $\rho_x$ which provides low probability of collision.
+
+\subsection{Inserting in DCS}
+
 Inserting in this scheme is simple, since nothing else has to be changed from the mOPE scheme.
@@
 Once it arrives at a leaf node, the client will insert the new ciphertext in the correct direction.
-\begin{figure}
-%\lstset{language=Python}
-%\begin{lstlisting}
-%  TODO: Insert the insertion pseudocode here.
-%\end{lstlisting}
-%\caption{Pseudocode for the Insertion Algorithm}
-%\label{insertion_figure}
+Figure \ref{insertion_figure} provides pseudocode for how one might create an insertion algorithm at the client.
+
+\begin{figure}[htb]
+\lstset{language=Python}
+\begin{lstlisting}[frame=single]
+class Client:
+    def insert(x):
+        r = random()
+        xprime = x + r
+        c = encrypt(client.secret_key, xprime)
+        root_ciphertext = server.get_root()
+        tree_moves(xprime, c, root_ciphertext)
+
+    def tree_moves(value, encrypted_value, ciphertext):
+        plaintext = decrypt(server.secret_key, ciphertext)
+        if value < plaintext:
+            new_ciphertext = server.move_left()
+        elif value > plaintext:
+            new_ciphertext = server.move_right()
+        else:
+            return server.insert(encrypted_value)
+        tree_moves(value, encrypted_value, new_ciphertext)
+\end{lstlisting}
+\caption{Pseudocode for the Insertion Algorithm.
+The algorithm is a communication between the client and the server.
+The client asks for ciphertexts stored on the server, decrypts the ciphertexts, then determines whether to move left or right.}
+\label{insertion_figure}
 \end{figure}
-Querying, however, is more difficult, and the next section will discuss how the client can query for some value $y$.
 
@@
 Therefore, the encrypted plaintext of $y$ can be in the range $[y, y + 1)$.
-Thus, to query for the value $y$, we must perform a range query on any values in the range $[y, y+1)$.
-\\ \\
+Thus, to query for the value $y$, we must perform a range query on any values in the range $[y, y+1]$.
+The client will remove all values which are exactly equal to $y + 1$, but this should be arbitrarily small (in fact the probability will be $2^{-\rho}$ where $\rho$ is the collision parameter) so it should not affect performance in practice.
+Because of this, we shall abuse notation and say the process of querying the range $[y, y+1]$ and removing all values of $y+1$ will be equivalent to just querying the range $[y, y+1)$.
+
 Performing this range query on the binary search tree can be done by searching for $y$ and $y+1$ individually.
@@
 The subtree rooted at the least common ancestor will contain all possible values in the range $[y, y+1)$.
+\\
+
   \begin{lemma}
@@
   \item Adversary may perform encryptions and other operations in time $poly(\kappa)$.
+  \item Client chooses $b \leftarrow \{0,1\}$ uniformly at random (which the adversary does not know about).
 \end{itemize}
@@
 We shall show that encrypting $v = \{V_1, V_2, \ldots, V_{\kappa} \}$ and $w = \{W_1, W_2, \ldots, W_{\kappa}\}$ is information-theoretically the same, where $V_i, W_i$ are sequences of size $\lambda$.
-\\ \\
+
 We will show this by induction on the number of repeated elements in either $V_i$ or $W_i$.
@@
 This means that the DCS scheme is IND-CPDA secure when there are no repeated elements.
-\\ \\
+
 Now we shall use strong induction and assume that when there are a maximum of $k$ repeated elements in both $V_i$ and $W_i$, the DCS scheme is IND-CPDA secure.
 To complete the proof, we simply need to show that when there are $k+1$ repeated elements, the DCS scheme is still secure.
-\\ \\
+
 Let us compare the sets $V_i$ and $W_i$ with $k+1$ repeated elements to the sets with $k$ repeated elements.
@@
 Now consider the plaintext $x$ which is repeated.
-The probability that the OPE encoding of $x$ has already appeared in the sequence of elements in the set $V_i$ or $W_i$ is negligible at $O(2^{-\lambda} \kappa)$.
+The probability that the OPE encoding of $x$ has already appeared in the sequence of elements in the set $V_i$ or $W_i$ is negligible.
 Since the OPE encoding is not repeated by the new value $x$, the number of OPE encoding repetitions is at most $k$.
@@
 Therefore, when there are $k+1$ repeated elements, DCS is IND-CPDA secure.
-\\ \\
 We have therefore shown by induction that DCS is IND-CPDA secure for any number of repeated elements in the sets $V_i$ and $W_i$, which completes the proof that DCS is IND-CPDA secure.
@@
 
-Consider a simple tie-breaking rule on top of the mOPE scheme.
-When the client inserts a new ciphertext $c^*$ into the server, the client proceeds normally when the ciphertext $c_i$ returned by the server does not correspond to a plaintext $p_i$ which is equal to $p^* = Dec(SK, c^*)$.
+Consider another simple tie-breaking rule on top of the mOPE scheme.
+When the client inserts a new ciphertext $c^*$ into the server, the client proceeds normally when the ciphertext $c_i$ returned by the server does not get decrypted to a plaintext $p_i$ which is equal to $p^* = Dec(SK, c^*)$.
 However, if $p_i = p^*$, then the client tells the server to move left or right with uniform probability.
 Note that in this scheme, we will use a randomized encryption scheme which is IND-CCA so that the server cannot tell if two plaintext values are the same.
-\\ \\
+
 To query a ciphertext $c^*$, one needs to make sure to find all possible places where $c^*$ can exist.
@@
 Querying each subtree is done with the  normal Popa et al (2013) process.
-\\ \\
+
 This scheme is a simple extension of the mOPE scheme and handles repeated values. In RTOPE, the server cannot tell how many values are repeated, nor what distribution of repeated values looks like.
+
 \subsection{Querying Under RTOPE}
+
 Under RTOPE, there are multiple variations of querying for some value $x$.
@@
 The second query type is to query for all ciphertexts whose corresponding plaintext is equal to $x$.
-\\ \\
+
 The first case is easy to handle and can be achieved by using the regular query mechanism used by Popa et al (2013) and returning the first ciphertext found which matches.
 If there are any ciphertexts which can be decrypted to $x$, then the regular binary search tree mechanism will find at least one, which guarantees that this will correctly return one of these ciphertexts.
-\\ \\
+
 The second case can be handled by a modified query algorithm.
@@
 Doing this recursively until we reach a leaf will guarantee that we will find all possible places where $x$.
-\\ \\
 This gaurantee can be given in the following proposition: \\ \\
+
   \begin{proposition}
@@
 This implies that we will find all values of $x$ in the tree.
-\\ \\
-  The runtime of this query is
+
+The runtime $T(n)$ of this query can found by noting that in the worst case, every element in the tree is repeated so querying for $x$ will require $O(n)$ time.
+This is an extreme case, however, and it is more likely given by the relation:
+\begin{eqnarray}
+  T(n) = 2 T(n/2) + O(1)
+\end{eqnarray}
+
+Since if a node is found to be the same, then the problem is broken into two smaller problems on the left and right subtrees, which are both of size $O(n/2)$ for a balanced tree.
+The solution of this recurrence is $O(\log n)$, so one can usually expect a logarithmic running time.
 

### 2013-05-15 paper.tex
Finished product.

@@
 \small Hrishikesh Joshi, Max Kolysh, Mari Miyachi, John Wang \\
-\small 6.857 Final Paper}
-\date{\today}
+\small 6.857 Final Paper \\
+\small May 15, 2013}
+\date{}
 
@@
 \maketitle
+
+\abstract{Order Preserving Encryption (OPE) schemes have been heavily studied in the cryptography literature because of their potential application to database design.
+Unfortunately, few schemes have been able to achieve provable security and leak the minimum amount of information possible.
+Until Popa et al (2013), no OPE scheme achieved IND-OCPA security.
+However, even Popa et al's design potentially leaks the distribution of repeated ciphertexts.
+This paper provides two schemes which are both IND-OCPA secure and do not leak the distribution of ciphertexts.
+We introduce the notion of IND-CPDA security, and show that both of our schemes satisfy the notion.
+Finally, we provide experimental results on the effectiveness of these two schemes in practice.}
+
+\newpage
+
+\tableofcontents
+
+\newpage
 
@@
 The mOPE scheme by Popa et al (2013) is the first scheme to achieve ideal IND-OCPA security, and our schemes are built upon mOPE.
-Prior work on range query schemes all leak information about the underlying plaintext.
-Shi et al (2007) designed an encryption scheme that leaks the decrypted data for values that fall within the range query, but preserves the privacy of all other values.
-We chose to build on schemes on existing OPE schemes, instead of range query schemes, to guarantee that security of underlying plaintext even within the range queries.
-
 Further, Popa et al (2013) provides a new security definition, same-time OPE security, which dictates that an adversary can learn the order only for values stored in the application at the same time, and is stronger than IND-OCPA.
 Our security guarantee of IND-CPDA, explained later in the paper, asks furthermore that the ciphertexts not leak the distribution of values.
+Thus, our two schemes provide both same-time OPE security and IND-CPDA security.
+
+Prior work in the field of OPE schemes falls short of providing IND-OCPA, proposed by Boldyreva et al (2009).
+Boldyreva et al (2009) prove that no immutable scheme can achieve IND-OCPA, however, Popa et al (2013) prove that IND-OCPA is in fact achievable with mutable ciphertexts, as described in the procedure above.
+The security alternative that Boldyreva et al (2009) present is that of random order-preserving function (ROPF).
+ROPF asks that an OPE scheme look "as-random-as-possible", while preserving order, and Boldyreva et al (2009) provide an OPE scheme that satisfies the notion of ROPF based on a random order-preserving function.
+However, OPE schemes that fall under the ROPF notion have been shown to leak at least half of the plaintext bits, in addition to order.
+
+Prior work on range query schemes all leak information about the underlying plaintext.
+Shi et al (2007) designed an encryption scheme that encrypts the summaries of encrypted data, such that an authority may decrypt summaries that fall within a specific range.
+This scheme leaks the decrypted data for values that fall within the range query, but preserves the privacy of all other values.
+There is a tradeoff here, as for range queries under OPE schemes, one peice of information can be leaked for every value - the order - while in Shi et al's (2007) scheme, decrypted values are leaked, but nothing beyond the range query.
+We chose to build our schemes upon mOPE, instead of range query schemes, to guarantee that security of underlying plaintext.
+However, it would be interesting to explore the layering of range query schemes with OPE schemes to protect both the order and plaintext values.
 
@@
 
-  RTOPE can be proven to be IND-CPDA, just like the DCS scheme.
+  RTOPE can be proven to be IND-CPDA, just like the DCS scheme. \\
+
   \begin{theorem}
@@
 Again, we shall use induction on the number of repeated elements in either $V_i$ or $W_i$.
-\\ \\
+
 When there are no repeated elements, we can use the same argument we used in the DCS proof.
@@
 Thus, the base case of no repetitions is secure.
-\\ \\
+
 Now, suppose that RTOPE is IND-CPDA secure when there are at most $k$ repetitions across $V_i$ and $W_i$.
 Now consider a sequence where there are $k+1$ repetitions across $V_i$ and $W_i$ for all $i$.
-Select two ciphertexts $c_1$ and $c_2$ of some repeated value $x$ and let us consider how it this pair of repetitions is inserted into the tree.
+Select two ciphertexts $c_1$ and $c_2$ of some repeated value $x$ and let us consider how this pair of repetitions is inserted into the tree.
 Since RTOPE uses an encryption scheme which is IND-CCA for its ciphertexts, the adversary will not be able to tell whether $Dec(SK, c_1) = Dec(SK, c_2)$ with more than $1/2$ probability (by the definition of IND-CCA security).
@@
 \section{Relationship Between DCS and RTOPE}
-  In this section, we shall propose a notion of equivalence between two OPE schemes.
+
+  In this section, we shall propose a notion of equivalence between two OPE schemes and examine whether DCS and RTOPE are equivalent.
 
@@
 Hence, if $x$ is structurally expectation equivalent to $y$, then $y$ is necessarily structurally expectation equivalent to $x$ because one can simply use $f^{-1}$ as the mapping, which necessarily exists because of $f$ being bijective.
+\\
 
@@
 So now we can suppose that $x$ is IND-CPDA secure and $x,y$ are equivalent schemes.
-\\ \\
-Since $x$ is IND-CPDA secure, then for any two sequences $v = \{V_1, V_2, \ldots, V_{\kappa}\}$ and $w = \{W_1, W_2, \ldots, W_{\kappa} \}$ that the adversary provides, the adversary cannot correctly distinguish between $v$ and $w$ with non-neglible advantage.
+
+Since $x$ is IND-CPDA secure, then for any two sequences $v = \{V_1, V_2, \ldots, V_{\kappa}\}$ and $w = \{W_1, W_2, \ldots, W_{\kappa} \}$ that the adversary provides to scheme $x$, the adversary cannot correctly distinguish between $v$ and $w$ with non-neglible advantage.
 Now suppose by contradiction that $y$ is not IND-CPDA secure.
-Then there exist two sequences $v' = \{V_1', \ldots, V_{\kappa}'\}$ and $w' = \{W_1', \ldots, W_{\kappa}'\}$ of plaintexts that the adversary can provide to the client so that he can distinguish the two sequences with non-neglible advantage in the client-server interaction.
-This means that the adversary can distinguish the encoding $Encode_y(V_i') = \{Encode_y(V_{ij}' \}_{j=1}^{\lambda}$ for some $i$ from the encoding $Encode_y(W_i') = \{Encode_y(W_{ij}') \}_{j=1}^{\lambda}$.
-\\ \\
+Then there exist two sequences $v' = \{V_1', \ldots, V_{\kappa}'\}$ and $w' = \{W_1', \ldots, W_{\kappa}'\}$ of plaintexts that the adversary can provide to the client in scheme $y$ so that he can distinguish the two sequences with non-neglible advantage in the client-server interaction.
+This means that the adversary can distinguish the encoding $Encode_y(V_i') = \{Encode_y(V_{ij}') \}_{j=1}^{\lambda}$ for some $i$ from the encoding $Encode_y(W_i') = \{Encode_y(W_{ij}') \}_{j=1}^{\lambda}$.
+
 This means the adversary can also distinguish the mapping $Encode_x(V_i')$ from the encoding $Encode_x(W_i')$ by applying the bijective mapping $f$ (from the definition of equivalence) to obtain $Encode_x(V_i') = f(Encode_y(V_i'))$ and $Encode_x(W_i') = f(Encode_y(W_i'))$.
@@
 
-In this section, we shall investigate whether DCS and RTOPE are structurally expectation equivalent. To do this, we shall first examine some propositions.
+In this section, we shall investigate whether DCS and RTOPE are structurally expectation equivalent. To do this, we shall first examine some propositions. \\
 
@@
 First, we show that the root of the smallest possible such subtree must be a ciphertext which gets decrypted to $x$.
+\\
 
@@
     \{ m_0(x), m_1(x), \ldots, m_k(x) \}
-  \end{eqnarray} \\ \\
+  \end{eqnarray}
 We shall drop the $x$ for convenience and commonly refer to moves as $m_i$. We see that $m_i$ can take on two possibilities, 0 for left or 1 for moving right, and we can characterize the moves:
@@
     \end{array} \right.
-  \end{eqnarray}\\ \\
-Here $p_i$ is the underlying plaintext value of the node at the $i$th move.\\ \\
-We shall proceed to show that the two schemes do not produce the same expected tree. \begin{theorem}
+  \end{eqnarray}
+
+Here $p_i$ is the underlying plaintext value of the node at the $i$th move. We shall proceed to show that the two schemes do not produce the same expected tree. \\
+\begin{theorem}
     DCS and RTOPE are not structurally expectation equivalent.
@@
 Thus, we know that the moves in these cases will be equivalent and the probability of making the moves on non-repeated nodes will be equal.
-\\ \\
+
 Thus, we can reduce our problem to considering a sequence of moves \{$m_i\}_{i=1}^k$ on the plaintext values which are equal to $x$.
-If we can show that the probability of making a particular sequence of moves on the repeated values is the same for DCS and RTOPE, then we will be done.
+By the propsition we proved above, this sequence of moves will be rooted at a ciphertext which is an encrypted value of $x$.
 Making any sequence of moves on repeated values in RTOPE will have probability $2^{-k}$ where $k$ is the number of repeated value in the sequence down the tree.
 This is becase one moves left or right with probability $\frac{1}{2}$.
-\\ \\
+
 Now we shall examine the sequence of moves in DCS.
@@
 Therefore, we need only compare $r_i$ to the value $r^*$, where $r^*$ is the random part of the new plaintext we are inserting.
-\\ \\
+
 The probability that we make a series of moves $\{m_i\}_{i=1}^k$ is the probability that $r^*$ has the $j$ and $j+1$st smallest elements in the sequence of random values $\{ r_i\}_{i=1}^k$.
 Let $n = R(x)$ be the total number of repeated values of $x$.
-\\ \\
+
 It is well known that the probability that the $j$th smallest element falling in the interval $[u, u + du]$ is given by:
@@
       \frac{n!}{(j-1)!(n-j)!} u^{j-1} (1-u)^{n-j} du
-    \end{eqnarray} \\ \\
+    \end{eqnarray}
+
 Therefore, the probability that $r^*$ falls between the $j$th and $j+1$st value is just the difference between all potential values $u_1$ of the $j$th smallest element and all potential values $u_2$ of the $j+1$st element.
@@
       \int_{0}^1 \int_0^{u_2} Pr[U_2 = u_2] Pr[U_1 = u_1] Pr[u_1 < r^* < u_2] d_{u_1} d_{u_2}
-    \end{eqnarray} \\ \\
+    \end{eqnarray}
+
 Where we take $U_1$ as the $j$th smallest value and $U_2$ as the $j+1$st smallest value.
-Thus, the probability of $r^*$ falling in that interval is the integral over all possible values of $U_2$ and $U_1$, and the probabilitiy that it falls inside of the that interval.
-Since $Pr[u_1 < r^* < u_2] = (u_2 - u_1)$, we can write the above as:\\ \\
+Thus, the probability of $r^*$ falling in that interval is the integral over all possible values of $U_2$ and $U_1$, and the probability that it falls inside of the that interval.
+Since $Pr[u_1 < r^* < u_2] = (u_2 - u_1)$, we can write the above as:
 \begin{eqnarray}
       \int_{0}^1 \int_0^{u_2} \left( \frac{n!}{j!(n-j-1)!} u_2^j (1 - u_2)^{n-j-1} \right) \left( \frac{n!}{(j-1)!(n-j)!} u_1^{j-1} (1 - u_1)^{n-j} \right) (u_2 - u_1) d_{u_1} d_{u_2}
-    \end{eqnarray} \\ \\
+    \end{eqnarray}
+
 Letting $C(j) = \frac{n!}{j!(n-j-1)!} \frac{n!}{(j-1)!(n-j)!}$, and integrating the expression for $u_1$, we can obtain the following result:
@@
       C(j) \int_0^1 u_2^j (1 - u_2)^{n-j-1} \left( \frac{(u_2 (n+1) - j) B(j, n-j+1) + u_2^j (1-u_2)^{n-j+1}}{n+1} \right) d u_2
-    \end{eqnarray} \\ \\
-The above is the probability that $r^*$ falls between the $j$th and $j+1$st values.
-Simulating this in the figure below, it is clear that this is not uniform for all values of $j$ (like RTOPE is).
-\\ \\
+    \end{eqnarray}
+
+The above is the probability that $r^*$ falls between the $j$th and $j+1$st values. Simulating this in the figure below, it is clear that this is not uniform for all values of $j$ (like RTOPE is).
     \begin{figure}[H]
@@
     \end{figure}
-  \end{proof}
 
-\subsection{Convergence in Number of Re-encodings}
-
-Although DCS and RTOPE are not structurally expectation equivalent, we can examine other properties between these two schemes.
-In particular, we can show that as $n \to \infty$, if $R_{DCS} / R_{RTOPE} = c$ for some constant $c$ where $R_{i}$ is the number of repetitions for scheme $i$, then the number of re-encodings in DCS and RTOPE will converge to the same number.
-\begin{theorem}
-    As $n \to \infty$, if $R_{DCS} / R_{RTOPE} = c$ for some constant $c$, then the number of re-econdings in DCS and RTOPE will converge to the same number.
-  \end{theorem}
-  \begin{proof}
+  We have therefore shown that DCS and RTOPE are not structurally expectation equivalent.
   \end{proof}
@@
 
-To confirm our theoretical analysis, we implemented both the DCS and RTOPE encryption schemes on top of a simplified version of CryptDB.
-First, we created a framework that mimicked the necessary features of CryptDB, including the client-server interaction and full insertion and query functionality.
+To confirm our theoretical analysis, we implemented both the DCS and RTOPE encryption schemes on top of a simplified client server interface (like the one Popa et al (2013) used).
+First, we created a framework that mimicked the necessary features of an mOPE, including the client-server interaction and full insertion and query functionality.
 We then made a testing framework which allowed us to easily change the number of inputs, the number of repeats in the inputs, and the choice of whether to use DCS or RTOPE.
-The results are summarized in the table below.
-\\ \\
+The results are summarized in the table \ref{tab:results_table}.
+
 \begin{table} % Add the following just after the closing bracket on this line to specify a position for the table on the page: [h], [t], [b] or [p] - these mean: here, top, bottom and on a separate page, respectively
@@
 \label{tab:results_table} % A label for referencing this table elsewhere, references are used in text as \ref{label}
-\end{table} \\ \\
+\end{table}
+
 Each iteration constructed an entire tree from random inputs fitting the input criteria.
 The averages and standard deviations describe the distribution of the number of OPE re-encodings required throughout the construction of the tree.
-We make several observations from the data above:  \\ \\
+We make several observations from the data:
+
 \begin{enumerate}
@@
 The average number of OPE re-encodings is roughly the same for any number of repeated items.
-DCS, each duplicate is converted into a unique number before the insertion phase.
+In DCS, each duplicate is converted into a unique number before the insertion phase.
 In RTOPE, each value is treated as if it were either larger or smaller than its duplicate during the insertion phase.
@@
 \end{enumerate}
+
 \section{Conclusion}
+
  We presented DCS and RTOPE, two order-preserving encryption schemes that achieve ideal IND-CPDA security, where an adversary learns nothing about the distribution of the plaintext values based on the ciphertexts, and only the order of the elements.
@@
 Again, we created a modified querying algorithm for RTOPE that requires recursive queries once one occurence of the plaintext query is found.
-\\ \\
+
 We proved that DCS and RTOPE are IND-CPDA secure and introduced the notion of structurally expectation equivalence.
 We also proved the important theorem that if two OPE schemes are structurally expectation equivalent, then one is IND-CPDA secure if and only if the other is IND-CPDA secure as well.
-We then showed that though DCS and RTOPE do not satisfy this structurally expectation equivalence relationship, they are both IND-CPDA secure.
-\\ \\
-We also noted that though the schemes are not structurally expectation equivalent, the number of OPE re-encodings will converege to the same number, given identical inputs.
-Finally, this notion was further supported by our experimental results.
-We tested our implementation of DCS and RTOPE on a range of inputs, and found that the number of OPE re-encodings were of the same order.
+We then showed that DCS and RTOPE do not satisfy this structurally expectation equivalence relationship.
+
+We noted that though the schemes are not structurally expectation equivalent, the number of OPE re-encodings will converege to the same number, given identical inputs.
+This notion was supported by our experimental results, which we tested on a range of inputs.
 
@@
   2013.
+
+\bibitem{boldyreva11}
+  A. Boldyreva, N. Chenette, and A. O’Neill. 
+  Order-preserving encryption revisited: improved security analysis and alternative
+  solutions. \emph{CRYPTO}, 2011.
 

### 2013-05-15 paper.tex
superficial change made pics smaller
Fixes to the dynmaic DCS changing parameter section.

@@
 %-------Packages---------
-\usepackage{amssymb,amsfonts}
 \usepackage{enumerate}
@@
 \usepackage{listings}
-\usepackage[parfill]{parskip}
 
@@
 \item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
+
+\usepackage{parskip}
 
@@
 
-\abstract{Order Preserving Encryption (OPE) schemes have been heavily studied in the cryptography literature because of their potential application to database design.
+\begin{abstract}
+  Order Preserving Encryption (OPE) schemes have been heavily studied in the cryptography literature because of their potential application to database design.
 Unfortunately, few schemes have been able to achieve provable security and leak the minimum amount of information possible.
@@
 We introduce the notion of IND-CPDA security, and show that both of our schemes satisfy the notion.
-Finally, we provide experimental results on the effectiveness of these two schemes in practice.}
+Finally, we provide experimental results on the effectiveness of these two schemes in practice.
+\end{abstract}
 
@@
 \begin{center}
-\includegraphics[height=1.2in,width=4in,angle=0]{857pic4.png}
+\includegraphics[scale=0.6]{857pic4.png}
 \caption{The client hosts confidential data in encrypted form on the untrusted server. mOPE allows subsequent operations requiring order to be performed on the encrypted data on the untrusted server.}
@@
 \begin{center}
-\includegraphics[height=4.2in,width=6in,angle=0]{857pic6.png}
+\includegraphics[scale=0.6]{857pic6.png}
 \caption{The client hosts a series of plaintexts and their corresponding ciphertexts.
@@
 \begin{center}
-\includegraphics[height=4.5in,width=6in,angle=0]{857pic5.png}
+\includegraphics[scale=0.6]{857pic5.png}
 \caption{The server is able to order the B-tree by the plaintext values of the nodes using an interactive protocol with the client.}
@@
 \begin{eqnarray}
-  Pr[\textrm{Ciphertext Collision of } Encode(SK, x)] = \prod_{i=1}^{R(x)} \left(1 - \frac{i}{2^{\rho}} \right)
+  Pr[\textrm{Ciphertext Collision of } Encode(SK, x)] = 1 - \prod_{i=1}^{R(x)} \left(1 - \frac{i}{2^{\rho}} \right)
 \end{eqnarray}
@@
 
-Moreover, one can find an upper bound on the collision parameter $\rho$ one needs in order to not have collisions by using the upper bound of $(1 - R(x)/2^{\rho})^{R(x)}$ on the probability of no collisions.
-Setting this equal to one, we obtain:
+Moreover, one can find an lower bound on the collision parameter $\rho$ that is needed. We can set the probability of no collisions to 0 and see when items will always collide. We obtain:
 \begin{eqnarray}
-  \left(1 - \frac{R(x)}{2^{\rho}} \right)^{R(x)} &=& 1 \\
+  \left(1 - \frac{R(x)}{2^{\rho}} \right)^{R(x)} &=& 0 \\
                                             \rho &=& \log_2 R(x)
@@
 
-Thus, choosing the correct $\rho$ to use is as simple as taking $y = \max_x R(x)$ over all input plaintext values $x$, and setting $\rho = \log_2 y$.
+Thus, one must choose $\rho > \max_x \log_2 R(x)$ to have a valid $\rho$.
+Anything less will cause collisions with certainty.
+We can also provide a bound on how certain you are of not having a collision.
+If one would like to limit the probability of having a collision to $k$.
+We have:
+\begin{eqnarray}
+  \left(1 - \frac{R(x)}{2^{\rho}} \right)^{R(x)} \leq k
+\end{eqnarray}
+
+Solving for $\rho$, we get:
+\begin{eqnarray}
+   \rho \geq - \log_2 \left( \frac{1 - k^{1/R(x)}}{R(x)} \right)
+\end{eqnarray}
+
+Thus, choosing the correct $\rho$ can be achieved by taking $y = \max_x R(x)$ over all input plaintext values $x$, and setting $\rho > - \log_2 \left( \frac{1 - k^{1/y}}{y} \right)$ for some confidence level $k$.
+Choose $k$ closer to $1$ will result in larger $\rho$, but will give a higher probability of no collisions.
 Unfortunately, it may not be possible to predict $y$ ahead of time before insertions, and in any case, it would be nice to have a dynamic way of changing $\rho$ to the specifications of the problem.
@@
 \section{Indistinguishability Under Chosen Plaintext Distribution Attack (IND-CPDA)}
-This security definition consists of two phases of interaction between the adversary and the challenger. \\ \\
-In phase I:
+
+This security definition consists of two phases of interaction between the adversary and the challenger. In phase I:
+
 \begin{itemize}
@@
 In phase II, the client and server engage in $poly(\kappa)$ rounds of interaction in which the adversary is adaptive. In each round $i$:
+
 \begin{itemize}
@@
 In phase III:
+
 \begin{itemize}
@@
 Here $p_i$ is the underlying plaintext value of the node at the $i$th move. We shall proceed to show that the two schemes do not produce the same expected tree. \\
-\begin{theorem}
+\begin{proposition}
     DCS and RTOPE are not structurally expectation equivalent.
-  \end{theorem}
+\end{proposition}
 \begin{proof}
